### 2015-03-25 template.tex
primeiro commit

%  LaTeX support: latex@mdpi.com
%  In case you need support, please attach any log files that you could have, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).

%=================================================================

% LaTeX Class File and Rendering Mode (choose one)
% You will need to save the "mdpi.cls" and "mdpi.bst" files into the same folder as this template file.

%=================================================================

\documentclass[journal,article,accept,moreauthors,pdftex,12pt,a4paper]{mdpi} 
\usepackage{tikz}
\usepackage{tikz-3dplot}
\usetikzlibrary{shapes,calc,positioning}
\tdplotsetmaincoords{60}{60}
\usepackage{amsmath}
\usepackage{graphicx,subcaption}

%--------------------
% Class Options:
%--------------------
% journal
%----------
% Choose between the following MDPI journals:
% actuators, administrativesciences, aerospace, agriculture, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, appliedsciences, arts, atmosphere, atoms, axioms, batteries, behavioralsciences, bioengineering, biology, biomedicines, biomolecules, biosensors, brainsciences, buildings, cancers, catalysts, cells, challenges, chemosensors, children, chromatography, climate, coatings, computation, computers, cosmetics, crystals, dentistryjournal, diagnostics, diseases, diversity, econometrics, economies, education, electronics, energies, entropy, environmentalsciences, environments, epigenomes, fibers, foods, forests, futureinternet, galaxies, games, gels, genealogy, genes, geosciences, healthcare, horticulturae, humanities, hydrology, informatics, information, inorganics, insects, ijerph, ijfs, ijms, ijgi, jcdd, jcm, jdb, jfb, jimaging, jof, joi, jlpea, jmse, jpm, jrfm, jsan, land, laws, life, lubricants, machines, marinedrugs, materials, mathematics, medicalsciences, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, molbank, molecules, nanomaterials, ncrna, nutrients, pathogens, pharmaceuticals, pharmaceutics, pharmacy, photonics, plants, polymers, processes, proteomes, publications, religions, remotesensing, resources, risks, robotics, safety, sensors, sinusitis, socialsciences, societies, sports, standards, sustainability, symmetry, systems, technologies, toxics, toxins, universe, vaccines, veterinarysciences, viruses, water
%---------
% article
%---------
% The default type of manuscript is article, but could be replaced by using one of the class options: 
% article, review, communication, commentary, bookreview, correction, addendum, editorial, changes, supfile, casereport, comment, conceptpaper, conferencereport, meetingreport, discussion, essay, letter, newbookreceived, opinion, projectreport, reply, retraction, shortnote, technicalnote, creative
%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g. the logo of the journal will get visible), the headings, and the copyright information. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
% Please insert a blank line is before and after all equation and eqnarray environments to ensure proper line numbering when option submit is chosen
%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
%---------
% pdftex
%---------
% The option "pdftex" is for use with pdfLaTeX only. If eps figure are used, use the optioin "dvipdfm", with LaTeX and dvi2pdf only.

%=================================================================
\setcounter{page}{1}
\lastpage{x}
\doinum{10.3390/------}
\pubvolume{xx}
\pubyear{2015}
%\externaleditor{Academic Editor: xx}
\history{Received: xx / Accepted: xx / Published: xx}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================

% Add packages and commands to include here
% The amsmath, amsthm, amssymb, hyperref, caption, float and color packages are loaded by the MDPI class.
%\usepackage{graphicx}
%\usepackage{subfigure,psfig}

%=================================================================
%% Please use the following mathematics environments:
%\theoremstyle{mdpi}
%\newcounter{thm}
%\setcounter{thm}{0}
%\newcounter{ex}
%\setcounter{ex}{0}
%\newcounter{re}
%\setcounter{re}{0}
%\newtheorem{Theorem}[thm]{Theorem}
%\newtheorem{Lemma}[thm]{Lemma}
%\newtheorem{Characterization}[thm]{Characterization}
%\newtheorem{Proposition}[thm]{Proposition}
%\newtheorem{Property}[thm]{Property}
%\newtheorem{Problem}[thm]{Problem}
%\newtheorem{Example}[ex]{Example}
%\newtheorem{Remark}[re]{Remark}
%\newtheorem{Corollary}[thm]{Corollary}
%\newtheorem{Definition}[thm]{Definition}
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================

% Full title of the paper (Capitalized)
\Title{Comparing Probabilistic Predictive Models}

% Authors (Add full first names)
\Author{Marcio A. Diniz $^{1,}$*, Rafael Izbicki $^{1}$, Danilo Lopes $^{1}$ and Luis Ernesto Salasar $^{1}$}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ Department of Statistics, Federal University of S\~ao Carlos, Rod. Washington Luis, km 235, S. Carlos, Brazil}

% Contact information of the corresponding author (Add [2] after \corres if there are more than one corresponding author.)
\corres{e-mail, telephone and fax number of the corresponding author.}

% Abstract (Do not use inserted blank lines, i.e. \\) 
\abstract{This is the abstract section. The abstract should be one section and count less than 200 words.}

% Keywords: add 3 to 10 keywords
\keyword{keyword; keyword; keyword}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{}
%\MSC{}
%\JEL{}

% If this is an expanded version of a conference paper, please cite it here: enter the full citation of your conference paper, and add $^\dagger$ in the end of the title of this article.
%\conference{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

The famous saying of John von Neumann: {\it ``With four parameters I can fit an elephant, and with five I can make him wiggle his trunk''} is a perhaps just a humorous version of Ockham's razor: 
{\it``Entities are not to be multiplied without necessity''}, but illustrates very well a principle that is not often followed by researchers, especially when building predictive models. 
This is true also in the literature of probabilistic sports predictions, particularly regarding models devoted to football predictions.

Bothered by such concerns, we tried to answer the following question: is it possible, using a simple probabilistic model, to predict results of football matches better than more sophisticated or complex models?
To answer this question we compared two sophisticated models with simple multinomial-Dirichlet models that consider only the number of matches won, drawn or lost by each team as inputs.
The models were tested for the second round of the Brazilian football championships of first and second divisions and compared using standard metrics or scoring rules (Brier, logarithmic and spherical).
We also used other criteria such as the proportion of matches that were predicted ``correctly'' by each model and a measure of calibration, both explained in detail below.
According to the adopted criteria, the simple models showed a predictive performance quite similar to the complex ones.

The complex models used here as benchmarks publish their predictions on Internet websites for every matchday and are treated by us as black-box models, since we were not interested in how they were built or the assumptions on which they are based.
We know that\footnote{One of the authors is responsible for one of these models and the other was described in a dissertation.} both models are based on the bivariate Poisson or Holgate distribution, being able to predict the final score of a match given explanatory variables.
\footnote{For more details see \cite{arruda2000}.}
Simulating the model a given number of times, the estimated probability that, for instance, the home team will win, draw or loose is the proportion of times the simulated score favors the home team, were equal or favors the visiting team, respectively.
Therefore, knowing that both model are based on an elaborate parametric model, they are suitable for the comparison we are proposing: simple versus complex models.

There are several ways to score or classify predictions of categorical events like football matches, that assume one out of three possible modes.
See \cite{constantinou} for a brief survey of such measures applied to football.
We decided to, primarily, score the previsions for each match in terms of its distance from the truth, i.e. the verified event, once it has occurred, and chose the most used distances in the literature: Brier (\cite{brier1950}), logarithmic and spherical.
The total inaccuracy of each model is then defined as the sum of the point-wise scores of all its previsions.

This paper is organized as follows.
Section 1 describes the proposed models, Section 2 presents the scoring rules and criteria used in this work to classify the models.
Section 3 reports the performance of the models predicting 380 matches comprising the second half of Brazilian championships of first and second divisions.
In Section 4 we discuss the results and Section 5 closes with some remarks and proposals for future research.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experimental Section}
%% Only for the journal Gels: Please place the Experimental Section after the Conclusions

The black-box models used as benchmarks make their predictions available at {chancedegol.uol.com.br} and {www.previsaoesportiva.com.br}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Multinomial-Dirichlet}

Considering team $A$: the result of its next match may be considered a categorical random quantity (r.q.) that may assume only three modes; win ($W$), draw ($D$) or loss ($L$).

If we denote the probability of $W$, by $\theta_1$, of $D$ by $\theta_2$ and of $L$ by $\theta_3=1-\theta_1-\theta_2$ where $\theta_1+\theta_2\leq 1$.

The p.m.f of such r.q. is

\[
P(X=x|\theta)=\theta_1^{I(x=W)}\theta_2^{I(x=D)}(1-\theta_1-\theta_2)^{I(x=L)}
\]

\noindent
where $\mathcal{X}=\{W,D,L\}$ and $I(x=i)$ is the indicator function, that takes value 1 if $x$ equals $i= W, D, L$ and 0 otherwise; $\theta=\{(\theta_1,\theta_2)\in\Re^2:\theta_1+\theta_2\leq1 ~ \text{and} ~ \theta_i\geq0 ~ \text{for} ~ i=1, 2\}$

We may also call it multivariate Bernoulli r.q.

Assuming that the matches of team $A$, given $\theta$, are i.i.d. with categorical distribution, the sum of $n$ r.q.'s has multinomial distribution with parameters $\theta$ and $n$.

\[
P(M_1=n_1,M_2=n_2,M_3=n_3|\theta,n)=\]
\[
\frac{n!}{n_1!n_2!(n-n_1-n_2)!}\theta_1^{n_1}\theta_2^{n_2}(1-\theta_1-\theta_2)^{n-n_1-n_2}
\]

when $n_1+n_2+n_3=n$ and 0 otherwise, for non-negative integers $n_1$, $n_2$ and $n_3$.

$n_1$ is the number of matches won, $n_2$ the matches drawn and $n_3=n-n_1-n_2$ the matches lost.

{\bf Summary}: under the given assumptions, the vector of matches won, drawn or lost by some team, has multinomial distribution with parameters $n$ and $\theta$.

We want to compute:

\[P(X_{n+1}=W|M_1=n_1,M_2=n_2,M_3=n_3)=p_1;\]

\[P(X_{n+1}=D|M_1=n_1,M_2=n_2,M_3=n_3)=p_2;\] and

\[P(X_{n+1}=L|M_1=n_1,M_2=n_2,M_3=n_3)=p_3.\]

Using Bayesian inference these probabilities are easily computed.

If the prior for $\theta$ is Dirichlet with parameter vector $(\alpha_1,\alpha_2,\alpha_3)$, its density function is:

\[
f(\theta|\alpha)=\frac{\Gamma(\alpha_1+\alpha_2+\alpha_3)}{\Gamma(\alpha_1)\Gamma(\alpha_2)\Gamma(\alpha_3)}\theta_1^{\alpha_1-1}\theta_2^{\alpha_2-1}(1-\theta_1-\theta_2)^{\alpha_3-1}
\]

\noindent
for $\alpha_1$, $\alpha_2$, $\alpha_3 > 0$, then the posterior is Dirichlet with parameters $(n_1+\alpha_1,n_2+\alpha_2,n_3+\alpha_3)$ and it is easy to show that

\[p_1=P(X_{n+1}=W|M_1=n_1,M_2=n_2,M_3=n_3)=\frac{n_1+\alpha_1}{n+\alpha};\]

\noindent
where $n=n_1+n_2+n_3$ and $\alpha=\alpha_1+\alpha_2+\alpha_3$.

Similarly:

\[p_2=P(X_{n+1}=D|M_1=n_1,M_2=n_2,M_3=n_3)=\frac{n_2+\alpha_2}{n+\alpha};\]

\[p_3=P(X_{n+1}=L|M_1=n_1,M_2=n_2,M_3=n_3)=\frac{n_3+\alpha_3}{n+\alpha};\]

Parameters of the prior: (1,1,1), uniform on the simplex.

\section{Scoring rules}

\subsection{Brier score or de Finetti measure}

\begin{center}
\begin{tikzpicture}[scale=2,tdplot_main_coords,axis/.style={->},thick]

% -- remove these 3 lines if no axis is preferred
\draw[axis] (0, 0, 0) -- (1.4, 0, 0) node [right] {$p_1$};
\draw[axis] (0, 0, 0) -- (0, 1.4, 0) node [above] {$p_2$};
\draw[axis] (0, 0, 0) -- (0, 0, 1.4) node [above] {$p_3$};

\coordinate  (d1) at (1,0,0){};
\coordinate  (d2) at (0,1,0){};
\coordinate  (d3) at (0,0,1){};

% fill gray color with opacity
\fill[green!80,opacity=0.2] (d1) -- (d2) -- (d3)-- cycle;

\draw[-, green, thick] (0,0,1) -- (1,0,0);
\draw[-, green, thick] (0,0,1) -- (0,1,0);
\draw[-, green ,thick] (1,0,0) -- (0,1,0);

\node[fill,circle,inner sep=1.5pt,label={left:$(1,0,0)$}] at (d1) {};
\node[fill,circle,inner sep=1.5pt,label={south east:$(0,1,0)$}] at (d2) {};
\node[fill,circle,inner sep=1.5pt,label={left:$(0,0,1)$}] at (d3) {};

\draw[-latex,thick](d3) to [out=60,in=180] (1,1,2);

\node[label={right:away team wins}] at (1,1,2) {};

\draw[-latex,thick](d1) to [out=-90,in=180] (1,1,-1);

\node[label={right:home team wins}] at (1,1,-1) {};

\draw[-latex,thick](d2) to [out=-120,in=180] (1,1,-.25);

\node[label={right:draw}] at (1,1,-.25) {};

\node[fill, blue, circle,inner sep=1.5pt] at (0.25,0.35,0.40) {};

\draw[-latex,thick](0.25,0.35,0.40) to [out=90,in=180] (1,1,1.2);

\node[label={right:$(0.25,0.35,0.40)$: prediction}] at (1,.9,1.2) {};

\end{tikzpicture}
\end{center}

The green surface is the 2-simplex, i.e. the set of point such that $p_1+p_2+p_3=1$ for non-negative values of $p_1$, $p_2$ and $p_3$.

Now let us look just to the simplex (green triangle).
Its sides have length $\sqrt{2}$ and its height is $\sqrt{6}/2$.
Drawing a similar equilateral triangle with height 1 and sides $2\sqrt{3}/3$, all the points originally represented in the simplex can still be represented.

\begin{figure}[!ht]
    \centering
    \begin{subfigure}[b]{0.48\linewidth}        %% or \columnwidth
        \centering

\begin{tikzpicture}[scale=4]
\draw [thick](0,0) -- (1.1547,0) -- (0.57735,1)-- (0,0);

\node[fill, blue, circle,inner sep=1.5pt] at (0.63509,0.40) {};

\draw[dashed,thick] (0.63509,0.40) -- (0.63509,0);
\draw[dashed,thick] (0.63509,0.40) -- (0.85159,0.525);
\draw[dashed,thick] (0.63509,0.40) -- (0.331976,0.575);

\node[label={left:$p_3$}] at (.63509,.2) {};
\node[label={below:$p_1$}] at (.79,.48) {};
\node[label={below:$p_2$}] at (.39,.54) {};

\node[label={below:Home wins}] at (0,0) {};
\node[label={below:Draw}] at (1.1547,0) {};
\node[label={above:Home looses}] at (0.57735,1) {};

\draw[-,thick] (-.5,0) -- (-.5,1);
\draw[-,thick] (-.45,0) -- (-.55,0);
\draw[-,thick] (-.45,1) -- (-.55,1);

\node[label={right:$1$}] at (-.5,.5) {};

\end{tikzpicture}

        \caption{Caption A}
        \label{fig:A}
    \end{subfigure}
    \begin{subfigure}[b]{0.48\linewidth}        %% or \columnwidth
        \centering

\begin{tikzpicture}[scale=4]
\draw [thick](0,0) -- (1.1547,0) -- (0.57735,1)-- (0,0);

\node[fill, blue, circle,inner sep=1.5pt] at (0.63509,0.40) {};
\node[label={below:$p$}] at (0.63509,0.40) {};

\node[label={left:$d$}] at (0.62,0.62) {};

\draw[dashed,thick] (0.63509,0.40) -- (0.57735,1);

\node[label={below:Home wins}] at (0,-0.05) {};
\node[label={below:Draw}] at (1.1547,-0.05) {};
\node[label={above:Home looses}] at (0.57735,1.05) {};

\node[label={below:$(1,0,0)$}] at (0,0.05) {};
\node[label={below:$(0,1,0)$}] at (1.1547,0.05) {};
\node[label={above:$(0,0,1)$}] at (0.57735,0.95) {};

\draw[-,thick] (-.5,0) -- (-.5,1);
\draw[-,thick] (-.45,0) -- (-.55,0);
\draw[-,thick] (-.45,1) -- (-.55,1);

\node[label={right:$\frac{\sqrt{6}}{2}$}] at (-.5,.5) {};

\end{tikzpicture}

        \caption{Caption B}
        \label{fig:B}
    \end{subfigure}
    \caption{ROC curve of failure detection;}
    \label{fig:roc_curve}
\end{figure}

For every point inside this triangle $p_1+p_2+p_3=1$.

\[p=(0.25,0.35,0.40)\]
\[d^2=(0-0.25)^2+(0-0.35)^2+(1-0.40)^2=0.545\]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Example}

Gr\^emio $\times$ Atl\'etico-PR (Matchday 20), at Gr\^emio.

\begin{table}[h]
\begin{center}
\begin{tabular}{lccccccccc}

\hline
 & \multicolumn{3}{c}{Home} & \multicolumn{3}{c}{Away}& \multicolumn{3}{c}{Overall} \\
\hline
\hline
Team & W & D & L & W & D & L & W & D & L\\
\hline
Gr\^emio & 6 & 2 & 1 & 3 & 2 & 5 & 9 & 4 & 6\\
Atl\'etico-PR & 4 & 4 & 2 & 2 & 3 & 4 & 6 & 7 & 6\\
\hline
\end{tabular}
\caption{Gr\^emio and Atl\'etico-PR counts after 19 matchdays (first round)}
\end{center}
\end{table}

$h_1$=number of matches won by Gr\^emio when playing home

$h_2$=number of matches drawn by Gr\^emio when playing home

$h_3$=number of matches lost by Gr\^emio when playing home

\

$(h_1,h_2,h_3)=(6,2,1)$

\[
p_{1h}=\frac{h_1+\alpha_1}{h+\alpha}=\frac{6+1}{9+3}=\frac{7}{12}=0.583\]

\[
p_{2h}=\frac{h_2+\alpha_2}{h+\alpha}=\frac{2+1}{9+3}=\frac{3}{12}=0.25\]

\[
p_{3h}=\frac{h_3+\alpha_3}{h+\alpha}=\frac{1+1}{9+3}=\frac{2}{12}=0.167\]

$a_1$=number of matches won by Atl\'etico-PR when playing away

$a_2$=number of matches drawn by Atl\'etico-PR when playing away

$a_3$=number of matches lost by Atl\'etico-PR when playing away

\

$(a_1,a_2,a_3)=(3,2,5)$

\[
p_{1a}=\frac{a_1+\alpha_1}{h+\alpha}=\frac{2+1}{9+3}=\frac{3}{12}=0.25\]

\[
p_{2a}=\frac{a_2+\alpha_2}{h+\alpha}=\frac{3+1}{9+3}=\frac{4}{12}=0.333\]

\[
p_{3a}=\frac{a_3+\alpha_3}{h+\alpha}=\frac{4+1}{9+3}=\frac{5}{12}=0.417\]

What's the probability that Gr\^emio wins: $p_{1h}=0.583$ or $p_{3a}=0.417$?

What's the probability of a draw: $p_{2h}=0.25$ or $p_{2a}=0.333$?

What's the probability that Gr\^emio looses: $p_{3h}=0.167$ or $p_{1a}=0.25$?

Three ways of combining these probabilities are proposed: (I) a mixture with equal weights to both teams;

\[
\frac{1}{2}\times p_{1h}+\frac{1}{2}\times p_{3a}=\frac{1}{2}\times0.583+\frac{1}{2}\times0.417=0.5
\]

\noindent
is the probability that Gr\^emio wins.

\[
\frac{1}{2}\times p_{2h}+\frac{1}{2}\times p_{2a}=\frac{1}{2}\times0.25+\frac{1}{2}\times0.333=0.2917
\]

\noindent
is the probability of a draw.

\[
\frac{1}{2}\times p_{3h}+\frac{1}{2}\times p_{1a}=\frac{1}{2}\times0.167+\frac{1}{2}\times0.25=0.2083
\]

\noindent
is the probability that Atl\'etico wins.

(II) a mixture with weights (inversely) proportional to the teams rank before the match; 
after 19 matchdays, Gr\^emio was the $6^{th}$ place and Atl\'etico-PR the $11^{th}$:

\[w_1 = \frac{1/6}{1/6+1/11}=0.647 ~ ~ ~ ~ ~ w_2 = \frac{1/11}{1/6+1/11}=0.353\]

\[
w_1\times p_{1h}+w_2\times p_{3a}=0.647\times0.583+0.353\times0.417=0.525 (\text{Gr\^emio wins})
\]

\[
w_1\times p_{2h}+w_2\times p_{2a}=0.647\times0.25+0.353\times0.333=0.279 (\text{draw})
\]

\[
w_1\times p_{1h}+w_2\times p_{3a}=0.647\times0.167+0.353\times0.25=0.196 (\text{Atl\'etico wins})
\]

(III) combine the counts to generate one prediction:

$(h_1,h_2,h_3)=(6,2,1)$ and $(a_1,a_2,a_3)=(2,3,4)$ $\Rightarrow$ $(c_1,c_2,c_3)=(10,5,3)$

$c_1=h_1+a_3 \Rightarrow$ number of matches won by Gr\^emio playing home plus matches lost by Atl\'etico playing away.

\[\frac{c_1+\alpha_1}{c+\alpha}=\frac{10+1}{18+3}=0.524
\]

\[\frac{c_2+\alpha_3}{c+\alpha}=\frac{5+1}{18+3}=0.286
\]

\[\frac{c_3+\alpha_3}{c+\alpha}=\frac{3+1}{18+3}=0.190
\]

\noindent
where $c=c_1+c_2+c_3$, $c_2=h_2+a_2$ and $c_3=h_3+a_1$.

Final result: Gr\^emio 1 $\times$ 0 Atl\'etico-PR

\begin{table}[h]
\begin{center}
\begin{tabular}{ccccc}

\hline
Model & Gr\^emio & Draw & Atl\'etico-PR & Score \\
\hline
\hline
BB1 & 0.505 & 0.263 & 0.232 & 0.368 \\
BB2 & 0.55 & 0.27 & 0.18 & 0.308 \\
$Mn-Dir_1$ & 0.50 & 0.292 & 0.208 & 0.379 \\
$Mn-Dir_2$ & 0.525 & 0.279 & 0.196 & 0.342\\
$Mn-Dir_3$ & 0.524 & 0.286 & 0.190 & 0.345\\
\hline
\end{tabular}
%\caption{Score of the ten first rounds and mean score per match after 190 matches}
\end{center}
\end{table}

\section{Results}

\subsection{First Division (S\'erie A)}

\begin{table}[h]
\begin{center}
\begin{tabular}{cccccc}

\hline
Matchday & BB1 & BB2 & $Mn-Dir_1$ & $Mn-Dir_2$ & $Mn-Dir_3$\\
\hline
\hline
1$^{st}$ &4.992 & 5.055 & 5.630 & 5.053 & 5.521 \\
2$^{nd}$ &5.006 & 5.328 & 5.327 & 5.533 & 5.201 \\
3$^{rd}$ &7.129 & 6.568 & 7.979 & 7.640 & 8.216 \\
4$^{th}$ &5.941 & 5.782 & 6.513 & 6.848 & 6.564 \\
5$^{th}$ &5.246 & 5.858 & 5.669 & 5.368 & 5.601 \\
6$^{th}$ &5.584 & 5.095 & 6.055 & 6.112 & 6.033 \\
7$^{th}$ &5.641 & 5.817 & 5.250 & 5.062 & 5.134 \\
8$^{th}$ &6.112 & 6.710 & 6.315 & 6.673 & 6.348 \\
9$^{th}$ &6.433 & 6.714 & 5.768 & 6.061 & 5.717 \\
10$^{th}$ &4.912 & 4.620 & 6.019 & 6.115 & 6.010 \\
\hline
Total & 111.04 & 111.32 & 115.45 & 115.36 & 115.29 \\
\hline
Mean & 0.5844 & 0.5859 & 0.6076 & 0.6072 & 0.6068 \\
\hline
\end{tabular}
\caption{Score of the ten first rounds and mean score per match after 190 matches}
\end{center}
\end{table}

\subsection{Second Division (S\'erie B)}

\begin{table}[h]
\begin{center}
\begin{tabular}{ccccc}

\hline
Matchday & BB1 & $Mn-Dir_1$ & $Mn-Dir_2$ & $Mn-Dir_3$\\
\hline
\hline
1$^{st}$ & 7.267 & 8.003 & 8.131 & 8.263 \\
2$^{nd}$ & 5.633 & 6.073 & 6.119 & 6.057 \\
3$^{rd}$ & 7.183 & 7.086 & 7.384 & 7.183 \\
4$^{th}$ & 7.458 & 6.776 & 6.731 & 6.829 \\
5$^{th}$ & 5.246 & 5.492 & 5.494 & 5.414 \\
6$^{th}$ & 5.126 & 5.169 & 5.589 & 5.043 \\
7$^{th}$ & 5.837 & 5.033 & 4.939 & 4.897 \\
8$^{th}$ & 7.462 & 6.616 & 6.509 & 6.667 \\
9$^{th}$ & 8.223 & 7.520 & 7.733 & 7.671 \\
10$^{th}$ & 4.818 & 5.623 & 5.825 & 5.578 \\
\hline
Total & 118.00 & 117.68 & 119.33 & 117.70 \\
\hline
Mean & 0.6178 & 0.6161 & 0.6248 & 0.6162 \\

\hline
\end{tabular}
\caption{Score of the ten first rounds and mean score per match after 191 matches}
\end{center}
\end{table}

\begin{table}[h]
\begin{center}
\begin{tabular}{ccccc}

\hline
BB1 & $Mn-Dir_1$ & $Mn-Dir_2$ & $Mn-Dir_3$\\
\hline
\hline
0.6011 & 0.6119 & 0.6159 & 0.6115\\
\hline
\multicolumn{4}{c}{Chance de gol historic mean (1998-2015): 0.5977}\\
\hline
\end{tabular}
\caption{First and Second Divisions means}
\end{center}
\end{table}

\section{Discussion}
%De Finetti was a radical subjectivist and pragmatist about probability and did not believe that it even made sense to talk about credences as being ``accurate'' or ``inaccurate''. 
%Like Ramsey and Savage, he offered pragmatic arguments for probabilism. 
%As a result, de Finetti did not speak of ``measures of inaccuracy'' or ``measures of distance from the truth'': he used the terms ``scoring rule'' and ``loss function''.

%De Finetti used what is called the Brier score, which is just the (squared) Euclidean distance — i.e., the sum of the squared differences between credences and (the 0/1 numerical correlates of) truth values.

It is possible to interpret the score as a numerical measure of how inaccurate was the 
prevision.

\begin{itemize}

\item Markov chain: the transitions ($W\to D$, $W \to L$ etc) have multinomial distribution;

\item other weights to combine the predictions from both teams;

\item other distances;

\item \dots  
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusions}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\acknowledgments{Acknowledgments}

Main text.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\authorcontributions{Author Contributions}

Main text.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\conflictofinterests{Conflicts of Interest}

State any potential conflicts of interest here or ``The authors declare no conflict of interest''.

%=================================================================
% References: Variant A
%=================================================================
% Back Matter (References and Notes)
%----------------------------------------------------------
% Style and layout of the references
\bibliographystyle{mdpi}
\makeatletter
\renewcommand\@biblabel[1]{#1. }
\makeatother

\begin{thebibliography}{999} % if there are less than 10 entries, enter a one digit number

% Reference 1
\bibitem{ref-journal}
Lastname, F.; Author, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142-149.

% Reference 2
\bibitem{ref-book}
Lastname, F.F.; Author, T. The title of the cited contribution. In {\em The Book Title}; Editor, F., Meditor, A., Eds.; Publishing House: City, Country, 2007; pp. 32-58.

\bibitem{arruda2000}
Arruda, M. L. {\em Poisson, Bayes, Futebol e De Finetti}, M. A. dissertation (in Portuguese), University of S\~ao Paulo, 2000.

\bibitem{brier1950}
Brier, G. Verification of forecasts expressed in terms of probability. {\em Monthly Weather Review} {\bf 1950}, {\em 78}, 1-3.

\bibitem{constantinou}
Constantinou, A. and Fenton, N. E. Evaluating the Predictive Accuracy of Association Football Forecasting Systems. Unpublished paper.

\end{thebibliography}

%=================================================================
% References:  Variant B
%=================================================================
% Use the following option to include external BibTeX files:
%\bibliography{lite}
%\bibliographystyle{mdpi}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\abbreviations{Abbreviations/Nomenclature}
%
%Main text.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\appendix
%\section{Appendix Title}
%
%Main text.

\end{document}

### 2015-03-25 template.tex
Sugestoes do Rafael.

@@
 % Full title of the paper (Capitalized)
-\Title{Comparing Probabilistic Predictive Models}
+\Title{Comparing probabilistic predictive models applied to football}
 
@@
 
-Bothered by such concerns, we tried to answer the following question: is it possible, using a simple probabilistic model, to predict results of football matches better than more sophisticated or complex models?
-To answer this question we compared two sophisticated models with simple multinomial-Dirichlet models that consider only the number of matches won, drawn or lost by each team as inputs.
-The models were tested for the second round of the Brazilian football championships of first and second divisions and compared using standard metrics or scoring rules (Brier, logarithmic and spherical).
+Bothered by such concerns, our goal was to answer the following question: is it possible, using a simple probabilistic model, to predict results of football matches better than more sophisticated or complex models?
+To answer this, we compared two sophisticated models with simple multinomial-Dirichlet models that consider only the number of matches won, drawn or lost by each team as inputs.
+The models were tested for the second round of the Brazilian football championships of first and second divisions and compared using standard metrics or scoring rules.
 We also used other criteria such as the proportion of matches that were predicted ``correctly'' by each model and a measure of calibration, both explained in detail below.
-According to the adopted criteria, the simple models showed a predictive performance quite similar to the complex ones.
+According to the adopted criteria, the simple models showed a similar predictive performance to the complex ones.
 
-The complex models used here as benchmarks publish their predictions on Internet websites for every matchday and are treated by us as black-box models, since we were not interested in how they were built or the assumptions on which they are based.
+The predictions of the complex models used here as benchmarks are published on Internet websites for every matchday, and are treated by us as black-box models since we are not interested in how they were built or the assumptions on which they are based.
 We know that\footnote{One of the authors is responsible for one of these models and the other was described in a dissertation.} both models are based on the bivariate Poisson or Holgate distribution, being able to predict the final score of a match given explanatory variables.
 \footnote{For more details see \cite{arruda2000}.}
-Simulating the model a given number of times, the estimated probability that, for instance, the home team will win, draw or loose is the proportion of times the simulated score favors the home team, were equal or favors the visiting team, respectively.
-Therefore, knowing that both model are based on an elaborate parametric model, they are suitable for the comparison we are proposing: simple versus complex models.
+Therefore, to estimate the probability that, for instance, the home team will win, the estimated model---the model estimated with available information---is simulated a given number of times and the proportion of simulated scores favoring the home team will be the predicted probability of the model.
+Knowing that both models are based on an elaborate parametric model, they are suitable for the comparison we are proposing: simple versus complex models.
 
-There are several ways to score or classify predictions of categorical events like football matches, that assume one out of three possible modes.
+There are several ways to score or classify predictions of categorical events that assume one out of three possible outcomes, like football matches.
 See \cite{constantinou} for a brief survey of such measures applied to football.
-We decided to, primarily, score the previsions for each match in terms of its distance from the truth, i.e.
+We decided to score the previsions for each match in terms of their distances from the truth, i.e.
 the verified event, once it has occurred, and chose the most used distances in the literature: Brier (\cite{brier1950}), logarithmic and spherical.
@@
 Section 3 reports the performance of the models predicting 380 matches comprising the second half of Brazilian championships of first and second divisions.
-In Section 4 we discuss the results and Section 5 closes with some remarks and proposals for future research.
+In Section 4 we discuss the results, and Section 5 closes with some remarks and proposals for future research.
 
@@
 
-We want to compute:
+Our goal is to compute:
 
@@
 
-Using Bayesian inference these probabilities are easily computed.
-
-If the prior for $\theta$ is Dirichlet with parameter vector $(\alpha_1,\alpha_2,\alpha_3)$, its density function is:
+Using Bayesian inference these probabilities are easily computed: if the prior for $\theta$ is Dirichlet with parameter vector $(\alpha_1,\alpha_2,\alpha_3)$, i.e. its density function is
 
@@
 \noindent
-for $\alpha_1$, $\alpha_2$, $\alpha_3 > 0$, then the posterior is Dirichlet with parameters $(n_1+\alpha_1,n_2+\alpha_2,n_3+\alpha_3)$ and it is easy to show that
+for $\alpha_1$, $\alpha_2$, $\alpha_3 > 0$, then the posterior is Dirichlet with parameters $(n_1+\alpha_1,n_2+\alpha_2,n_3+\alpha_3)$, and hence
 
@@
 
-Similarly:
+Similarly
 
@@
 
-\subsection{Brier score or de Finetti measure}
+\subsection{Brier score}
 
+\begin{figure}
 \begin{center}
@@
 \end{tikzpicture}
+\caption{Bi-dimensional simplex (green surface): area of possible predictions}\label{fig:simplex}
 \end{center}
+\end{figure}
 
-The green surface is the 2-simplex, i.e. the set of point such that $p_1+p_2+p_3=1$ for non-negative values of $p_1$, $p_2$ and $p_3$.
-
-Now let us look just to the simplex (green triangle).
-Its sides have length $\sqrt{2}$ and its height is $\sqrt{6}/2$.
-Drawing a similar equilateral triangle with height 1 and sides $2\sqrt{3}/3$, all the points originally represented in the simplex can still be represented.
+The green surface represents the 2-simplex, i.e. the set of points such that $p_1+p_2+p_3=1$ for non-negative values of $p_1$, $p_2$ and $p_3$.
+The triangle representing the simplex has sides of length $\sqrt{2}$ and its height is $\sqrt{6}/2$.
+Drawing a similar equilateral triangle with height 1 and sides $2\sqrt{3}/3$, it is possible to represent all the points of the simplex.
+This new triangle is usually used to graphically display the predictions as internal points because the sum of the distances of every point inside it to each side is always one representing the probability of each event.
 
@@
 
-        \caption{Caption A}
+        \caption{Normalized simplex: $p_1+p_2+p_3=1$}
         \label{fig:A}
@@
 
-        \caption{Caption B}
+        \caption{Original simplex: used to compute the Brier score}
         \label{fig:B}
     \end{subfigure}
-    \caption{ROC curve of failure detection;}
-    \label{fig:roc_curve}
+    \caption{Normalized and standard simplexes}
+    \label{fig:norm_stand}
 \end{figure}

### 2015-04-08 template.tex
Teste
Inicio conclusoes e fucoes de perda

@@
 
+it is all wrong.
+
 If we denote the probability of $W$, by $\theta_1$, of $D$ by $\theta_2$ and of $L$ by $\theta_3=1-\theta_1-\theta_2$ where $\theta_1+\theta_2\leq 1$.
@@
 
-\section{Scoring rules}
+\section{Scoring rules and calibration}
+
+How can we fairly distinguish better-informed states of knowledge from more poorly informed states?
+Using proper scoring rules for evaluating states of uncertain knowledge.
+A scoring rule is a function of two variables (or vectors, matrices etc) that accords a real number (score) to each pair of numbers that could represent the value of X and the prevision value, P(X).
+It is maximum for each x when x=P(X) and nonincreasing as x departs from P(X) for each P(X), and as P(X) departs from x for each x.
+The best score is achieved when knowledge of X is asserted as the value of X itself, whatever it might be.
+Most of the scoring rules exhibit an arbitrary normalizing feature, that S[x,P(X)]=0 for each x.
+Many functions satisfy the criteria for a scoring rule specified above, but not every scoring rule would be regarded as providing a fair assessment of the assertion P(X).
+Proper scoring rules encourages honesty and accuracy in assessing numerical values for their previsions.
+
+One usage of a scoring function could be to give a reward of $S(\mathbf{r},i)$ if the ith event occurs.
+If a proper scoring rule is used, then the highest expected reward is obtained by reporting the true probability distribution.
+The use of a proper scoring rule encourages the forecaster to be honest to maximize the expected reward.
+
+The scoring rule is constructed according to the basic idea that the resulting device should oblige each participant to express his true feelings, because any departure from his own personal probability results in a diminution of his own average score as he sees it.
+
+Moreover, this method leads automatically to an overall comparison between the outcomes of different personal evaluations concerned with the same totality of events.
+The accumulated loss is indeed a throughly concrete measure of success.
+
+Proper scoring rules are devised so that no one previses (expects) that intrigue in falsely announcing some other number as P(X) would be advantageous for achieving a better score.
+The particular scoring functions we study in the generic form S(X,P(X)) can also be considered as utility functions, U(X,P(X)).
+The principle of asserting numerical values for P(X) in such a way as to maximize your prevision for your score is equivalent to acting in a decision problem so as to maximize your expected utility.
+
+Probability assertions are said to be well calibrated at the level of probability p if the observed proportion of all propositions that are assessed with probability p equals p.
+
+A person's probability assertions are said to be well calibrated at the value p if the limiting frequency of occurrence of events that are assessed with probability p, equals p.
 
@@
 
-\begin{itemize}
-
-\item Markov chain: the transitions ($W\to D$, $W \to L$ etc) have multinomial distribution;
-
-\item other weights to combine the predictions from both teams;
-
-\item other distances;
-
-\item \dots  
-\end{itemize}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Conclusions}
+
+We compared the probabilistic predictions of three simple models with the ones provided by two more complex models for the second round of the 2014 Brazilian football championships of first and second divisions.
+According to standard scoring rules and other criteria here adopted to qualify the predictions, our results show that the predictive power of all models was quite similar.
+
+On the one hand, our findings appear as another supportive example of Ockham's razor but, on the other, poses several questions about probabilistic prediction of sport events.
+We mention just a couple of them, raised by the similar performance of the considered models: is there an irreducible ``randomness'' or ``degree of unpredictability'' implicit in these events?
+Is this degree an indicator of how close is the championship being studied?
+To answer these questions we would have to consider more championships and models and compare them using other scoring rules, being a suggestion for further research.
+Also as future research we would like to test other weights and study their impact on the predictive power of models 1 and 2 here proposed.
+
+%The most useful statement of the principle for scientists is
+%"when you have two competing theories that make exactly the same predictions, the simpler one is the better."
+
+%What to infer from known recorded measurements about the values of yet unrecorded measurements is the responsibility of each knowing person.
+%There is general agreement in evaluating the evidence that the measured observations provide for yet unmeasured experiences.
+%There have been controversies among very respected scientists regarding what conclusions are to be drawn from observations.
 

### 2015-05-08 template.tex
teste Rafael

--- 2015-03-25 template.tex
@@
 \usepackage{graphicx,subcaption}
+
+\usepackage{color}
+\newcommand{\red}[1]{\textbf{\color{red} ***ATT*** #1}}
+
+\usepackage{changes}
+\definechangesauthor[name={Rafael}, color=blue]{raf}
+\setremarkmarkup{(#2)}
 
@@
 Bothered by such concerns, our goal was to answer the following question: is it possible, using a simple probabilistic model, to predict results of football matches better than more sophisticated or complex models?
-To answer this, we compared two sophisticated models with simple multinomial-Dirichlet models that consider only the number of matches won, drawn or lost by each team as inputs.
+To answer this, we compared two sophisticated models \added{that consider several covariates} with simple multinomial-Dirichlet models that consider only the number of matches won, drawn or lost by each team as inputs.
 The models were tested for the second round of the Brazilian football championships of first and second divisions and compared using standard metrics or scoring rules.
-We also used other criteria such as the proportion of matches that were predicted ``correctly'' by each model and a measure of calibration, both explained in detail below.
+We also used other criteria such as the proportion of matches that were predicted ``correctly'' by each model and a measure of calibration, both explained in details below.
 According to the adopted criteria, the simple models showed a similar predictive performance to the complex ones.
@@
 The predictions of the complex models used here as benchmarks are published on Internet websites for every matchday, and are treated by us as black-box models since we are not interested in how they were built or the assumptions on which they are based.
-We know that\footnote{One of the authors is responsible for one of these models and the other was described in a dissertation.} both models are based on the bivariate Poisson or Holgate distribution, being able to predict the final score of a match given explanatory variables.
-\footnote{For more details see \cite{arruda2000}.}
-Therefore, to estimate the probability that, for instance, the home team will win, the estimated model---the model estimated with available information---is simulated a given number of times and the proportion of simulated scores favoring the home team will be the predicted probability of the model.
-Knowing that both models are based on an elaborate parametric model, they are suitable for the comparison we are proposing: simple versus complex models.
+We know that\footnote{One of the authors is responsible for one of these models and the other was described in a dissertation.} both models are based on the bivariate Poisson or Holgate distributions, and are able to predict the final score of a match given explanatory variables.\footnote{For more details see \cite{arruda2000}.}
+\deleted[remark={acho que essa parte nao eh tao simples de entender e nao eh vital para o artigo}]{Therefore, to estimate the probability that, for instance, the home team will win, the estimated model---the model estimated with available information---is simulated a given number of times and the proportion of simulated scores favoring the home team will be the predicted probability of the model.} \added{Both models output three probabilities for each match: the probability that the house team wins, the probability that
+the visitor wins, and the probability that there is a draw.} \red{usei a nomenclatura correta na frase anterior?}
+\replaced{Because both}{Knowing that both} models are based on an elaborate parametric model, they are suitable for the comparison we are proposing: simple versus complex models.
 
@@
 the verified event, once it has occurred, and chose the most used distances in the literature: Brier (\cite{brier1950}), logarithmic and spherical.
-The total inaccuracy of each model is then defined as the sum of the point-wise scores of all its previsions.
+\deleted{The total inaccuracy of each model is then defined as the sum of the point-wise scores of all its previsions.}
 
 This paper is organized as follows.
-Section 1 describes the proposed models, Section 2 presents the scoring rules and criteria used in this work to classify the models.
-Section 3 reports the performance of the models predicting 380 matches comprising the second half of Brazilian championships of first and second divisions.
-In Section 4 we discuss the results, and Section 5 closes with some remarks and proposals for future research.
+Section \ref{sec::experimental} describes the proposed models, Section \ref{sec::scoring} presents the scoring rules and criteria used in this work to classify the models.
+Section \ref{sec::results} reports the performance of the models predicting 380 matches comprising the second half of Brazilian championships of first and second divisions.
+In Section \ref{sec::discussion} we discuss the results, and Section \ref{sec::conclusions} closes with some remarks and proposals for future research.
+\red{talvez juntar as duas ultimas secoes?}
 
@@
 \section{Experimental Section}
+\label{sec::experimental}
 %% Only for the journal Gels: Please place the Experimental Section after the Conclusions
 
-The black-box models used as benchmarks make their predictions available at {chancedegol.uol.com.br} and {www.previsaoesportiva.com.br}.
+The black-box models used as benchmarks make their predictions available at \url{chancedegol.uol.com.br} and \url{www.previsaoesportiva.com.br}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\red{nao olhei o resto desta secao}
 
@@
 Considering team $A$: the result of its next match may be considered a categorical random quantity (r.q.) that may assume only three modes; win ($W$), draw ($D$) or loss ($L$).
+
+it is all wrong.
 
@@
 
-\section{Scoring rules}
+\section{Scoring rules and calibration}
+\label{sec::scoring}
 
-\subsection{Brier score}
+How can we fairly distinguish better-informed states of knowledge from more poorly informed states?
+\replaced{A way of doing this is to use proper scoring rules for evaluating states of uncertain knowledge.}{Using proper scoring rules for evaluating states of uncertain knowledge.}
+A scoring rule is a function of two variables (or vectors, matrices etc) that \replaced{assigns}{accords} a real number (score) 
+\replaced{to each
+possible outcome $X$ and its respective prevision value, $P(X)$.}{
+to each pair of numbers that could represent the value of $X$ and the prevision value $P(X)$.}
+\replaced{ It is maximum for each $x$ when $x=P(X)$, and is nonincreasing both as $x$ departs from $P(X)$ (for each $P(X)$) and as $P(X)$ departs from $x$ (for each $x$).}{It is maximum for each $x$ when $x=P(X)$, and nonincreasing as $x$ departs from $P(X)$ for each $P(X)$, and as $P(X)$ departs from $x$ for each $x$.
+} \added{Thus},
+the best score is achieved when knowledge of $X$ is asserted as the value of $X$ itself, whatever it might be.
+Most of the scoring rules \added{also} exhibit an arbitrary normalizing feature \added{such that} $S[x,P(X)]=0$ for each $x$.
+
+Although many functions satisfy the criteria for a scoring rule specified above, not every scoring rule \replaced{can}{would} be regarded as providing a fair assessment of the assertion $P(X)$.
+That is,
+not all scoring rules encourage honesty and accuracy in assessing numerical values for their   previsions.
+Those that do encourage a fair assessment are named \emph{proper scoring rules} \red{colocar referencia}.
+
+\added{Say a forecaster's uncertainty about $X$ is $P_0$.
+A proper scoring rule is a scoring rule $S$ such that the prevision value $P(X)$ that minimizes $E_{P_0}[S(X,P(X))]$ is $P_0$.
+} \replaced{In other words, if one receives a reward $S(x,P(x))$ when $x$ happens and if $S$ is a proper scoring rule, then the highest expected reward is obtained by reporting one's  true uncertainty about $X$}{Imagine one receives a reward of $S(\mathbf{r},i)$ if the $i$-th event occurs.} The use of a proper scoring rule \added{thus} encourages the forecaster to be honest \deleted{to maximize the expected reward}.
+
+The scoring rule is constructed according to the basic idea that the resulting device should oblige each participant to express his true feelings, because any departure from his own personal probability results in a diminution of his own average score as he sees it.
+\red{esse paragrafo me parece um pouco redundante, serah que eh melhor tirar?}
+
+Moreover, this method leads automatically to an overall comparison between the outcomes of different personal evaluations concerned with the same totality of events.
+The accumulated loss is indeed a \replaced{truly?}{throughly} concrete measure of success.
+
+\added{In what follows, we describe in detais three proper scoring rules we use to asses the various models considered. We also 
+recall the concept of calibration.}
+
+\red{parei de rever essa secao aqui}
+
+Proper scoring rules are devised so that no one previses (expects) that intrigue in falsely announcing some other number as $P(X)$ would be advantageous for achieving a better score.
+The particular scoring functions we study in the generic form $S(X,P(X))$ can also be considered as utility functions, $U(X,P(X))$.
+The principle of asserting numerical values for $P(X)$ in such a way as to maximize your prevision for your score is equivalent to acting in a decision problem so as to maximize your expected utility.
+
+\subsection{Brier \replaced{scoring rule}{score}}
 
@@
 
-The green surface represents the 2-simplex, i.e. the set of points such that $p_1+p_2+p_3=1$ for non-negative values of $p_1$, $p_2$ and $p_3$.
+The green surface \added{in Figure \ref{fig:simplex}} represents the 2-simplex, i.e. the set of points such that $p_1+p_2+p_3=1$ for non-negative values of $p_1$, $p_2$ and $p_3$.
 The triangle representing the simplex has sides of length $\sqrt{2}$ and its height is $\sqrt{6}/2$.
@@
 
-For every point inside this triangle $p_1+p_2+p_3=1$.
+For every point inside this triangle, $p_1+p_2+p_3=1$.
+
+\red{parei aqui}
 
@@
 
+\subsection{Logarithmic scoring rule}
+
+\subsection{Spherical scoring rule}
+
+\subsection{Calibration}
+
+Probability assertions are said to be well calibrated at the level of probability p if the observed proportion of all propositions that are assessed with probability $p$ equals $p$.
+
+A person's probability assertions are said to be well calibrated at the value p if the limiting frequency of occurrence of events that are assessed with probability $p$, equals $p$.
+
 \section{Example}
+
+\red{temos que descrever o que esta aqui (nao li essa secao)}
 
@@
 \section{Results}
+\label{sec::results}
 
-\subsection{First Division (S\'erie A)}
+We display only the results for the first division
+of the Brazilian football championship; the second
+division yielded similar results.
+There is a total of \red{xxxx} games and \red{xxxx}
+teams. \red{descrever mais alguma coisa sobre o campionato?}
 
-\begin{table}[h]
+\begin{table}[H]
 \begin{center}
@@
 
-\subsection{Second Division (S\'erie B)}
+%\begin{table}[h]
+%\begin{center}
+%\begin{tabular}{ccccc}
 
-\begin{table}[h]
-\begin{center}
-\begin{tabular}{ccccc}
+%\hline
+%Matchday & BB1 & $Mn-Dir_1$ & $Mn-Dir_2$ & $Mn-Dir_3$\\
+%\hline
+%\hline
+%1$^{st}$ & 7.267 & 8.003 & 8.131 & 8.263 \\
+%2$^{nd}$ & 5.633 & 6.073 & 6.119 & 6.057 \\
+%3$^{rd}$ & 7.183 & 7.086 & 7.384 & 7.183 \\
+%4$^{th}$ & 7.458 & 6.776 & 6.731 & 6.829 \\
+%5$^{th}$ & 5.246 & 5.492 & 5.494 & 5.414 \\
+%6$^{th}$ & 5.126 & 5.169 & 5.589 & 5.043 \\
+%7$^{th}$ & 5.837 & 5.033 & 4.939 & 4.897 \\
+%8$^{th}$ & 7.462 & 6.616 & 6.509 & 6.667 \\
+%9$^{th}$ & 8.223 & 7.520 & 7.733 & 7.671 \\
+%10$^{th}$ & 4.818 & 5.623 & 5.825 & 5.578 \\
+%\hline
+%Total & 118.00 & 117.68 & 119.33 & 117.70 \\
+%\hline
+%Mean & 0.6178 & 0.6161 & 0.6248 & 0.6162 \\
 
-\hline
-Matchday & BB1 & $Mn-Dir_1$ & $Mn-Dir_2$ & $Mn-Dir_3$\\
-\hline
-\hline
-1$^{st}$ & 7.267 & 8.003 & 8.131 & 8.263 \\
-2$^{nd}$ & 5.633 & 6.073 & 6.119 & 6.057 \\
-3$^{rd}$ & 7.183 & 7.086 & 7.384 & 7.183 \\
-4$^{th}$ & 7.458 & 6.776 & 6.731 & 6.829 \\
-5$^{th}$ & 5.246 & 5.492 & 5.494 & 5.414 \\
-6$^{th}$ & 5.126 & 5.169 & 5.589 & 5.043 \\
-7$^{th}$ & 5.837 & 5.033 & 4.939 & 4.897 \\
-8$^{th}$ & 7.462 & 6.616 & 6.509 & 6.667 \\
-9$^{th}$ & 8.223 & 7.520 & 7.733 & 7.671 \\
-10$^{th}$ & 4.818 & 5.623 & 5.825 & 5.578 \\
-\hline
-Total & 118.00 & 117.68 & 119.33 & 117.70 \\
-\hline
-Mean & 0.6178 & 0.6161 & 0.6248 & 0.6162 \\
+%\hline
+%\end{tabular}
+%\caption{Score of the ten first rounds and mean score per match after 191 matches}
+%\end{center}
+%\end{table}
 
-\hline
-\end{tabular}
-\caption{Score of the ten first rounds and mean score per match after 191 matches}
-\end{center}
-\end{table}
+%\begin{table}[h]
+%\begin{center}
+%\begin{tabular}{ccccc}
+%
+%\hline
+%BB1 & $Mn-Dir_1$ & $Mn-Dir_2$ & $Mn-Dir_3$\\
+%\hline
+%\hline
+%0.6011 & 0.6119 & 0.6159 & 0.6115\\
+%\hline
+%\multicolumn{4}{c}{Chance de gol historic mean (1998-2015): 0.5977}\\
+%\hline
+%\end{tabular}
+%\caption{First and Second Divisions means}
+%\end{center}
+%\end{table}
 
-\begin{table}[h]
-\begin{center}
-\begin{tabular}{ccccc}
+Figure \ref{fig::scores} displays the boxplots of the scores and proportion of errors of the predictive models considered.
+It also shows an horizontal line with the score of the trivial prediction $(1/3,1/3,1/3)$. 
+All methods have similar performance, and they are more accurate than the trivial prediction, displayed in the plots
+as an horizontal line.\footnote{None of the 95\% confidence intervals for the mean score contain the score given by the trivial prediction.}
 
-\hline
-BB1 & $Mn-Dir_1$ & $Mn-Dir_2$ & $Mn-Dir_3$\\
-\hline
-\hline
-0.6011 & 0.6119 & 0.6159 & 0.6115\\
-\hline
-\multicolumn{4}{c}{Chance de gol historic mean (1998-2015): 0.5977}\\
-\hline
-\end{tabular}
-\caption{First and Second Divisions means}
-\end{center}
-\end{table}
+Figure \ref{fig::entropy} presents the boxplots of the entropy of each prediction for the predictive models considered.\footnote{Recall
+that the entropy of a prediction $(p_1,p_2,p_3)$ is given by $- \sum_{i=1}^3 p_i \log{p_i}$} It shows that the predictions
+are typically more informative than $(1/3,1/3,1/3)$, but overall all methods yield similar entropies in average.
+
+We evaluate how reasonable
+predictions  by assessing the calibration of the methods considered,
+i.e., by evaluating how often events which have assigned probability $p$ (for each $0<p<1$) happen (Section \ref{sec::scoring}).
+If these probabilities are close to $p$, one concludes that the methods are well-calibrated. 
+Results are displayed in Figure \ref{fig::calibration}.
+Because we typically do not have several
+predictions with the same assigned probability $p$, we obtain the plot by smoothing the indicator function of whether
+a given event happened on  the assigned  probability of that event. The smoothing is done via smoothing splines 
+\cite{wahba}, with tuning parameters chosen by cross-validation.
+Because the curves obtain are close to the identity, we conclude that all methods are well-calibrate, except perhaps BB1, in which events with both low and high estimated probabilities happen more often
+than predicted.
+
+\begin{figure}[H]
+  \centering
+\includegraphics[page=1,scale=0.3]{futebolComparacaoModelosForPaper.pdf}
+\includegraphics[page=2,scale=0.3]{futebolComparacaoModelosForPaper.pdf}\\
+\includegraphics[page=3,scale=0.3]{futebolComparacaoModelosForPaper.pdf}
+\includegraphics[page=4,scale=0.3]{futebolComparacaoModelosForPaper.pdf}
+  \caption{Scores and proportion of errors of the various predictive methods. Horizontal line represents the score of the trivial prediction $(1/3,1/3,1/3)$.}
+  \label{fig::scores}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+\includegraphics[page=10,scale=0.3]{futebolComparacaoModelosForPaper.pdf}
+  \caption{Entropy of the predictions of the various methods. Horizontal line represents the entropy of the trivial prediction $(1/3,1/3,1/3)$.}
+  \label{fig::entropy}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+\includegraphics[page=5,scale=0.3]{futebolComparacaoModelosForPaper.pdf}
+\includegraphics[page=6,scale=0.3]{futebolComparacaoModelosForPaper.pdf}\\
+\includegraphics[page=7,scale=0.3]{futebolComparacaoModelosForPaper.pdf}
+\includegraphics[page=8,scale=0.3]{futebolComparacaoModelosForPaper.pdf}
+\includegraphics[page=9,scale=0.3]{futebolComparacaoModelosForPaper.pdf}
+  \caption{Calibration of the various predictive methods: estimates of occurrence frequency obtained by smoothing splines, with 95\% confidence bands. Black line is the identity $y=x$.}
+  \label{fig::calibration}
+\end{figure}
+
+\red{incluir envoltorio convexo para mostrar que probs estimadas sao relativamente parecidas, talvez colocar os 4, 5 exemplos com maiores envoltorios?}
 
 \section{Discussion}
+\label{sec::discussion}
+
+\red{talvez juntar com as conclusoes?}
+
 %De Finetti was a radical subjectivist and pragmatist about probability and did not believe that it even made sense to talk about credences as being ``accurate'' or ``inaccurate''. 
@@
 \section{Conclusions}
+\label{sec::conclusions}
+
+We compared the probabilistic predictions of three simple models with the ones provided by two more complex models for the second round of the 2014 Brazilian football championships of first and second divisions.
+According to standard scoring rules and other criteria here adopted to qualify the predictions, our results show that the predictive power of all models was quite similar.
+
+\added{This work thus indicates that while there has been a boom in the literature with the proposal of several
+ fancy and involved models, especially in the era
+ of big data, simple models
+ can many times do as well as their complex counterparts. This is many time
+ unnoticed by users of such methods, which
+leads to the overuse of  models that are hard to interpret and to implement, and that also require
+one to keep track of several covariates. This 
+phenomenon is \red{nao consegui ligar as ideias formalmente, nao sei se vale a pena mencionar algo assim}
+  ''But he isn't wearing anything at all!" Anderson's "The Emperor's New Clothes" \cite{emperor}.
+Although we have explored only models for
+football games,
+we believe the same extends to other fields as, for instance, \red{exemplos}}
+
+On the one hand, our findings appear as another supportive example of Ockham's razor but, on the other, \replaced{they pose}{poses} several questions about probabilistic prediction of sport events.
+\replaced{In particular, based on the fact that
+the models has similar performance, one may ask:}{We mention just a couple of them, raised by the similar performance of the considered models:}
+ is there an irreducible ``randomness'' or ``degree of unpredictability'' implicit in these events?
+Is this degree an indicator of how close is the championship being studied? \red{nao entendi bem a segunda pergunta!}
+\replaced{A suggestion to future research
+is to answer these questions by considering more championships and models, and  by comparing them using other scoring rules.}{To answer these questions we would have to consider more championships and models and compare them using other scoring rules, being a suggestion for further research.}
+\replaced{Another direction we would like to address is to test other weighting methods 
+in models 1 and 2 we propose, and to evaluate
+their impact on the predictive power of the resulting predictions.}{Also as future research we would like to test other weights and study their impact on the predictive power of models 1 and 2 here proposed.}
+
+%The most useful statement of the principle for scientists is
+%"when you have two competing theories that make exactly the same predictions, the simpler one is the better."
+
+%What to infer from known recorded measurements about the values of yet unrecorded measurements is the responsibility of each knowing person.
+%There is general agreement in evaluating the evidence that the measured observations provide for yet unmeasured experiences.
+%There have been controversies among very respected scientists regarding what conclusions are to be drawn from observations.
 
@@
 
+\bibitem{wahba}
+Wahba, G. Spline models for observational data.
+SIAM, Philadelphia, 1990.
+
+\bibitem{emperor}
+Andersen, H.  C. The emperor's new clothes. Genesis Publishing Pvt Ltd, 1987.
+
 \end{thebibliography}

### 2015-05-08 template.tex
Alteracoes gerais e sugestoes do Rafael

@@
 Bothered by such concerns, our goal was to answer the following question: is it possible, using a simple probabilistic model, to predict results of football matches better than more sophisticated or complex models?
-To answer this, we compared two sophisticated models \added{that consider several covariates} with simple multinomial-Dirichlet models that consider only the number of matches won, drawn or lost by each team as inputs.
+To answer this, we compared two sophisticated models that consider several covariates with simple multinomial-Dirichlet models that consider only the number of matches won, drawn or lost by each team as inputs.
 The models were tested for the second round of the Brazilian football championships of first and second divisions and compared using standard metrics or scoring rules.
-We also used other criteria such as the proportion of matches that were predicted ``correctly'' by each model and a measure of calibration, both explained in details below.
+We also used other criteria such as the proportion of matches that were predicted ``correctly'' by each model and a measure of calibration, both explained in detail below.
 According to the adopted criteria, the simple models showed a similar predictive performance to the complex ones.
 
-The predictions of the complex models used here as benchmarks are published on Internet websites for every matchday, and are treated by us as black-box models since we are not interested in how they were built or the assumptions on which they are based.
-We know that\footnote{One of the authors is responsible for one of these models and the other was described in a dissertation.} both models are based on the bivariate Poisson or Holgate distributions, and are able to predict the final score of a match given explanatory variables.\footnote{For more details see \cite{arruda2000}.}
-\deleted[remark={acho que essa parte nao eh tao simples de entender e nao eh vital para o artigo}]{Therefore, to estimate the probability that, for instance, the home team will win, the estimated model---the model estimated with available information---is simulated a given number of times and the proportion of simulated scores favoring the home team will be the predicted probability of the model.} \added{Both models output three probabilities for each match: the probability that the house team wins, the probability that
-the visitor wins, and the probability that there is a draw.} \red{usei a nomenclatura correta na frase anterior?}
-\replaced{Because both}{Knowing that both} models are based on an elaborate parametric model, they are suitable for the comparison we are proposing: simple versus complex models.
+The predictions of the complex models used here as benchmarks are published on Internet websites for every matchday, and are treated by us as black-box models since we are not specifically interested in how they were built or the assumptions on which they are based.
+We know that both models are based on the bivariate Poisson or Holgate distributions, and are able to predict the final score of a match given explanatory variables.\footnote{One of the authors is responsible for one of these models and the other was described in a dissertation, see \cite{arruda2000}.}
+Both models output three probabilities for each match: the probability that the home team wins, the probability that the away team wins, and the probability that there is a draw.
+Because both models are based on an elaborate parametric assumptions, they are suitable for the comparison we are proposing: simple versus complex models.\footnote{To be precise we would have to define what is a ``simple'' model and what is a ``complex'' model.
+Based on the opening quotations, one may say that the number of parameters defines the complexity of a model.
+This is not the exactly the definition we will use since we consider other criteria, like the interpretation of explanatory variables and mathematical structure of the statistical model.}
 
@@
 the verified event, once it has occurred, and chose the most used distances in the literature: Brier (\cite{brier1950}), logarithmic and spherical.
-\deleted{The total inaccuracy of each model is then defined as the sum of the point-wise scores of all its previsions.}
 
@@
 Section \ref{sec::results} reports the performance of the models predicting 380 matches comprising the second half of Brazilian championships of first and second divisions.
-In Section \ref{sec::discussion} we discuss the results, and Section \ref{sec::conclusions} closes with some remarks and proposals for future research.
-\red{talvez juntar as duas ultimas secoes?}
+In Section \ref{sec::remarks} we discuss the results and close with proposals for future research.
 
@@
 How can we fairly distinguish better-informed states of knowledge from more poorly informed states?
-\replaced{A way of doing this is to use proper scoring rules for evaluating states of uncertain knowledge.}{Using proper scoring rules for evaluating states of uncertain knowledge.}
-A scoring rule is a function of two variables (or vectors, matrices etc) that \replaced{assigns}{accords} a real number (score) 
-\replaced{to each
-possible outcome $X$ and its respective prevision value, $P(X)$.}{
-to each pair of numbers that could represent the value of $X$ and the prevision value $P(X)$.}
-\replaced{ It is maximum for each $x$ when $x=P(X)$, and is nonincreasing both as $x$ departs from $P(X)$ (for each $P(X)$) and as $P(X)$ departs from $x$ (for each $x$).}{It is maximum for each $x$ when $x=P(X)$, and nonincreasing as $x$ departs from $P(X)$ for each $P(X)$, and as $P(X)$ departs from $x$ for each $x$.
-} \added{Thus},
-the best score is achieved when knowledge of $X$ is asserted as the value of $X$ itself, whatever it might be.
-Most of the scoring rules \added{also} exhibit an arbitrary normalizing feature \added{such that} $S[x,P(X)]=0$ for each $x$.
+A way of doing this is to use proper scoring rules for evaluating states of uncertain knowledge, where 
+the score may be interpreted as a numerical measure of how inaccurate was the prevision.
 
-Although many functions satisfy the criteria for a scoring rule specified above, not every scoring rule \replaced{can}{would} be regarded as providing a fair assessment of the assertion $P(X)$.
-That is,
-not all scoring rules encourage honesty and accuracy in assessing numerical values for their   previsions.
+More precisely, a scoring rule is a function of two variables (or vectors, matrices etc) that assigns a real number (score) to each possible outcome $X$ and its respective prevision value, $P(X)$.
+It is maximum for each $x$ when $x=P(X)$, and is nonincreasing both as $x$ departs from $P(X)$ (for each $P(X)$) and as $P(X)$ departs from $x$ (for each $x$).
+Thus, the best score is achieved when knowledge of $X$ is asserted as the value of $X$ itself, whatever it might be.
+Most of the scoring rules also exhibit an arbitrary normalizing feature such as $S[x,P(X)]=0$ for each $x$.
+
+Although many functions satisfy the criteria for a scoring rule specified above, not every scoring rule can be regarded as providing a fair assessment of the assertion $P(X)$, that is, not all scoring rules encourage honesty and accuracy in assessing numerical values for their previsions.
 Those that do encourage a fair assessment are named \emph{proper scoring rules} \red{colocar referencia}.
 
-\added{Say a forecaster's uncertainty about $X$ is $P_0$.
-A proper scoring rule is a scoring rule $S$ such that the prevision value $P(X)$ that minimizes $E_{P_0}[S(X,P(X))]$ is $P_0$.
-} \replaced{In other words, if one receives a reward $S(x,P(x))$ when $x$ happens and if $S$ is a proper scoring rule, then the highest expected reward is obtained by reporting one's  true uncertainty about $X$}{Imagine one receives a reward of $S(\mathbf{r},i)$ if the $i$-th event occurs.} The use of a proper scoring rule \added{thus} encourages the forecaster to be honest \deleted{to maximize the expected reward}.
+Say a forecaster's uncertainty about $X$ is $P_0$. A proper scoring rule is a scoring rule $S$ such that the prevision value $P(X)$ that minimizes $E_{P_0}[S(X,P(X))]$ is $P_0$. 
+In other words, if one receives a reward $S(x,P(x))$ when $x$ happens and if $S$ is a proper scoring rule, then the highest expected reward is obtained by reporting one's  true uncertainty about $X$.
+The use of a proper scoring rule thus encourages the forecaster to be honest to maximize the expected reward.
+Moreover, this method leads automatically to an overall comparison between the outcomes of different personal evaluations concerned with the same totality of events.
+Therefore, the accumulated score may be considered a concrete measure of success of each forecaster or model.
 
-The scoring rule is constructed according to the basic idea that the resulting device should oblige each participant to express his true feelings, because any departure from his own personal probability results in a diminution of his own average score as he sees it.
-\red{esse paragrafo me parece um pouco redundante, serah que eh melhor tirar?}
-
-Moreover, this method leads automatically to an overall comparison between the outcomes of different personal evaluations concerned with the same totality of events.
-The accumulated loss is indeed a \replaced{truly?}{throughly} concrete measure of success.
-
-\added{In what follows, we describe in detais three proper scoring rules we use to asses the various models considered. We also 
-recall the concept of calibration.}
+In what follows, we describe in detail three proper scoring rules we use to asses the various models considered. 
+We also recall the concept of calibration.
 
@@
 
-\subsection{Brier \replaced{scoring rule}{score}}
+\subsection{Brier scoring rule}
 
@@
 
-The green surface \added{in Figure \ref{fig:simplex}} represents the 2-simplex, i.e. the set of points such that $p_1+p_2+p_3=1$ for non-negative values of $p_1$, $p_2$ and $p_3$.
+The green surface in Figure \ref{fig:simplex} represents the 2-simplex, i.e. the set of points such that $p_1+p_2+p_3=1$ for non-negative values of $p_1$, $p_2$ and $p_3$.
 The triangle representing the simplex has sides of length $\sqrt{2}$ and its height is $\sqrt{6}/2$.
 Drawing a similar equilateral triangle with height 1 and sides $2\sqrt{3}/3$, it is possible to represent all the points of the simplex.
-This new triangle is usually used to graphically display the predictions as internal points because the sum of the distances of every point inside it to each side is always one representing the probability of each event.
+This new triangle is used to graphically display the predictions as internal points because the sum of the distances of every point inside it to each side, representing the probability of each event, is always one.
 
@@
 \draw[-,thick] (-.45,1) -- (-.55,1);
+\draw[dashed,thick] (-.5,1) -- (0.57735,1);
+\draw[dashed,thick] (-.5,0) -- (0,0);
 
@@
 \end{figure}
-
-For every point inside this triangle, $p_1+p_2+p_3=1$.
 
@@
 
-Probability assertions are said to be well calibrated at the level of probability p if the observed proportion of all propositions that are assessed with probability $p$ equals $p$.
+Probability assertions are said to be well calibrated at the level of probability $p$ if the observed proportion of all propositions that are assessed with probability $p$ equals $p$.
 
-A person's probability assertions are said to be well calibrated at the value p if the limiting frequency of occurrence of events that are assessed with probability $p$, equals $p$.
+A person's probability assertions are said to be well calibrated at the value $p$ if the limiting frequency of occurrence of events that are assessed with probability $p$, equals $p$.
 
@@
 
-We display only the results for the first division
-of the Brazilian football championship; the second
+We display only the results for the first division of the Brazilian football championship; the second
 division yielded similar results.
-There is a total of \red{xxxx} games and \red{xxxx}
-teams. \red{descrever mais alguma coisa sobre o campionato?}
+Both divisions have 20 teams that play against each other twice (home and away) and the team with more points after all matches were played is declared champion.
+The last four are relegated to a minor division and, in first division, the first four play Copa Libertadores (South America champions league) and in second division the first four are promoted to first division.
+Therefore, in each championship there is a total of 380 matches, 190 in each round.
 
@@
 \hline
-1$^{st}$ &4.992 & 5.055 & 5.630 & 5.053 & 5.521 \\
-2$^{nd}$ &5.006 & 5.328 & 5.327 & 5.533 & 5.201 \\
-3$^{rd}$ &7.129 & 6.568 & 7.979 & 7.640 & 8.216 \\
-4$^{th}$ &5.941 & 5.782 & 6.513 & 6.848 & 6.564 \\
-5$^{th}$ &5.246 & 5.858 & 5.669 & 5.368 & 5.601 \\
-6$^{th}$ &5.584 & 5.095 & 6.055 & 6.112 & 6.033 \\
-7$^{th}$ &5.641 & 5.817 & 5.250 & 5.062 & 5.134 \\
-8$^{th}$ &6.112 & 6.710 & 6.315 & 6.673 & 6.348 \\
-9$^{th}$ &6.433 & 6.714 & 5.768 & 6.061 & 5.717 \\
-10$^{th}$ &4.912 & 4.620 & 6.019 & 6.115 & 6.010 \\
+1 &4.992 & 5.055 & 5.630 & 5.053 & 5.521 \\
+2 &5.006 & 5.328 & 5.327 & 5.533 & 5.201 \\
+3 &7.129 & 6.568 & 7.979 & 7.640 & 8.216 \\
+4 &5.941 & 5.782 & 6.513 & 6.848 & 6.564 \\
+5 &5.246 & 5.858 & 5.669 & 5.368 & 5.601 \\
 \hline
@@
 \end{tabular}
-\caption{Score of the ten first rounds and mean score per match after 190 matches}
+\caption{Score of the five first matchdays and mean score per match after 190 matches}
 \end{center}
@@
 
-We evaluate how reasonable
-predictions  by assessing the calibration of the methods considered,
-i.e., by evaluating how often events which have assigned probability $p$ (for each $0<p<1$) happen (Section \ref{sec::scoring}).
+We evaluate how reasonable \added{were the?} predictions by assessing the calibration of the methods considered, i.e., by evaluating how often events which have assigned probability $p$ (for each $0<p<1$) happen \added{or happened?} (Section \ref{sec::scoring}).
 If these probabilities are close to $p$, one concludes that the methods are well-calibrated. 
 Results are displayed in Figure \ref{fig::calibration}.
-Because we typically do not have several
-predictions with the same assigned probability $p$, we obtain the plot by smoothing the indicator function of whether
-a given event happened on  the assigned  probability of that event. The smoothing is done via smoothing splines 
-\cite{wahba}, with tuning parameters chosen by cross-validation.
-Because the curves obtain are close to the identity, we conclude that all methods are well-calibrate, except perhaps BB1, in which events with both low and high estimated probabilities happen more often
+Because we typically do not have several predictions with the same assigned probability $p$, we obtain the plot by smoothing the indicator function of whether a given event happened on  the assigned  probability of that event.
+The smoothing is done via smoothing splines \cite{wahba}, with tuning parameters chosen by cross-validation.
+Because the curves obtain \added{(ou we obtained?)} are close to the identity, we conclude that all methods are well-calibrated, except perhaps BB1, in which events with both low and high estimated probabilities happen more often
 than predicted.
@@
 
-\section{Discussion}
-\label{sec::discussion}
-
-\red{talvez juntar com as conclusoes?}
+\section{Final remarks}
+\label{sec::remarks}
 
@@
 
-It is possible to interpret the score as a numerical measure of how inaccurate was the 
-prevision.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Conclusions}
-\label{sec::conclusions}
-
 We compared the probabilistic predictions of three simple models with the ones provided by two more complex models for the second round of the 2014 Brazilian football championships of first and second divisions.
@@
 
-\added{This work thus indicates that while there has been a boom in the literature with the proposal of several
- fancy and involved models, especially in the era
- of big data, simple models
- can many times do as well as their complex counterparts. This is many time
- unnoticed by users of such methods, which
-leads to the overuse of  models that are hard to interpret and to implement, and that also require
-one to keep track of several covariates. This 
-phenomenon is \red{nao consegui ligar as ideias formalmente, nao sei se vale a pena mencionar algo assim}
-  ''But he isn't wearing anything at all!" Anderson's "The Emperor's New Clothes" \cite{emperor}.
-Although we have explored only models for
-football games,
-we believe the same extends to other fields as, for instance, \red{exemplos}}
+This work thus indicates that while there has been a boom in the literature with the proposal of several fancy and involved models, especially in the era of big data, simple models can many times do as well as their complex counterparts.
+This is often unnoticed by users of such methods, which leads to the overuse of models that are hard to interpret and to implement, and that also require one to keep track of several covariates.
+We would call this phenomenon the {\it king's nudity}\footnote{In allusion to Anderson's {\it The Emperor's New Clothes}, \cite{emperor}: ``But he isn't wearing anything at all!''.}, that is not, of course, always observed.
+In this spirit, since we have explored only the prediction of football matches, we would like to study if the the same extends to other fields such as, for instance, \red{exemplos} \red{Tentei aqui Rafael, veja o que acha.}
 
-On the one hand, our findings appear as another supportive example of Ockham's razor but, on the other, \replaced{they pose}{poses} several questions about probabilistic prediction of sport events.
-\replaced{In particular, based on the fact that
-the models has similar performance, one may ask:}{We mention just a couple of them, raised by the similar performance of the considered models:}
- is there an irreducible ``randomness'' or ``degree of unpredictability'' implicit in these events?
-Is this degree an indicator of how close is the championship being studied? \red{nao entendi bem a segunda pergunta!}
-\replaced{A suggestion to future research
-is to answer these questions by considering more championships and models, and  by comparing them using other scoring rules.}{To answer these questions we would have to consider more championships and models and compare them using other scoring rules, being a suggestion for further research.}
-\replaced{Another direction we would like to address is to test other weighting methods 
-in models 1 and 2 we propose, and to evaluate
-their impact on the predictive power of the resulting predictions.}{Also as future research we would like to test other weights and study their impact on the predictive power of models 1 and 2 here proposed.}
+If, on the one hand, our findings appear as another supportive example of Ockham's razor, on the other they pose several questions about probabilistic prediction of sport events.
+In particular, based on the fact that the models have similar performance, one may ask: is there an irreducible ``randomness'' or ``degree of unpredictability'' implicit in these events?
+Is this degree an indicator of how tight or leveled is the championship being studied?
+\red{ficou mais clara a segunda pergunta?
+Queria perguntar se a dificuldade de prever os resultados indica o quao disputado ou equilibrado \'e o campeonato.}
+
+A suggestion of future research is to answer these questions by considering more championships and models, and  by comparing them using other scoring rules.
+Another direction we would like to address is to test other weighting methods in models 1 and 2 here proposed, and to evaluate their impact on the predictive power of the resulting predictions.
 
@@
 
-\acknowledgments{Acknowledgments}
+%\acknowledgments{Acknowledgments}
 
-Main text.
+%Main text.
 
@@
 
-\authorcontributions{Author Contributions}
+%\authorcontributions{Author Contributions}
 
-Main text.
+%Main text.
 
@@
 
-\conflictofinterests{Conflicts of Interest}
+%\conflictofinterests{Conflicts of Interest}
 
-State any potential conflicts of interest here or ``The authors declare no conflict of interest''.
+%State any potential conflicts of interest here or ``The authors declare no conflict of interest''.
 
@@
 % Reference 1
-\bibitem{ref-journal}
-Lastname, F.; Author, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142-149.
+%\bibitem{ref-journal}
+%Lastname, F.; Author, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142-149.
 
 % Reference 2
-\bibitem{ref-book}
-Lastname, F.F.; Author, T. The title of the cited contribution. In {\em The Book Title}; Editor, F., Meditor, A., Eds.; Publishing House: City, Country, 2007; pp. 32-58.
+%\bibitem{ref-book}
+%Lastname, F.F.; Author, T. The title of the cited contribution. In {\em The Book Title}; Editor, F., Meditor, A., Eds.; Publishing House: City, Country, 2007; pp. 32-58.
 

### 2015-05-09 template.tex
alguns errinhos a menos; figura atualizada

@@
 
-\begin{table}[H]
-\begin{center}
-\begin{tabular}{cccccc}
-
-\hline
-Matchday & BB1 & BB2 & $Mn-Dir_1$ & $Mn-Dir_2$ & $Mn-Dir_3$\\
-\hline
-\hline
-1 &4.992 & 5.055 & 5.630 & 5.053 & 5.521 \\
-2 &5.006 & 5.328 & 5.327 & 5.533 & 5.201 \\
-3 &7.129 & 6.568 & 7.979 & 7.640 & 8.216 \\
-4 &5.941 & 5.782 & 6.513 & 6.848 & 6.564 \\
-5 &5.246 & 5.858 & 5.669 & 5.368 & 5.601 \\
-\hline
-Total & 111.04 & 111.32 & 115.45 & 115.36 & 115.29 \\
-\hline
-Mean & 0.5844 & 0.5859 & 0.6076 & 0.6072 & 0.6068 \\
-\hline
-\end{tabular}
-\caption{Score of the five first matchdays and mean score per match after 190 matches}
-\end{center}
-\end{table}
-
 %\begin{table}[h]
@@
 It also shows an horizontal line with the score of the trivial prediction $(1/3,1/3,1/3)$. 
-All methods have similar performance, and they are more accurate than the trivial prediction, displayed in the plots
-as an horizontal line.\footnote{None of the 95\% confidence intervals for the mean score contain the score given by the trivial prediction.}
-
-Figure \ref{fig::entropy} presents the boxplots of the entropy of each prediction for the predictive models considered.\footnote{Recall
-that the entropy of a prediction $(p_1,p_2,p_3)$ is given by $- \sum_{i=1}^3 p_i \log{p_i}$} It shows that the predictions
-are typically more informative than $(1/3,1/3,1/3)$, but overall all methods yield similar entropies in average.
-
-We evaluate how reasonable \added{were the?} predictions by assessing the calibration of the methods considered, i.e., by evaluating how often events which have assigned probability $p$ (for each $0<p<1$) happen \added{or happened?} (Section \ref{sec::scoring}).
-If these probabilities are close to $p$, one concludes that the methods are well-calibrated. 
-Results are displayed in Figure \ref{fig::calibration}.
-Because we typically do not have several predictions with the same assigned probability $p$, we obtain the plot by smoothing the indicator function of whether a given event happened on  the assigned  probability of that event.
-The smoothing is done via smoothing splines \cite{wahba}, with tuning parameters chosen by cross-validation.
-Because the curves obtain \added{(ou we obtained?)} are close to the identity, we conclude that all methods are well-calibrated, except perhaps BB1, in which events with both low and high estimated probabilities happen more often
-than predicted.
+According to all scoring rules, all methods have similar performance, and they are more accurate than the trivial prediction, displayed in the plots
+as an horizontal line.\footnote{None of the 95\% confidence intervals for the mean score contain the score given by the trivial prediction.} The Brier score the first five matchdays, as well as the total Brier score is also displayed
+in Table \ref{tab::brier}.
 
@@
 
+\begin{table}[H]
+\begin{center}
+\begin{tabular}{cccccc}
+\hline
+Matchday & BB1 & BB2 & $Mn-Dir_1$ & $Mn-Dir_2$ & $Mn-Dir_3$\\
+\hline
+\hline
+1 &4.992 & 5.055 & 5.630 & 5.053 & 5.521 \\
+2 &5.006 & 5.328 & 5.327 & 5.533 & 5.201 \\
+3 &7.129 & 6.568 & 7.979 & 7.640 & 8.216 \\
+4 &5.941 & 5.782 & 6.513 & 6.848 & 6.564 \\
+5 &5.246 & 5.858 & 5.669 & 5.368 & 5.601 \\
+\hline
+Total & 111.04 & 111.32 & 115.45 & 115.36 & 115.29 \\
+\hline
+Mean & 0.5844 & 0.5859 & 0.6076 & 0.6072 & 0.6068 \\
+\hline
+\end{tabular}
+\caption{Brier score of the five first matchdays and mean score per match after 190 matches.
+The score of the trivial prediction $(1/3,1/3,1/3)$ is 0.667.}
+\label{tab::brier}
+\end{center}
+\end{table}
+
+Figure \ref{fig::entropy} presents the boxplots of the entropy of each prediction for the predictive models considered.\footnote{Recall
+that the entropy of a prediction $(p_1,p_2,p_3)$ is given by $- \sum_{i=1}^3 p_i \log{p_i}$} 
+Because the entropy values are smaller than 1.09, 
+the plots shows that the predictions
+are typically more informative than $(1/3,1/3,1/3)$. Nevertheless, all methods yield similar entropies in average, that is,
+none of them seem to give more informative probabilities.
+
 \begin{figure}[H]
@@
 \end{figure}
+
+We evaluate how reasonable were the predictions by assessing the calibration of the methods considered, i.e., by evaluating how often events which have assigned probability $p$ (for each $0<p<1$) happened (Section \ref{sec::scoring}).
+If these probabilities are close to $p$, one concludes that the methods are well-calibrated. 
+Results are displayed in Figure \ref{fig::calibration}.
+Because we typically do not have several predictions with the same assigned probability $p$, we obtain the plot by smoothing the indicator function of whether a given event happened on  the assigned  probability of that event.
+The smoothing is done via smoothing splines \cite{wahba}, with tuning parameters chosen by cross-validation.
+Because the curves we obtained are close to the identity, we conclude that all methods are well-calibrated, except perhaps BB1, in which events with both low and high estimated probabilities happen more often
+than predicted.
 
@@
 \end{figure}
+
+We therefore conclude that all methods have similar predictive power, and none of them is more informative in average.
+Nevertheless, all methods yield better predictions than the non-informative vector of probabilities $(1/3,1/3,1/3)$, and they are well-calibrated.
 
@@
 We would call this phenomenon the {\it king's nudity}\footnote{In allusion to Anderson's {\it The Emperor's New Clothes}, \cite{emperor}: ``But he isn't wearing anything at all!''.}, that is not, of course, always observed.
-In this spirit, since we have explored only the prediction of football matches, we would like to study if the the same extends to other fields such as, for instance, \red{exemplos} \red{Tentei aqui Rafael, veja o que acha.}
+In this spirit, since we have explored only the prediction of football matches, we would like to study if the the same extends to other fields such as, for instance, \red{exemplos}
 
@@
 Is this degree an indicator of how tight or leveled is the championship being studied?
-\red{ficou mais clara a segunda pergunta?
-Queria perguntar se a dificuldade de prever os resultados indica o quao disputado ou equilibrado \'e o campeonato.}
 

### 2015-05-17 template.tex
figura adicionada nas analises; revisei secao sobre scoring rules

@@
 \usepackage{graphicx,subcaption}
+
+\usepackage{amssymb}
 
@@
 
-More precisely, a scoring rule is a function of two variables (or vectors, matrices etc) that assigns a real number (score) to each possible outcome $X$ and its respective prevision value, $P(X)$.
-It is maximum for each $x$ when $x=P(X)$, and is nonincreasing both as $x$ departs from $P(X)$ (for each $P(X)$) and as $P(X)$ departs from $x$ (for each $x$).
-Thus, the best score is achieved when knowledge of $X$ is asserted as the value of $X$ itself, whatever it might be.
+%More precisely, a scoring rule is a function of two variables (or vectors, matrices etc) that assigns a real number (score) to each possible outcome $X$ and its respective prevision value, $P(X)$.
+%It is maximum for each $x$ when $x=P(X)$, and is nonincreasing both as $x$ departs from $P(X)$ (for each $P(X)$) and as $P(X)$ departs from $x$ (for each $x$).
+%Thus, the best score is achieved when knowledge of $X$ is asserted as the value of $X$ itself, whatever it might be.
 Most of the scoring rules also exhibit an arbitrary normalizing feature such as $S[x,P(X)]=0$ for each $x$.
 
-Although many functions satisfy the criteria for a scoring rule specified above, not every scoring rule can be regarded as providing a fair assessment of the assertion $P(X)$, that is, not all scoring rules encourage honesty and accuracy in assessing numerical values for their previsions.
-Those that do encourage a fair assessment are named \emph{proper scoring rules} \red{colocar referencia}.
+%Although many functions satisfy the criteria for a scoring rule specified above, not every scoring rule can be regarded as providing a fair assessment of the assertion $P(X)$, that is, not all scoring rules encourage honesty and accuracy in assessing numerical values for their previsions.
+%Those that do encourage a fair assessment are named \emph{proper scoring rules} \cite{lad}.
 
-Say a forecaster's uncertainty about $X$ is $P_0$. A proper scoring rule is a scoring rule $S$ such that the prevision value $P(X)$ that minimizes $E_{P_0}[S(X,P(X))]$ is $P_0$. 
-In other words, if one receives a reward $S(x,P(x))$ when $x$ happens and if $S$ is a proper scoring rule, then the highest expected reward is obtained by reporting one's  true uncertainty about $X$.
-The use of a proper scoring rule thus encourages the forecaster to be honest to maximize the expected reward.
+%Say a forecaster's uncertainty about $X$ is $P_0$. A proper scoring rule is a scoring rule $S$ such that the prevision value $P(X)$ that minimizes $E_{P_0}[S(X,P(X))]$ is $P_0$. 
+%In other words, if one receives a reward $S(x,P(x))$ when $x$ happens and if $S$ is a proper scoring rule, then the highest expected reward is obtained by reporting one's  true uncertainty about $X$.
+%The use of a proper scoring rule thus encourages the forecaster to be honest to maximize the expected reward.
+%Moreover, this method leads automatically to an overall comparison between the outcomes of different personal evaluations concerned with the same totality of events.
+%Therefore, the accumulated score may be considered a concrete measure of success of each forecaster or model.
+
+More precisely, a scoring rule is a function of two variables (or vectors, matrices etc) that assigns a real number (score) to each possible outcome $X$ and its respective prevision value, $P_X$.
+That is, $P_X$ is the probability assigned to each possible
+outcome $X$.
+It is minimum for each $x$ when $P_X$ is such that $P_X(X=x)=1$, and is nondecreasing both as $x$ departs from $P_X$ (for each $P_X$) and as $P_X$ departs from $x$ (for each $x$).
+Thus, the best score (the smaller value of $S$) is achieved when knowledge of $X$ is asserted as the value of $X$ itself, whatever it might be.\footnote{A scoring rule can also be defined to be such that a \emph{large}
+value of $S$ indicates good predictions.} 
+%Most of the scoring rules also exhibit an arbitrary normalizing feature such as $S(x,P_X)=0$ for each $x$.
+
+Although many functions satisfy the criteria for a scoring rule specified above, not every scoring rule can be regarded as providing a fair assessment of the assertion $P_X$, that is, not all scoring rules encourage honesty and accuracy in assessing numerical values for their previsions.
+Those that do encourage a fair assessment are named \emph{proper scoring rules} \cite{lad}.
+
+Say a forecaster's uncertainty about $X$ is $P_0$. A proper scoring rule is a scoring rule $S$ such that the prevision value $P_X$ that minimizes $E_{P_0}[S(X,P_X)]$ is $P_0$. 
+In other words, if one receives a penalty $S(x,P_X)$ when $x$ happens and if $S$ is a proper scoring rule, then the lowest expected penalty is obtained by reporting one's  true uncertainty about $X$.
+The use of a proper scoring rule thus encourages the forecaster to be honest to minimize the expected penalty.
 Moreover, this method leads automatically to an overall comparison between the outcomes of different personal evaluations concerned with the same totality of events.
@@
 \subsection{Brier scoring rule}
+
+Let $P_X$ be a probability assignment for $X$.
+The Brier score is given by
+$$S(X;P_X)= \sum_{i}\mathbb{I}(X=x_i)(1- P_X(x_i))^2+\sum_{i}\mathbb{I}(X\neq x_i)P_X^2(x_i),$$
+where $\mathbb{I}$ is the indicator function.
 
@@
 
+We interpret the Brier score in the case only three events can happen, the case of a football match.
 The green surface in Figure \ref{fig:simplex} represents the 2-simplex, i.e. the set of points such that $p_1+p_2+p_3=1$ for non-negative values of $p_1$, $p_2$ and $p_3$.
@@
 \node[label={below:Draw}] at (1.1547,0) {};
-\node[label={above:Home looses}] at (0.57735,1) {};
+\node[label={above:Home loses}] at (0.57735,1) {};
 
@@
 \node[label={below:Draw}] at (1.1547,-0.05) {};
-\node[label={above:Home looses}] at (0.57735,1.05) {};
+\node[label={above:Home loses}] at (0.57735,1.05) {};
 
@@
 
-\red{parei aqui}
-
-\[p=(0.25,0.35,0.40)\]
-\[d^2=(0-0.25)^2+(0-0.35)^2+(1-0.40)^2=0.545\]
+The Brier score for the prediction $p=(0.25,0.35,0.40)$ when the home loses is therefore given by
+$d^2=(0-0.25)^2+(0-0.35)^2+(1-0.40)^2=0.545$. If the prediction was
+ $p=(0,0,1)$, the score would be 0 instead.
 
@@
 
+The logarithmic  score is given by
+$$S(X;P(X))=- \sum_{i}\mathbb{I}(X=x_i)\log(P(x_i)),$$
+
+This is the negative log likelihood
+of the event that occurred.
+
+The logarithmic score for the prediction $p=(0.25,0.35,0.40)$ when the home loses is therefore given by
+$-\log(0.4)\approx 0.91$. If the prediction was
+ $p=(0,0,1)$, the score would be $0$ instead.
+
 \subsection{Spherical scoring rule}
+
+The spherical score is given by
+$$S(X;P(X))=- \frac{1}{\sqrt{\sum_i P^2(x_i)}}\sum_{i}\mathbb{I}(X=x_i)P(x_i),$$
+
+This is the negative likelihood
+of the event that occurred, normalized by the square-root of the assigned probabilities.
+
+The logarithmic score for the prediction $p=(0.25,0.35,0.40)$ when the home loses is therefore given by
+$-0.4/\sqrt{0.25^2+0.35^2+0.40^2} \approx -0.68$. If the prediction was
+ $p=(0,0,1)$, the score would be $-1$ instead.
 
@@
 
-What's the probability that Gr\^emio looses: $p_{3h}=0.167$ or $p_{1a}=0.25$?
+What's the probability that Gr\^emio loses: $p_{3h}=0.167$ or $p_{1a}=0.25$?
 
@@
 
+In order to have a deeper understatement about the probabilities given by each method,
+Figure \ref{fig::probMandante} displays the estimated conditional probability that the home team wins given there is no draw.
+All models assign higher probabilities to the home team, a fact that illustrates that
+they capture \red{?the well known fact?} that it is easier for a team to win at home. 
+Morever, the outputs from the methods introduced in this paper
+are less dispersed than those from the other models used in the literature.
+
+\begin{figure}[H]
+  \centering
+\includegraphics[page=11,scale=0.4]{futebolComparacaoModelosForPaper.pdf}
+  \caption{Conditional probability that the home team wins given there is no draw. Horizontal line indicates a 50\%
+  probability.}
+  \label{fig::probMandante}
+\end{figure}
+
 We therefore conclude that all methods have similar predictive power, and none of them is more informative in average.
@@
 
+\bibitem{lad}
+Lad, F. Operational Subjective Statistical Methods: a mathematical, philosophical, and historical introduction. New York: Wiley, 1996.
+
 \end{thebibliography}

### 2015-06-26 template.tex
intoducao de secao benchmark models

@@
 \usepackage{graphicx,subcaption}
+\usepackage{amssymb}
+\usepackage{color}
+\usepackage{float}
 
-\usepackage{amssymb}
-
-\usepackage{color}
 \newcommand{\red}[1]{\textbf{\color{red} ***ATT*** #1}}
+\newcommand{\green}[1]{\textbf{\color{green} ***ATT*** #1}}
 
@@
 \definechangesauthor[name={Rafael}, color=blue]{raf}
+\setremarkmarkup{(#2)}
+\definechangesauthor[name={Luis}, color= magenta]{luis}
 \setremarkmarkup{(#2)}
@@
 % Contact information of the corresponding author (Add [2] after \corres if there are more than one corresponding author.)
-\corres{e-mail, telephone and fax number of the corresponding author.}
+\corres{marcio.alves.diniz@gmail.com, (+5516) 3351-9387.}
 
 % Abstract (Do not use inserted blank lines, i.e. \\)
-\abstract{This is the abstract section. The abstract should be one section and count less than 200 words.}
+\abstract{We create three simple multinomial-Dirichlet models and compare them to two well-known sophisticated statistical models for association football (soccer) predictions according to their performance in predicting the full-time results for the second round of the 2014 Brazilian first division championship.
+The predictive models are compared using three proper scoring rules, the proportion of errors and the calibration assessment.
+Our results show similar predictive performances for all the five methods, thus discouraging the use of overcomplicated models for match result forecast.}
 
 % Keywords: add 3 to 10 keywords
-\keyword{keyword; keyword; keyword}
+\keyword{predictive inference; probabilistic prediction; Bayesian inference; scoring rules}
 
@@
 {\it``Entities are not to be multiplied without necessity''}, but illustrates very well a principle that is not often followed by researchers, especially when building predictive models.
-This is true also in the literature of probabilistic sports predictions, particularly regarding models devoted to football predictions.
+This is true also in the literature of probabilistic sports predictions, particularly regarding models devoted to football or soccer\footnote{Henceforth, football.} predictions.
 
 Bothered by such concerns, our goal was to answer the following question: is it possible, using a simple probabilistic model, to predict results of football matches better than more sophisticated or complex models?
-To answer this, we compared two sophisticated models that consider several covariates with simple multinomial-Dirichlet models that consider only the number of matches won, drawn or lost by each team as inputs.
-The models were tested for the second round of the Brazilian football championships of first and second divisions and compared using standard metrics or scoring rules.
+To answer this, we compared two sophisticated models that consider multiple covariates with simple multinomial-Dirichlet models that consider only the number of matches won, tied or lost by each team as inputs.
+The models were tested for the second round of the Brazilian football championships of first division and compared using standard metrics or scoring rules.
 We also used other criteria such as the proportion of matches that were predicted ``correctly'' by each model and a measure of calibration, both explained in detail below.
@@
 
-The predictions of the complex models used here as benchmarks are published on Internet websites for every matchday, and are treated by us as black-box models since we are not specifically interested in how they were built or the assumptions on which they are based.
-We know that both models are based on the bivariate Poisson or Holgate distributions, and are able to predict the final score of a match given explanatory variables.\footnote{One of the authors is responsible for one of these models and the other was described in a dissertation, see \cite{arruda2000}.}
-Both models output three probabilities for each match: the probability that the home team wins, the probability that the away team wins, and the probability that there is a draw.
-Because both models are based on an elaborate parametric assumptions, they are suitable for the comparison we are proposing: simple versus complex models.\footnote{To be precise we would have to define what is a ``simple'' model and what is a ``complex'' model.
-Based on the opening quotations, one may say that the number of parameters defines the complexity of a model.
-This is not the exactly the definition we will use since we consider other criteria, like the interpretation of explanatory variables and mathematical structure of the statistical model.}
+The predictions of the two benchmark models were published on Internet websites before every matchday, and are treated by us as black-box models (BB1 and BB2). 
+We know that\footnote{One of the authors is responsible for one of these models and the other was described in a dissertation.
+See \cite{arruda2000}.} both models are based on Holgate bivariate Poisson regression considering as explanatory variables the home field advantage, attack and defense strength for each team, and provide the probabilities of all possible outcomes (home team wins, draws or loses) for each match.
+Because both models are based on elaborate parametric assumptions, they are suitable for the comparison we are proposing: simple versus complex models\footnote{To be precise we would have to define what is a ``simple'' model and what is a ``complex'' model.
+Based on the opening quotations, one may say that the number of parameters defines the complexity of a model, which is not exactly the definition we will use, since we consider other criteria, like the interpretation of explanatory variables and mathematical structure of the statistical model.}.
 
-There are several ways to score or classify predictions of categorical events that assume one out of three possible outcomes, like football matches.
+There are several ways to score or classify predictions of categorical events that assume one result out of a discrete set of mutually exclusive possible outcomes, like football matches.
 See \cite{constantinou} for a brief survey of such measures applied to football.
 We decided to score the previsions for each match in terms of their distances from the truth, i.e.
-the verified event, once it has occurred, and chose the most used distances in the literature: Brier (\cite{brier1950}), logarithmic and spherical.
+the verified event, once it has occurred, and chose the most used distances in the literature: Brier \cite{brier1950}, logarithmic and spherical.
 
@@
 Section \ref{sec::experimental} describes the proposed models, Section \ref{sec::scoring} presents the scoring rules and criteria used in this work to classify the models.
-Section \ref{sec::results} reports the performance of the models predicting 380 matches comprising the second half of Brazilian championships of first and second divisions.
+Section \ref{sec::results} reports the performance of the models predicting 190 matches comprising the second half of the Brazilian championship of first division.
 In Section \ref{sec::remarks} we discuss the results and close with proposals for future research.
@@
 
-\section{Experimental Section}
+\section{The models: theoretical background}
 \label{sec::experimental}
@@
 
-The black-box models used as benchmarks make their predictions available at \url{chancedegol.uol.com.br} and \url{www.previsaoesportiva.com.br}.
+In the literature, statistical models devoted to the prediction of
+football matches can be divided in two classes: models that make
+assumptions about the number of goals each team scores
+\citep{Maher82, Dixon97, Karlis2003} and models that make
+assumptions about the categorical final outcome (win, draw or defeat
+of the home team) \citep{Forrest2000, Koning2000, Brillinger2008,
+Brillinger2009}. For a discussion of these two approaches see
+\cite{Goddard2005}. The benchmark models considered in this work are
+part of the first approach, while the models proposed by us are part
+of the second one.
+
+In this section, we present the basic assumptions adopted by the benchmark models and 
+by the three proposed models. The predictions of the
+two benchmark models were published before each matchday at
+\url{http://chancedegol.uol.com.br} and
+\url{http://www.previsaoesportiva.com.br}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\red{nao olhei o resto desta secao}
+\subsection{Benchmark Models}
+\label{sec::Benchmark}
 
 \subsection{Multinomial-Dirichlet}
+\label{sec::Mn_Dir}
 
-Considering team $A$: the result of its next match may be considered a categorical random quantity (r.q.) that may assume only three modes; win ($W$), draw ($D$) or loss ($L$).
+We adopt a Bayesian approach to calculate the prediction probabilities of an upcoming match of team $T$ ($A$ or $B$) based on its past performance, i.e, the number of matches it has won, tied and lost.
 
-it is all wrong.
-
-If we denote the probability of $W$, by $\theta_1$, of $D$ by $\theta_2$ and of $L$ by $\theta_3=1-\theta_1-\theta_2$ where $\theta_1+\theta_2\leq 1$.
-
-The p.m.f of such r.q. is
-
+Let us consider the outcome of each match of team $T$ as a categorical random quantity $X$ that may assume only the values $1$, $2$, $3$, where $1$ means win ($W$), $2$ draw ($D$) and $3$ loss ($L$).
+Denoting by $\theta_1, \theta_2$ and $\theta_3$ ($\theta_3 = 1-\theta_1 - \theta_2$), the probabilities of win, draw and loss, respectively, the probability mass function of $X$ is
 \[
-P(X=x|\theta)=\theta_1^{I(x=W)}\theta_2^{I(x=D)}(1-\theta_1-\theta_2)^{I(x=L)}
+P(X=x | \boldsymbol{\theta}) = \theta_1^{\mathbb{I}_{\{1\}}(x)}
+\theta_2^{\mathbb{I}_{\{2\}}(x)}(1 - \theta_1 -
+\theta_2)^{{\mathbb{I}_{\{3\}}}(x)}, \qquad x \in \mathcal{X},
 \]
@@
 \noindent
-where $\mathcal{X}=\{W,D,L\}$ and $I(x=i)$ is the indicator function, that takes value 1 if $x$ equals $i= W, D, L$ and 0 otherwise; $\theta=\{(\theta_1,\theta_2)\in\Re^2:\theta_1+\theta_2\leq1 ~ \text{and} ~ \theta_i\geq0 ~ \text{for} ~ i=1, 2\}$
+where $\mathcal{X}=\{1,2,3\}$ is the support of $X$,
+$\mathbb{I}_{\{i\}}(x)$ is the indicator function that assumes the
+value 1 if $x$ equals $i$ and 0 otherwise, and $\boldsymbol{\theta}
+= (\theta_1, \theta_2)$ belogns to $\boldsymbol{\Theta} =
+\{(\theta_1,\theta_2)\in [0,1]^2: \theta_1+\theta_2 \leq 1 \}$, the 2-simplex.
 
-We may also call it multivariate Bernoulli r.q.
+Assuming that $n$ matches of team $T$, given $\boldsymbol{\theta}$, are i.i.d.
+quantities with the above categorical distribution, and denoting by $M_1$, $M_2$ and $M_3$ the number of matches won, tied or lost by team $T$, the random vector $(M_1, M_2, M_2)$ has multinomial distribution with parameters $n$ and $\boldsymbol{\theta}$ given by
+\[
+P(M_1=n_1,M_2=n_2,M_3=n_3| n, \boldsymbol{\theta})=
+\frac{n!}{n_1!n_2!(n-n_1-n_2)!}\theta_1^{n_1}\theta_2^{n_2}(1-\theta_1-\theta_2)^{n-n_1-n_2},
+\]
+\noindent 
+where $n_1 + n_2 + n_3 = n$.
 
-Assuming that the matches of team $A$, given $\theta$, are i.i.d. with categorical distribution, the sum of $n$ r.q.'s has multinomial distribution with parameters $\theta$ and $n$.
+Our goal is to compute the predictive posterior distribution of the
+upcoming match, $X_{n+1}$, that is,
+$P(X_{n+1}=x|M_1=n_1,M_2=n_2,M_3=n_3)$, $x\in\mathcal{X}$. Using
+Bayesian inference this probability can be easily computed as
+follows. Suppose that $\boldsymbol{\theta}$ has Dirichlet prior distribution
+with parameter $(\alpha_1,\alpha_2,\alpha_3)$, denoted
+$\mathcal{D}(\alpha_1,\alpha_2,\alpha_3)$, with density function
+\[
+\pi(\boldsymbol{\theta}|\alpha)=\frac{\Gamma(\alpha_1+\alpha_2+\alpha_3)}{\Gamma(\alpha_1)\Gamma(\alpha_2)\Gamma(\alpha_3)}\theta_1^{\alpha_1-1}\theta_2^{\alpha_2-1}(1-\theta_1-\theta_2)^{\alpha_3-1}
+\]
+\noindent for $\alpha_1$, $\alpha_2$, $\alpha_3 > 0$, then the
+posterior distribution of $\boldsymbol{\theta}$ is
+$\mathcal{D}(n_1+\alpha_1,n_2+\alpha_2,n_3+\alpha_3)$. Thus, the
+predictive distribution of $X_{n + 1}$ is given by the
+integral
+$$
+P(X_{n + 1} = x | M_1 = n_1, M_2 = n_2, M_3 = n_3) = \int_{\boldsymbol{\Theta}} P(X_{n
++ 1} = x | \boldsymbol{\theta}) \pi(\boldsymbol{\theta} | M_1 = n_1, M_2 = n_2, M_3
+= n_3) d\boldsymbol{\theta},
+$$
+which leads to the following probabilities of win, tie and loss:
+\begin{align*}
+P(X_{n+1} = 1 | M_1=n_1,M_2=n_2,M_3=n_3) &=
+\frac{n_1+\alpha_1}{n+\alpha}\\
+& \\
+P(X_{n+1} = 2 | M_1=n_1,M_2=n_2,M_3=n_3) &=
+\frac{n_2+\alpha_1}{n+\alpha} \\
+& \\
+P(X_{n+1} = 1 | M_1=n_1, M_2=n_2, M_3=n_3) &=
+\frac{n_3+\alpha_1}{n+\alpha}
+\end{align*}
+\noindent where $\alpha=\alpha_1+\alpha_2+\alpha_3$.
 
-\[
-P(M_1=n_1,M_2=n_2,M_3=n_3|\theta,n)=\]
-\[
-\frac{n!}{n_1!n_2!(n-n_1-n_2)!}\theta_1^{n_1}\theta_2^{n_2}(1-\theta_1-\theta_2)^{n-n_1-n_2}
-\]
+In this work we used the uniform prior on the 2-simplex, i.e. $\mathcal{D}(1,1,1)$. 
+This is not a restrictive prior because, since we predicted only the second round of the championship, the counts of the first round were used to update this prior---thanks to the conjugacy property of Dirichlet priors---and we may say that the actual prior we used is therefore the number of matches won, tied or lost by each team added by one.
+If we had started our predictions in the first round, this prior would not have given 
+a good predictive performance, but in this case we could have used team rankings such the ones provided by federations and leagues to assess a more realistic prior for each team instead.
 
-when $n_1+n_2+n_3=n$ and 0 otherwise, for non-negative integers $n_1$, $n_2$ and $n_3$.
+Before we explain and illustrate the proposed models with an example, we make two further remarks.
+The first one is that we will separately consider home and away games for each team. This will allow us to take into account the different performances under those conditions.
+The second remark is that the prediction of an upcoming match between $A$ and $B$ can be done using
+the past performance of either team $A$ or $B$.
+To solve this problem, a compromise between the two predictive distributions was adopted. 
+The next subsections \ref{sec::Mn_Dir1}, \ref{sec::Mn_Dir2} and \ref{sec::Mn_Dir3} present three different possible solutions.
 
-$n_1$ is the number of matches won, $n_2$ the matches drawn and $n_3=n-n_1-n_2$ the matches lost.
+\subsection{Model One: Multinomial-Dirichet $1$}
+\label{sec::Mn_Dir1}
 
-{\bf Summary}: under the given assumptions, the vector of matches won, drawn or lost by some team, has multinomial distribution with parameters $n$ and $\theta$.
+The model $Mn-Dir_1$ is defined as a mixture with equal weights of two Dirichlet distributions: the posterior distributions of teams $A$ and $B$. 
+Since teams $A$ and $B$ are the home and away teams, respectively, the two posterior distributions to be mixed are: (i) one considering only the matches $A$ played at home; (ii) another considering only the matches $B$ played away.
+The relevant past performance of teams $A$ and $B$ will be summarized, respectively, by the count vectors ${\bf h} = (h_1, h_2, h_3)$ (team $A$ at home) and ${\bf a} = (a_1, a_2, a_3)$ (team $B$ away), representing the numbers of matches won, tied and lost, respectively.
 
-Our goal is to compute:
+For instance, consider the match Gr\^emio versus Atl\'etico-PR played for matchday 20, at Gr\^emio stadium. Table \ref{tab:counts} displays the performances of both teams, home and away, after 19
+matches. The relevant vector of counts to be used are ${\bf h}=(h_1,h_2,h_3)=(6,2,1)$ and ${\bf a}=(a_1,a_2,a_3)=(2,3,4)$. 
+Therefore, Gr\^emio has a $\mathcal{D}(7,3,2)$ posterior for matches played at home and Atl\'etico has a $\mathcal{D}(3,4,5)$ posterior for matches played as visitor (recall that both priors were
+$\mathcal{D}(1,1,1)$).
 
-\[P(X_{n+1}=W|M_1=n_1,M_2=n_2,M_3=n_3)=p_1;\]
+\begin{table}[!h]
+\begin{center}
+\begin{tabular}{lccccccccc}
 
-\[P(X_{n+1}=D|M_1=n_1,M_2=n_2,M_3=n_3)=p_2;\] and
+\hline
+ & \multicolumn{3}{c}{Home} & \multicolumn{3}{c}{Away}& \multicolumn{3}{c}{Overall} \\
+\hline
+\hline
+Team & W & D & L & W & D & L & W & D & L\\
+\hline
+Gr\^emio & 6 & 2 & 1 & 3 & 2 & 5 & 9 & 4 & 6\\
+Atl\'etico-PR & 4 & 4 & 2 & 2 & 3 & 4 & 6 & 7 & 6\\
+\hline
+\end{tabular}
+\caption{Gr\^emio and Atl\'etico-PR counts after 19 matchdays (first round)}\label{tab:counts}
+\end{center}
+\end{table}
 
-\[P(X_{n+1}=L|M_1=n_1,M_2=n_2,M_3=n_3)=p_3.\]
+Thus, considering $X_{n + 1}$ the random outcome of this match with
+respect to the home team (Gr\^{e}mio), the predictive probabilities
+of $X_{n + 1}$ is obtained by equally weighting the two predictive
+distributions, resulting
+\begin{align*}
+P(X_{n+1}=1|{\bf h}, {\bf a}) &=
+\frac{1}{2}\left(\frac{h_1+\alpha_1}{h+\alpha}\right)+\frac{1}{2}\left(\frac{a_3+\alpha_3}{a+\alpha}\right)=0.5
+\\
+P(X_{n+1}=2|{\bf h}, {\bf a}) &=
+\frac{1}{2}\left(\frac{h_2+\alpha_2}{h+\alpha}\right)+\frac{1}{2}\left(\frac{a_2+\alpha_2}{a+\alpha}\right)\simeq0.2917, \\
+P(X_{n+1}=3|{\bf h}, {\bf a}) &= \frac{1}{2}
+\left(\frac{h_3+\alpha_3}{h+\alpha}\right)+\frac{1}{2}\left(\frac{a_1+\alpha_1}{a+\alpha}\right)\simeq0.2083.
+\end{align*}
+\noindent where $h=h_1+h_2+h_3$ and $a=a_1+a_2+a_3$.
 
-Using Bayesian inference these probabilities are easily computed: if the prior for $\theta$ is Dirichlet with parameter vector $(\alpha_1,\alpha_2,\alpha_3)$, i.e. its density function is
+\subsection{Model Two: Multinomial-Dirichlet $2$}
+\label{sec::Mn_Dir2}
 
-\[
-f(\theta|\alpha)=\frac{\Gamma(\alpha_1+\alpha_2+\alpha_3)}{\Gamma(\alpha_1)\Gamma(\alpha_2)\Gamma(\alpha_3)}\theta_1^{\alpha_1-1}\theta_2^{\alpha_2-1}(1-\theta_1-\theta_2)^{\alpha_3-1}
+The model $Mn-Dir_2$ is very similar to model $Mn-Dir_1$, but the
+weights used to mix the posterior distributions are not the same.
+Model $Mn-Dir_2$ weights the predictive distributions according to
+the team ranks just before the match is played. In the illustrative
+example, we know that after 19 matchdays, Gr\^emio was the $6^{th}$
+place and Atl\'etico-PR the $11^{th}$. Therefore, we shall consider
+the weights
+\[w_1 = \frac{1/6}{1/6+1/11}=0.647 ~ ~ ~ ~ ~\text{and} ~ ~ ~ w_2 = \frac{1/11}{1/6+1/11}=0.353\]
+\noindent for the Gr\^emio and Atl\'etico predicitive distributions,
+respectively. Thus, the winning probability for Gr\^emio is
+calculated as
+\[P(X_{n+1}= 1|{\bf h}, {\bf a})=0.647\left(\frac{h_1+\alpha_1}{h+\alpha}\right)+0.353\left(\frac{a_3+\alpha_3}{a+\alpha}\right)=0.525,\]
+\noindent and the other probabilities are computed similarly.
+
+\subsection{Model Three: Multinomial-Dirichlet 3}
+\label{sec::Mn_Dir3}
+
+Model $Mn-Dir_3$ is essentially different from the
+last two, because it combines the two different count vectors ${\bf
+h} = (h_1, h_2, h_3)$ and ${\bf a} = (a_1, a_2, a_3)$ instead of the
+predictive distributions. The main idea is to add the information
+contained in both vectors. From the point of view of team $A$, this can
+be done by considering a win of team $B$ as a ``negative event'' and a
+loss of team $B$ as a ``positive event'', while a draw is
+considered an ``indifferent event''. Applying this reasoning,
+we define the combined vector ${\bf c} = (c_1, c_2, c_3)$ by $c_1 =
+h_1 + a_3$, $h_2 = h_2 + a_2$, and $h_3 = h_3 + a_1$. Then, assuming that the vector ${\bf c} = (c_1, c_2, c_3)$, given $\boldsymbol{\theta}$, has multinomial distribution with parameters $n$ and
+$\boldsymbol{\theta}$, the predictive distribution for $X_{n + 1}$ can
+be obtained by the methods explained in subsection
+\ref{sec::Mn_Dir}.
+
+It is important to highlight that this model implicitly uses the strong assumption that, given $\boldsymbol{\theta}$, the matches of the home team, when playing in its stadium, and the matches of the visitor team, when playing away, are independent and identically distributed (reversing the result outcomes for team $B$).
+
+Considering the example above, the combined vector ${\bf c}$ is given by ${\bf c}=(c_1,c_2,c_3)=(10,5,3)$, which leads to a posterior $\mathcal{D}(11,6,4)$ when considering the prior $\mathcal{D}(1,1,1)$.
+The probability that Gr\^emio wins is therefore	
+\[P(X_{n+1}=1|{\bf c})=\frac{c_1+\alpha_1}{c+\alpha}\simeq0.524
 \]
@@
 \noindent
-for $\alpha_1$, $\alpha_2$, $\alpha_3 > 0$, then the posterior is Dirichlet with parameters $(n_1+\alpha_1,n_2+\alpha_2,n_3+\alpha_3)$, and hence
-
-\[p_1=P(X_{n+1}=W|M_1=n_1,M_2=n_2,M_3=n_3)=\frac{n_1+\alpha_1}{n+\alpha};\]
-
-\noindent
-where $n=n_1+n_2+n_3$ and $\alpha=\alpha_1+\alpha_2+\alpha_3$.
-
-Similarly
-
-\[p_2=P(X_{n+1}=D|M_1=n_1,M_2=n_2,M_3=n_3)=\frac{n_2+\alpha_2}{n+\alpha};\]
-
-\[p_3=P(X_{n+1}=L|M_1=n_1,M_2=n_2,M_3=n_3)=\frac{n_3+\alpha_3}{n+\alpha};\]
-
-Parameters of the prior: (1,1,1), uniform on the simplex.
+where $c=c_1+c_2+c_3$. The probabilities of drawing and losing are computed similarly.
 
@@
 
-More precisely, a scoring rule is a function of two variables (or vectors, matrices etc) that assigns a real number (score) to each possible outcome $X$ and its respective prevision value, $P_X$.
-That is, $P_X$ is the probability assigned to each possible
-outcome $X$.
+More precisely, a scoring rule is a function of two variables (or vectors, matrices etc) that assigns a real number (score) to each possible outcome of $X$ and its respective prevision value, $P_X$, i.e.
+$P_X$ is the probability assigned to each possible outcome of $X$.
 It is minimum for each $x$ when $P_X$ is such that $P_X(X=x)=1$, and is nondecreasing both as $x$ departs from $P_X$ (for each $P_X$) and as $P_X$ departs from $x$ (for each $x$).
-Thus, the best score (the smaller value of $S$) is achieved when knowledge of $X$ is asserted as the value of $X$ itself, whatever it might be.\footnote{A scoring rule can also be defined to be such that a \emph{large}
-value of $S$ indicates good predictions.} 
+Thus, the best score (the smaller value of the score) is achieved when knowledge of $X$ is asserted as the value of $X$ itself, whatever it might be\footnote{A scoring rule can also be defined to be such that a \emph{large} value of the score indicates good predictions.}.
 %Most of the scoring rules also exhibit an arbitrary normalizing feature such as $S(x,P_X)=0$ for each $x$.
@@
 The use of a proper scoring rule thus encourages the forecaster to be honest to minimize the expected penalty.
-Moreover, this method leads automatically to an overall comparison between the outcomes of different personal evaluations concerned with the same totality of events.
-Therefore, the accumulated score may be considered a concrete measure of success of each forecaster or model.
+Moreover, this method leads automatically to an overall comparison between the outcomes of different personal evaluations concerned with the same totality of events and, therefore, the accumulated score may be considered a concrete measure of success of each forecaster or model.
 
 In what follows, we describe in detail three proper scoring rules we use to asses the various models considered.
-We also recall the concept of calibration.
+We also recall the concept of calibration and propose a way to measure the calibration degree of each model.
 
-\red{parei de rever essa secao aqui}
-
-Proper scoring rules are devised so that no one previses (expects) that intrigue in falsely announcing some other number as $P(X)$ would be advantageous for achieving a better score.
-The particular scoring functions we study in the generic form $S(X,P(X))$ can also be considered as utility functions, $U(X,P(X))$.
-The principle of asserting numerical values for $P(X)$ in such a way as to maximize your prevision for your score is equivalent to acting in a decision problem so as to maximize your expected utility.
+%Proper scoring rules are devised so that no one previses (expects) that intrigue in falsely announcing some other number as $P(X)$ would be advantageous for achieving a better score.
+%The particular scoring functions we study in the generic form $S(X,P(X))$ can also be considered as utility functions, $U(X,P(X))$.
+%The principle of asserting numerical values for $P(X)$ in such a way as to maximize your prevision for your score is equivalent to acting in a decision problem so as to maximize your expected utility.
 
@@
 
-We interpret the Brier score in the case only three events can happen, the case of a football match.
+We interpret the Brier score in the case where one of three mutually exclusive outcomes happen, the case of a football match.
 The green surface in Figure \ref{fig:simplex} represents the 2-simplex, i.e. the set of points such that $p_1+p_2+p_3=1$ for non-negative values of $p_1$, $p_2$ and $p_3$.
 The triangle representing the simplex has sides of length $\sqrt{2}$ and its height is $\sqrt{6}/2$.
-Drawing a similar equilateral triangle with height 1 and sides $2\sqrt{3}/3$, it is possible to represent all the points of the simplex.
+Drawing a similar equilateral triangle with height 1 and sides $2\sqrt{3}/3$, it is possible to represent all points of the simplex.
 This new triangle is used to graphically display the predictions as internal points because the sum of the distances of every point inside it to each side, representing the probability of each event, is always one.
@@
 \node[label={below:Draw}] at (1.1547,-0.05) {};
-\node[label={above:Home loses}] at (0.57735,1.05) {};
+\node[label={above:Home loses}] at (0.57735,1.1) {};
 
@@
 
-The Brier score for the prediction $p=(0.25,0.35,0.40)$ when the home loses is therefore given by
-$d^2=(0-0.25)^2+(0-0.35)^2+(1-0.40)^2=0.545$. If the prediction was
- $p=(0,0,1)$, the score would be 0 instead.
+The Brier score for the prediction $P_X=(0.25,0.35,0.40)$, assuming the home team loses, is therefore given by $d^2=(0-0.25)^2+(0-0.35)^2+(1-0.40)^2=0.545$. 
+If the prediction was $P_X=(0,0,1)$, the score would be zero, the minimum for this rule.
+
+It is useful to consider the score of what we will call {\it trivial prediction}: $(1/3,1/3,1/3)$.
+This assessment will produce a Brier score of $2/3$, no matter what is the final result of the match, providing, thus, a threshold that a good model should consistently beat, meaning, for the Brier score, that the scores of its predictions should be smaller than $0.667$.
 
@@
 The logarithmic  score is given by
-$$S(X;P(X))=- \sum_{i}\mathbb{I}(X=x_i)\log(P(x_i)),$$
+$$S(X;P_X)=- \sum_{i}\mathbb{I}(X=x_i)\ln(P_X(x_i)),$$
 
-This is the negative log likelihood
-of the event that occurred.
+\noindent
+which is the negative log likelihood of the event that occurred.
 
-The logarithmic score for the prediction $p=(0.25,0.35,0.40)$ when the home loses is therefore given by
-$-\log(0.4)\approx 0.91$. If the prediction was
- $p=(0,0,1)$, the score would be $0$ instead.
+The logarithmic score for the prediction $P_X=(0.25,0.35,0.40)$, when the home team loses is therefore 
+$-\ln(0.4)\approx 0.91$. 
+If the prediction was $P_X=(0,0,1)$, the score would be zero, once again the minimum of this rule.
+For the logarithmic score, the trivial prediction gives a score of approximately $1.098$.
 
@@
 The spherical score is given by
-$$S(X;P(X))=- \frac{1}{\sqrt{\sum_i P^2(x_i)}}\sum_{i}\mathbb{I}(X=x_i)P(x_i),$$
+$$S(X;P_X)=- \frac{1}{\sqrt{\sum_i P_X^2(x_i)}}\sum_{i}\mathbb{I}(X=x_i)P_X(x_i),$$
 
-This is the negative likelihood
-of the event that occurred, normalized by the square-root of the assigned probabilities.
+\noindent
+which is the negative likelihood of the event that occurred, normalized by the square-root of the sum of the assigned squared probabilities.
 
-The logarithmic score for the prediction $p=(0.25,0.35,0.40)$ when the home loses is therefore given by
-$-0.4/\sqrt{0.25^2+0.35^2+0.40^2} \approx -0.68$. If the prediction was
- $p=(0,0,1)$, the score would be $-1$ instead.
+The spherical score for the prediction $P_X=(0.25,0.35,0.40)$, assuming the home team loses, is given by
+$-0.4/\sqrt{0.25^2+0.35^2+0.40^2} \approx -0.68$.
+If the prediction was $P_X=(0,0,1)$, the score would be $-1$ instead and, for this rule, the trivial prediction results in a score of approximately $-0.577$.
 
-\subsection{Calibration}
+\subsection{Calibration and proportion of errors}
+\label{sec::calib}
 
+Besides scoring rules, there are other criteria used to assess the quality of different predictions. Here we explore two of them.
+
+The first one is the proportion of errors made by the model or assessor. This is simply the proportion of mistakes made when considering the highest probability assessment.
+More precisely, the proportion of errors of a given prediction $P_X$ is defined by
+$$\frac{1}{n}\sum_{j=1}^n \mathbb{I}\left(X_j \neq \arg \max_{x} P_X(x_{j})\right),$$
+where $X_j$ is the outcome of the $j$-th match and $P_X(x_{j})$ is the probability attributed to result $x\in\mathcal{X}=\{1,2,3\}$ for the $j$-th match.
+
+The second concept we use is that of calibration \cite{Dawid}.
 Probability assertions are said to be well calibrated at the level of probability $p$ if the observed proportion of all propositions that are assessed with probability $p$ equals $p$.
 
-A person's probability assertions are said to be well calibrated at the value $p$ if the limiting frequency of occurrence of events that are assessed with probability $p$, equals $p$.
+Because we typically do not have several predictions with the same assigned probability $p$, we obtain a plot by smoothing (i.e., regressing) the indicator function of whether a given result happened as a function of the probability assigned for that result.
+That is, we estimate the probability that a event occurs given its assigned probability.
+%, that is, we regress  
+%$$\{ \mathbb{I}_{\{i\}}(X_j) \}_{j=1,\ldots,n;i=1,2,3} \mbox{ over } \{P_X(x_j)\}_{j=1,\ldots,n;i=1,2,3}$$
+% for each event $A_i$, i.e., each possible outcome of each match
+%that occurred.
+The smoothing is done via smoothing splines \cite{wahba}, with tuning parameters chosen by cross-validation.
 
-\section{Example}
-
-\red{temos que descrever o que esta aqui (nao li essa secao)}
-
-Gr\^emio $\times$ Atl\'etico-PR (Matchday 20), at Gr\^emio.
-
-\begin{table}[h]
-\begin{center}
-\begin{tabular}{lccccccccc}
-
-\hline
- & \multicolumn{3}{c}{Home} & \multicolumn{3}{c}{Away}& \multicolumn{3}{c}{Overall} \\
-\hline
-\hline
-Team & W & D & L & W & D & L & W & D & L\\
-\hline
-Gr\^emio & 6 & 2 & 1 & 3 & 2 & 5 & 9 & 4 & 6\\
-Atl\'etico-PR & 4 & 4 & 2 & 2 & 3 & 4 & 6 & 7 & 6\\
-\hline
-\end{tabular}
-\caption{Gr\^emio and Atl\'etico-PR counts after 19 matchdays (first round)}
-\end{center}
-\end{table}
-
-$h_1$=number of matches won by Gr\^emio when playing home
-
-$h_2$=number of matches drawn by Gr\^emio when playing home
-
-$h_3$=number of matches lost by Gr\^emio when playing home
-
-\
-
-$(h_1,h_2,h_3)=(6,2,1)$
-
-\[
-p_{1h}=\frac{h_1+\alpha_1}{h+\alpha}=\frac{6+1}{9+3}=\frac{7}{12}=0.583\]
-
-\[
-p_{2h}=\frac{h_2+\alpha_2}{h+\alpha}=\frac{2+1}{9+3}=\frac{3}{12}=0.25\]
-
-\[
-p_{3h}=\frac{h_3+\alpha_3}{h+\alpha}=\frac{1+1}{9+3}=\frac{2}{12}=0.167\]
-
-$a_1$=number of matches won by Atl\'etico-PR when playing away
-
-$a_2$=number of matches drawn by Atl\'etico-PR when playing away
-
-$a_3$=number of matches lost by Atl\'etico-PR when playing away
-
-\
-
-$(a_1,a_2,a_3)=(3,2,5)$
-
-\[
-p_{1a}=\frac{a_1+\alpha_1}{h+\alpha}=\frac{2+1}{9+3}=\frac{3}{12}=0.25\]
-
-\[
-p_{2a}=\frac{a_2+\alpha_2}{h+\alpha}=\frac{3+1}{9+3}=\frac{4}{12}=0.333\]
-
-\[
-p_{3a}=\frac{a_3+\alpha_3}{h+\alpha}=\frac{4+1}{9+3}=\frac{5}{12}=0.417\]
-
-What's the probability that Gr\^emio wins: $p_{1h}=0.583$ or $p_{3a}=0.417$?
-
-What's the probability of a draw: $p_{2h}=0.25$ or $p_{2a}=0.333$?
-
-What's the probability that Gr\^emio loses: $p_{3h}=0.167$ or $p_{1a}=0.25$?
-
-Three ways of combining these probabilities are proposed: (I) a mixture with equal weights to both teams;
-
-\[
-\frac{1}{2}\times p_{1h}+\frac{1}{2}\times p_{3a}=\frac{1}{2}\times0.583+\frac{1}{2}\times0.417=0.5
-\]
-
-\noindent
-is the probability that Gr\^emio wins.
-
-\[
-\frac{1}{2}\times p_{2h}+\frac{1}{2}\times p_{2a}=\frac{1}{2}\times0.25+\frac{1}{2}\times0.333=0.2917
-\]
-
-\noindent
-is the probability of a draw.
-
-\[
-\frac{1}{2}\times p_{3h}+\frac{1}{2}\times p_{1a}=\frac{1}{2}\times0.167+\frac{1}{2}\times0.25=0.2083
-\]
-
-\noindent
-is the probability that Atl\'etico wins.
-
-(II) a mixture with weights (inversely) proportional to the teams rank before the match; 
-after 19 matchdays, Gr\^emio was the $6^{th}$ place and Atl\'etico-PR the $11^{th}$:
-
-\[w_1 = \frac{1/6}{1/6+1/11}=0.647 ~ ~ ~ ~ ~ w_2 = \frac{1/11}{1/6+1/11}=0.353\]
-
-\[
-w_1\times p_{1h}+w_2\times p_{3a}=0.647\times0.583+0.353\times0.417=0.525 (\text{Gr\^emio wins})
-\]
-
-\[
-w_1\times p_{2h}+w_2\times p_{2a}=0.647\times0.25+0.353\times0.333=0.279 (\text{draw})
-\]
-
-\[
-w_1\times p_{1h}+w_2\times p_{3a}=0.647\times0.167+0.353\times0.25=0.196 (\text{Atl\'etico wins})
-\]
-
-(III) combine the counts to generate one prediction:
-
-$(h_1,h_2,h_3)=(6,2,1)$ and $(a_1,a_2,a_3)=(2,3,4)$ $\Rightarrow$ $(c_1,c_2,c_3)=(10,5,3)$
-
-$c_1=h_1+a_3 \Rightarrow$ number of matches won by Gr\^emio playing home plus matches lost by Atl\'etico playing away.
-
-\[\frac{c_1+\alpha_1}{c+\alpha}=\frac{10+1}{18+3}=0.524
-\]
-
-\[\frac{c_2+\alpha_3}{c+\alpha}=\frac{5+1}{18+3}=0.286
-\]
-
-\[\frac{c_3+\alpha_3}{c+\alpha}=\frac{3+1}{18+3}=0.190
-\]
-
-\noindent
-where $c=c_1+c_2+c_3$, $c_2=h_2+a_2$ and $c_3=h_3+a_1$.
-
-Final result: Gr\^emio 1 $\times$ 0 Atl\'etico-PR
-
-\begin{table}[h]
-\begin{center}
-\begin{tabular}{ccccc}
-
-\hline
-Model & Gr\^emio & Draw & Atl\'etico-PR & Score \\
-\hline
-\hline
-BB1 & 0.505 & 0.263 & 0.232 & 0.368 \\
-BB2 & 0.55 & 0.27 & 0.18 & 0.308 \\
-$Mn-Dir_1$ & 0.50 & 0.292 & 0.208 & 0.379 \\
-$Mn-Dir_2$ & 0.525 & 0.279 & 0.196 & 0.342\\
-$Mn-Dir_3$ & 0.524 & 0.286 & 0.190 & 0.345\\
-\hline
-\end{tabular}
-%\caption{Score of the ten first rounds and mean score per match after 190 matches}
-\end{center}
-\end{table}
+%A person's probability assertions are said to be well calibrated at the value $p$ if the limiting frequency of occurrence of events that are assessed with probability $p$, equals $p$.
 
@@
 
-We display only the results for the first division of the Brazilian football championship; the second
-division yielded similar results.
-Both divisions have 20 teams that play against each other twice (home and away) and the team with more points after all matches were played is declared champion.
+We display only the results for the first division of the Brazilian football championship; 
+we also analyzed the results for the second division, which yield similar conclusions.
+Both divisions have 20 teams that play against each other twice (home and away) and the team with more points after all matches are played is declared champion.
 The last four are relegated to a minor division and, in first division, the first four play Copa Libertadores (South America champions league) and in second division the first four are promoted to first division.
@@
 
-Figure \ref{fig::scores} displays the boxplots of the scores and proportion of errors of the predictive models considered.
-It also shows an horizontal line with the score of the trivial prediction $(1/3,1/3,1/3)$. 
+Figure~\ref{fig::scores} displays the boxplots of the scores and proportion of errors of the predictive models considered.
+%It also shows an horizontal line with the score of the trivial prediction.
 According to all scoring rules, all methods have similar performance, and they are more accurate than the trivial prediction, displayed in the plots
-as an horizontal line.\footnote{None of the 95\% confidence intervals for the mean score contain the score given by the trivial prediction.} The Brier score the first five matchdays, as well as the total Brier score is also displayed
+as an horizontal line\footnote{None of the 95\% confidence intervals for the mean score contain the score given by the trivial prediction.}. The mean scores and their standard errors are displayed
 in Table \ref{tab::brier}.
@@
 \begin{center}
-\begin{tabular}{cccccc}
+\begin{tabular}{ccccccc}
 \hline
-Matchday & BB1 & BB2 & $Mn-Dir_1$ & $Mn-Dir_2$ & $Mn-Dir_3$\\
+Score & BB1 & BB2 & $Mn-Dir_1$ & $Mn-Dir_2$ & $Mn-Dir_3$ & Trivial \\
 \hline
 \hline
-1 &4.992 & 5.055 & 5.630 & 5.053 & 5.521 \\
-2 &5.006 & 5.328 & 5.327 & 5.533 & 5.201 \\
-3 &7.129 & 6.568 & 7.979 & 7.640 & 8.216 \\
-4 &5.941 & 5.782 & 6.513 & 6.848 & 6.564 \\
-5 &5.246 & 5.858 & 5.669 & 5.368 & 5.601 \\
-\hline
-Total & 111.04 & 111.32 & 115.45 & 115.36 & 115.29 \\
-\hline
-Mean & 0.5844 & 0.5859 & 0.6076 & 0.6072 & 0.6068 \\
+Brier &0.58 (0.02) & 0.59 (0.02)& 0.61 (0.02)& 0.61 (0.02) & 0.61  (0.02) & 0.67 \\
+Logarithmic & 0.98 (0.03) & 0.99 (0.03) & 1.02 (0.03)  & 1.02 (0.03)  & 1.02 (0.03) & 1.10  \\
+Spherical &  -0.64 (0.02)& -0.64 (0.02)& -0.62 (0.02)& -0.63 (0.02)& -0.63 (0.02)& -0.58\\
 \hline
 \end{tabular}
-\caption{Brier score of the five first matchdays and mean score per match after 190 matches.
-The score of the trivial prediction $(1/3,1/3,1/3)$ is 0.667.}
+\caption{Mean scores and their standard errors for 190 matches of first division.}
 \label{tab::brier}
@@
 that the entropy of a prediction $(p_1,p_2,p_3)$ is given by $- \sum_{i=1}^3 p_i \log{p_i}$}
-Because the entropy values are smaller than 1.09, 
-the plots shows that the predictions
-are typically more informative than $(1/3,1/3,1/3)$. Nevertheless, all methods yield similar entropies in average, that is,
-none of them seem to give more informative probabilities.
+Since the entropy values are smaller than 1.09, the plots show that the predictions
+are typically more informative than the trivial prediction. Nevertheless, all methods yielded similar entropies in average, that is,
+none of them seem to provide more informative probabilities.
 
@@
 
-We evaluate how reasonable were the predictions by assessing the calibration of the methods considered, i.e., by evaluating how often events which have assigned probability $p$ (for each $0<p<1$) happened (Section \ref{sec::scoring}).
+We also evaluated how reasonable were the predictions by assessing the calibration of the methods considered, i.e., by evaluating how often events which have assigned probability $p$ (for each $0<p<1$) happened (Section \ref{sec::calib}).
 If these probabilities are close to $p$, one concludes that the methods are well-calibrated.
 Results are displayed in Figure \ref{fig::calibration}.
-Because we typically do not have several predictions with the same assigned probability $p$, we obtain the plot by smoothing the indicator function of whether a given event happened on  the assigned  probability of that event.
-The smoothing is done via smoothing splines \cite{wahba}, with tuning parameters chosen by cross-validation.
-Because the curves we obtained are close to the identity, we conclude that all methods are well-calibrated, except perhaps BB1, in which events with both low and high estimated probabilities happen more often
+Because the curves we obtained are close to the identity ($45^{\text{o}}$ line), we conclude that all methods are well-calibrated, except perhaps BB1, in which events with both low and high estimated probabilities happen more often
 than predicted.
 
-\begin{figure}[H]
-  \centering
+In order to have a deeper understanding about the probabilities
+given by each method, Figure \ref{fig::probMandante} displays the
+estimated conditional probability that the home team wins assuming
+the match will not be a tie.
+All models assign higher probabilities to the home team, showing that they capture the well known fact known as home advantage, peculiar in football matches and in other sport competitions \cite{Pollard86, Clarke95, Nevill99}.
+Morever, the outputs from the methods introduced in this paper are
+less dispersed than those from the other models used in the
+literature.
+
+\begin{figure}[H] \centering
 \includegraphics[page=5,scale=0.3]{futebolComparacaoModelosForPaper.pdf}
@@
 \includegraphics[page=9,scale=0.3]{futebolComparacaoModelosForPaper.pdf}
-  \caption{Calibration of the various predictive methods: estimates of occurrence frequency obtained by smoothing splines, with 95\% confidence bands. Black line is the identity $y=x$.}
+\caption{Calibration of the various predictive methods: estimates of
+occurrence frequency obtained by smoothing splines, with 95\%
+confidence bands. Black line is the identity $y=x$.}
 \label{fig::calibration}
@@
 
-In order to have a deeper understatement about the probabilities given by each method,
-Figure \ref{fig::probMandante} displays the estimated conditional probability that the home team wins given there is no draw.
-All models assign higher probabilities to the home team, a fact that illustrates that
-they capture \red{?the well known fact?} that it is easier for a team to win at home. 
-Morever, the outputs from the methods introduced in this paper
-are less dispersed than those from the other models used in the literature.
-
-\begin{figure}[H]
-  \centering
+\begin{figure}[H] \centering
 \includegraphics[page=11,scale=0.4]{futebolComparacaoModelosForPaper.pdf}
-  \caption{Conditional probability that the home team wins given there is no draw. Horizontal line indicates a 50\%
-  probability.}
+\caption{Conditional probability that the home team wins given there
+is no draw. Horizontal line indicates a 50\% probability.}
 \label{fig::probMandante}
@@
 We therefore conclude that all methods have similar predictive power, and none of them is more informative in average.
-Nevertheless, all methods yield better predictions than the non-informative vector of probabilities $(1/3,1/3,1/3)$, and they are well-calibrated.
-
-\red{incluir envoltorio convexo para mostrar que probs estimadas sao relativamente parecidas, talvez colocar os 4, 5 exemplos com maiores envoltorios?}
+Nevertheless, all methods yielded better predictions than the trivial prediction, and they are well-calibrated.
 
@@
 
-We compared the probabilistic predictions of three simple models with the ones provided by two more complex models for the second round of the 2014 Brazilian football championships of first and second divisions.
-According to standard scoring rules and other criteria here adopted to qualify the predictions, our results show that the predictive power of all models was quite similar.
+%In the statistical literature, football prediction models can be divided in two main approaches: (i) modeling the number of goals \citep{Maher82, Dixon97, Karlis2003} and (ii) modeling the final outcome (win, draw or lose) of the matches \citep{Forrest2000, Koning2000, Brillinger2008, Brillinger2009}.
+For a discussion of these two approaches see \cite{Goddard2005}.
+Although our benchmark models were here defined as complex, we can find much more elaborate models in the literature, hindering the estimation and prediction processes.
+Among them, we can cite those based on modeling the match as a stochastic process evolving through time \citep{Dixon98, Volf2009, Titman2015}, those allowing for the team performance parameters to
+change along the season \citep{Rue2000, Crowder2002, Owen2011, Koopman2015} and those modeling dependence between number of goals by means of bivariate count distributions \citep{Dixon97, Karlis2003, McHale2007, McHale2011}.
 
-This work thus indicates that while there has been a boom in the literature with the proposal of several fancy and involved models, especially in the era of big data, simple models can many times do as well as their complex counterparts.
-This is often unnoticed by users of such methods, which leads to the overuse of models that are hard to interpret and to implement, and that also require one to keep track of several covariates.
-We would call this phenomenon the {\it king's nudity}\footnote{In allusion to Anderson's {\it The Emperor's New Clothes}, \cite{emperor}: ``But he isn't wearing anything at all!''.}, that is not, of course, always observed.
-In this spirit, since we have explored only the prediction of football matches, we would like to study if the the same extends to other fields such as, for instance, \red{exemplos}
+%Although the benchmark models were here considered complex models, we can find in the literature much more elaborate models, hindering the estimation and prediction process. 
+%Among those, we can cite those based on modeling the match as a stochastic process evolving through time \citep{Dixon98, Volf2009, Titman2015}, those allowing for the team performance parameters to change along the season \citep{Rue2000, Crowder2002, Owen2011, Koopman2015} and those modeling dependence between number of goals by means of bivariate count distributions \citep{Dixon97, Karlis2003, McHale2007, McHale2011}.
+
+According to standard scoring rules and other criteria here adopted to qualify the predictions, our findings show that the predictive power of the three simple models was quite similar to the benchmark models.
+%We compared the probabilistic predictions of three simple models with the ones provided by two more complex models for the second round of the 2014 Brazilian football championships of first and second divisions.
+This work thus indicates that while there has been a boom in the literature with the proposal of several fancy and involved models, especially in the era of big data, simple models can many times do
+as well as their complex counterparts.
+
+This is often unnoticed by users of such methods, which leads to the overuse of models that are
+hard to interpret and to implement, and that also require one to keep track of several covariates. We would call this phenomenon the {\it king's nudity}\footnote{In allusion to Anderson's {\it The
+Emperor's New Clothes}, \cite{emperor}: ``But he isn't wearing anything at all!''.}, that is not, of course, always observed. 
+In this spirit, since we have explored only the prediction of football matches, we would like to study if the same extends to other fields such as, for instance, weather or economics forecasts.
 
@@
 A suggestion of future research is to answer these questions by considering more championships and models, and by comparing them using other scoring rules. 
-Another direction we would like to address is to test other weighting methods in models 1 and 2 here proposed, and to evaluate their impact on the predictive power of the resulting predictions.
+Another direction we would like to address is to test other weighting methods in models 1 and 2 here
+proposed, and to evaluate their impact on the predictive power of the resulting predictions.
 
-%The most useful statement of the principle for scientists is
-%"when you have two competing theories that make exactly the same predictions, the simpler one is the better."
+Once more we would like to stress that, when trying to answer all these questions, one must remember perhaps the most practical statement of Ockham's razor: ``when you have two competing theories that make exactly the same predictions, the simpler one is the better.''
+However, what to infer from known recorded measurements about the values of yet unrecorded measurements is the responsibility of each knowing person.
+There is general agreement in evaluating the evidence that measured observations provide for yet unmeasured experiences, but there have been controversies among very respected scientists regarding what conclusions are to be drawn from observations.
 
-%What to infer from known recorded measurements about the values of yet unrecorded measurements is the responsibility of each knowing person.
-%There is general agreement in evaluating the evidence that the measured observations provide for yet unmeasured experiences.
-%There have been controversies among very respected scientists regarding what conclusions are to be drawn from observations.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+\bibitem{Brillinger2008}
+Brillinger, D. R. Modelling game outcomes of the Brazilian 2006
+series A championship as ordinal-valued. {\em Brazilian Journal of Probability and Statistics} {\bf 2008}, {\em 22}, 89-104.
+
+\bibitem{Brillinger2009}
+Brillinger, D. R. An analysis of Chinese Super League partial
+results. {\em Science in China Series A} {\bf 2009}, {\em 52},
+1139-1151.
+
 \bibitem{constantinou}
-Constantinou, A. and Fenton, N. E. Evaluating the Predictive Accuracy of Association Football Forecasting Systems. Unpublished paper.
+Constantinou, A.
+and Fenton, N.
+E.
+Solving the problem of inadequate scoring rules for assessing probabilistic football forecast models.
+{\em Journal of Quantitative Analysis in Sports} {\bf 2012}, {\em 8}, manuscript 1418.
 
-\bibitem{wahba}
-Wahba, G. Spline models for observational data.
-SIAM, Philadelphia, 1990.
+\bibitem{Clarke95}
+Clarke, S. R.; Norman, J. N. Home ground advantage of individual clubs in English soccer. {\em Journal of the Royal Statistical Society - Series D} {\bf 1995} ,
+{\em 44}, 509-521.
+
+\bibitem{Crowder2002} Crowder, M.; Dixon, M.; Ledford, A.; Robinson, M. Dynamic modelling and prediction of English
+Football League matches for betting. {\em Journal of the Royal
+Statistical Society - Series D} {\bf 2002}, {\em 51}, 157-168.
+
+\bibitem{Dawid} Dawid, A. P. The well-calibrated Bayesian. 
+{\em Journal of the American Statistical Association} {\em 1982}, {\em 77}, 605-610.
+
+\bibitem{Dixon97} Dixon, M. J.; Coles, S. C. Modelling association football scores and inefficiencies in the football betting market. {\em Applied Statistics} {\bf 1997}, {\em 46}, 265-280.
+
+\bibitem{Dixon98} Dixon, M. J.; Robinson, M. E. A Birth Process Model for Association Football Matches. {\em Journal of the Royal Statistical Society - Series D}
+{\bf 1998}, {\em 47}, 523-538.
 
@@
 
+\bibitem{Forrest2000} Forrest, D.; Simmons, R. Making up the results: The work
+of the football pools panel, 1963-1997. {\em Journal of the Royal Statistical Society - Series D} {\bf 2000}, {\em 49}, 253-260.
+
+\bibitem{Goddard2005}
+Goddard, J. Regression models for forecasting goals and match
+results in association football. {\em International Journal of
+Forecasting} {\bf 2005}, {\em 21}, 331-340.
+
+\bibitem{Karlis2003}
+Karlis, D.; Ntzoufras, I. Analysis of sports data by using bivariate
+Poisson models. {\em Journal of the Royal Statistical Society - Series D} {\bf 2003}, {\em 52}, 381-393.
+
+\bibitem{Koning2000}
+Koning, R. H. . Balance in competition in Dutch soccer. {\em Journal of the Royal Statistical Society - Series D} {\bf 2000}, {\em 49}, 419-431.
+
+\bibitem{Koopman2015}
+Koopman, S. J.; Lit, Rutger. A dynamic bivariate Poisson model for
+analysing and forecasting match results in the English Premier
+League. {\em Journal of the Royal Statistical Society - Series A}
+{\bf 2015}, {\em 178}, 167-186.
+
 \bibitem{lad}
-Lad, F. Operational Subjective Statistical Methods: a mathematical, philosophical, and historical introduction. New York: Wiley, 1996.
+Lad, F. {\it Operational Subjective Statistical Methods: a mathematical,
+philosophical, and historical introduction}. New York: Wiley, 1996.
+
+\bibitem{Maher82}
+Maher, M. J. Modelling association football scores. {\em Statistica Neerlandica} {\bf 1982}, {\em 36}, 109-118.
+
+\bibitem{McHale2007}
+McHale, I.; Scarf, P. Modelling soccer matches using bivariate
+discrete distributions with general dependence structure. {\em
+Statistica Neerlandica} {\bf 2007}, {\em 61}, 432-445.
+
+\bibitem{McHale2011}
+McHale, I.; Scarf, P. Modelling the dependence of goals scored by
+opposing teams in international soccer matches. {\em Statistical
+Modelling} {\bf 2011}, {\em 11}, 219-236.
+
+\bibitem{Nevill99}
+Nevill, A. M.; Holder, R. L. Home advantage in sport. {\em Sports
+Medicine} {\bf 1999}, {\em 28}, 221-236.
+
+\bibitem{Owen2011}
+Owen, A. Dynamic Bayesian forecasting models of football match
+outcomes with estimation of the evolution variance parameter. {\em
+IMA Journal of Management Mathematics} {\bf 2011}, {\em 22}, 99-113.
+
+\bibitem{Pollard86}
+Pollard, R. Home advantage in soccer: a retrospective analysis. {\em Journal of Sports Sciences} {\bf 1986}, {\em 4}, 237-248.
+
+\bibitem{Rue2000}
+Rue, H.; Salvesen, O. Prediction and Retrospective Analysis of
+Soccer Matches in a League. {\em Journal of the Royal Statistical
+Society - Series D} {\bf 2000}, {\em 49}, 399-418.
+
+\bibitem{Titman2015}
+Titman, A. C.; Costain, D. A.; Ridall, P. G.; Gregory, K. Joint
+modelling of goals and bookings in association football. {\em
+Journal of the Royal Statistical Society - Series A} {\bf 2015},
+{\em 178}, 659-683.
+
+\bibitem{Volf2009}
+Volf, P. A random point process model for the score in sport
+matches. {\em IMA Journal of Management Mathematics} {\bf 2009},
+{\em 20}, 121-131.
+
+\bibitem{wahba}
+Wahba, G. Spline models for observational data. SIAM, Philadelphia,
+1990.
 

### 2015-06-30 template.tex
secao 3 revisada

@@
-%  LaTeX support: latex@mdpi.com
+%  LaTeX support: latex@mdpi.com\textbf{}
 %  In case you need support, please attach any log files that you could have, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).
@@
 
-How can we fairly distinguish better-informed states of knowledge from more poorly informed states?
-A way of doing this is to use proper scoring rules for evaluating states of uncertain knowledge, where
-the score may be interpreted as a numerical measure of how inaccurate was the prevision.
+	How can we fairly rank the various predictive models?
+	A way of doing this is by using proper scoring rules, where
+	the score may be interpreted as a numerical measure of how inaccurate was a given probabilistic prediction.
 
-%More precisely, a scoring rule is a function of two variables (or vectors, matrices etc) that assigns a real number (score) to each possible outcome $X$ and its respective prevision value, $P(X)$.
-%It is maximum for each $x$ when $x=P(X)$, and is nonincreasing both as $x$ departs from $P(X)$ (for each $P(X)$) and as $P(X)$ departs from $x$ (for each $x$).
-%Thus, the best score is achieved when knowledge of $X$ is asserted as the value of $X$ itself, whatever it might be.
-Most of the scoring rules also exhibit an arbitrary normalizing feature such as $S[x,P(X)]=0$ for each $x$.
-
-%Although many functions satisfy the criteria for a scoring rule specified above, not every scoring rule can be regarded as providing a fair assessment of the assertion $P(X)$, that is, not all scoring rules encourage honesty and accuracy in assessing numerical values for their previsions.
-%Those that do encourage a fair assessment are named \emph{proper scoring rules} \cite{lad}.
-
-%Say a forecaster's uncertainty about $X$ is $P_0$. A proper scoring rule is a scoring rule $S$ such that the prevision value $P(X)$ that minimizes $E_{P_0}[S(X,P(X))]$ is $P_0$.
-%In other words, if one receives a reward $S(x,P(x))$ when $x$ happens and if $S$ is a proper scoring rule, then the highest expected reward is obtained by reporting one's  true uncertainty about $X$.
-%The use of a proper scoring rule thus encourages the forecaster to be honest to maximize the expected reward.
-%Moreover, this method leads automatically to an overall comparison between the outcomes of different personal evaluations concerned with the same totality of events.
-%Therefore, the accumulated score may be considered a concrete measure of success of each forecaster or model.
-
-More precisely, a scoring rule is a function of two variables (or vectors, matrices etc) that assigns a real number (score) to each possible outcome of $X$ and its respective prevision value, $P_X$, i.e.
-$P_X$ is the probability assigned to each possible outcome of $X$.
-It is minimum for each $x$ when $P_X$ is such that $P_X(X=x)=1$, and is nondecreasing both as $x$ departs from $P_X$ (for each $P_X$) and as $P_X$ departs from $x$ (for each $x$).
-Thus, the best score (the smaller value of the score) is achieved when knowledge of $X$ is asserted as the value of $X$ itself, whatever it might be\footnote{A scoring rule can also be defined to be such that a \emph{large} value of the score indicates good predictions.}.
+	Formally, let $X$ be a random variable indicating
+	the result of a given match. Hence, $X$ assumes a value in $\{1,2,3\}$. Moreover, let $P$ denote one's probabilistic prediction
+	about $X$, i.e., $P$ is such that $\sum_{x=1}^3P(X=x)=1$ and
+    $P(X=x)\geq0$ for all $x$ in $\{1,2,3\}$.
+	A scoring rule is a function 
+	that assigns a real number (score) $S(x,P)$ to each combination $(x,P)$, where $x$ denotes each possible outcome of the match.
+	For a given $x$ in $\{1,2,3\}$, the score  $S(x,P)$ is minimum when $P$ is degenerate distribution on $x$, i.e., when $P(X=x)=1$.  
+	Thus, the best score (i.e., the score with the smallest value) is achieved when the probabilistic prediction for the outcome of the game is a degenerate  distribution
+  on the observed outcome of that match, i.e., a perfect prediction.\footnote{A scoring rule can also be defined to be such that a \emph{large} value of the score indicates good forecasts.}
 	%Most of the scoring rules also exhibit an arbitrary normalizing feature such as $S(x,P_X)=0$ for each $x$.
 
-Although many functions satisfy the criteria for a scoring rule specified above, not every scoring rule can be regarded as providing a fair assessment of the assertion $P_X$, that is, not all scoring rules encourage honesty and accuracy in assessing numerical values for their previsions.
-Those that do encourage a fair assessment are named \emph{proper scoring rules} \cite{lad}.
+	Although many functions satisfy the criteria for a scoring rule specified above, 
+	not all scoring rules encourage honesty and accuracy in assessing numerical values for their predictions.
+	Those that do encourage a fair assessment are named \emph{proper scoring rules} \cite{lad}, which we describe in the sequence.
 
-Say a forecaster's uncertainty about $X$ is $P_0$. A proper scoring rule is a scoring rule $S$ such that the prevision value $P_X$ that minimizes $E_{P_0}[S(X,P_X)]$ is $P_0$.
-In other words, if one receives a penalty $S(x,P_X)$ when $x$ happens and if $S$ is a proper scoring rule, then the lowest expected penalty is obtained by reporting one's  true uncertainty about $X$.
-The use of a proper scoring rule thus encourages the forecaster to be honest to minimize the expected penalty.
-Moreover, this method leads automatically to an overall comparison between the outcomes of different personal evaluations concerned with the same totality of events and, therefore, the accumulated score may be considered a concrete measure of success of each forecaster or model.
+	Say a model's probabilistic prediction for $X$ is $P^*.$ A proper scoring rule is a scoring rule $S$ such that the probabilistic prediction $P$ that minimizes 
+	$$E_{P^*}[S(X,P)]=\sum_{x=1}^3 S(x,P)P^*(X=x)$$
+	 is $P^*$  itself.
+	In other words, if one imagines 
+	a penalty $S(x,P)$ is received 
+	when $x$ happens then, 
+	if $S$ is a proper scoring rule, the lowest expected penalty is obtained by reporting the model's  uncertainty about $X$, $P^*$.
+	The use of a proper scoring rule thus encourages the forecaster to use $P^*$
+	as his probabilistic prediction for the outcome of the game, $X$, rather than some other quantity. 
+	%Moreover, this method automatically leads to an overall comparison between the outcomes of different personal evaluations concerned with the same totality of events and, therefore, the accumulated score may be considered a concrete measure of success of each model.
 
@@
 
-Let $P_X$ be a probability assignment for $X$.
-The Brier score is given by
-$$S(X;P_X)= \sum_{i}\mathbb{I}(X=x_i)(1- P_X(x_i))^2+\sum_{i}\mathbb{I}(X\neq x_i)P_X^2(x_i),$$
+	Let $P$ be a probabilistic prediction  for $X$.
+	The Brier score for a given outcome $x\in\{1,2,3\}$ is given by
+	$$S(x,P)= \sum_{i=1}^3\mathbb{I}(x=i)(1- P(X=i))^2+\sum_{i=1}^3\mathbb{I}(x\neq i)P^2(X=i),$$
 	where $\mathbb{I}$ is the indicator function.
@@
 			\end{tikzpicture}
-\caption{Bi-dimensional simplex (green surface): area of possible predictions}\label{fig:simplex}
+			\caption{Bi-dimensional simplex (green surface): area of possible forecasts}\label{fig:simplex}
 		\end{center}
@@
 	Drawing a similar equilateral triangle with height 1 and sides $2\sqrt{3}/3$, it is possible to represent all points of the simplex.
-This new triangle is used to graphically display the predictions as internal points because the sum of the distances of every point inside it to each side, representing the probability of each event, is always one.
+	This new triangle is used to graphically display the forecast as a internal point because the sum of the distances of every point inside it to each side, representing the probability of each event, is always one.
 
@@
 
-The Brier score for the prediction $P_X=(0.25,0.35,0.40)$, assuming the home team loses, is therefore given by $d^2=(0-0.25)^2+(0-0.35)^2+(1-0.40)^2=0.545$. 
-If the prediction was $P_X=(0,0,1)$, the score would be zero, the minimum for this rule.
+	The Brier score for the probabilistic prediction
+	$$P(X=1)=0.25, P(X=2)=0.35, P(X=3)=0.40,$$ 
+	assuming the home team loses, is therefore given by $d^2=(0-0.25)^2+(0-0.35)^2+(1-0.40)^2=0.545$. 
+	On the other hand, the prediction $P(X=3)=1$ achieves score  zero, the minimum for this rule.
 
-It is useful to consider the score of what we will call {\it trivial prediction}: $(1/3,1/3,1/3)$.
+	It is useful to consider the score of what we will call {\it trivial prediction}:
+	$$P(X=1)=1/3, P(X=2)=1/3, P(X=3)=1/3.$$
 	This assessment will produce a Brier score of $2/3$, no matter what is the final result of the match, providing, thus, a threshold that a good model should consistently beat, meaning, for the Brier score, that the scores of its predictions should be smaller than $0.667$.
@@
 	The logarithmic  score is given by
-$$S(X;P_X)=- \sum_{i}\mathbb{I}(X=x_i)\ln(P_X(x_i)),$$
+	$$S(x,P)=- \sum_{i=1}^3\mathbb{I}(x=i)\ln(P(X=i)),$$
 
@@
 
-The logarithmic score for the prediction $P_X=(0.25,0.35,0.40)$, when the home team loses is therefore 
+	The logarithmic score for the prediction 
+		$$P(X=1)=0.25, P(X=2)=0.35, P(X=3)=0.40,$$ 
+		 when the home team loses is therefore 
 	$-\ln(0.4)\approx 0.91$. 
-If the prediction was $P_X=(0,0,1)$, the score would be zero, once again the minimum of this rule.
-For the logarithmic score, the trivial prediction gives a score of approximately $1.098$.
+	On the other hand, the prediction $P(X=3)=1$ achieves score zero, once again the minimum of this rule.
+	Moreover, for the logarithmic score, the trivial prediction gives a score of approximately $1.098$.
 
@@
 	The spherical score is given by
-$$S(X;P_X)=- \frac{1}{\sqrt{\sum_i P_X^2(x_i)}}\sum_{i}\mathbb{I}(X=x_i)P_X(x_i),$$
+	$$S(x,P)=- \frac{1}{\sqrt{\sum_{i=1}^3 P^2(X=i)}}\sum_{i=1}^3\mathbb{I}(x=x_i)P(X=i),$$
 
@@
 
-The spherical score for the prediction $P_X=(0.25,0.35,0.40)$, assuming the home team loses, is given by
+	The spherical score for the prediction 
+		$$P(X=1)=0.25, P(X=2)=0.35, P(X=3)=0.40,$$ 
+		 assuming the home team loses, is given by
 	$-0.4/\sqrt{0.25^2+0.35^2+0.40^2} \approx -0.68$.
-If the prediction was $P_X=(0,0,1)$, the score would be $-1$ instead and, for this rule, the trivial prediction results in a score of approximately $-0.577$.
+	On the other hand, the prediction $P(X=3)=1$ achieves score  $-1$ instead and, for this rule, the trivial prediction results in a score of approximately $-0.577$.
 
@@
 	The first one is the proportion of errors made by the model or assessor. This is simply the proportion of mistakes made when considering the highest probability assessment.
-More precisely, the proportion of errors of a given prediction $P_X$ is defined by
-$$\frac{1}{n}\sum_{j=1}^n \mathbb{I}\left(X_j \neq \arg \max_{x} P_X(x_{j})\right),$$
-where $X_j$ is the outcome of the $j$-th match and $P_X(x_{j})$ is the probability attributed to result $x\in\mathcal{X}=\{1,2,3\}$ for the $j$-th match.
+	More precisely, the proportion of errors of a given probabilistic prediction $P$ is defined by
+	$$\frac{1}{n}\sum_{j=1}^n \mathbb{I}\left(X_j \neq \arg \max_{x \in \{1,2,3\}} P(X_j=x)\right),$$
+	where $X_j$ is the outcome of the $j$-th match.
 
@@
 
-%De Finetti used what is called the Brier score, which is just the (squared) Euclidean distance — i.e., the sum of the squared differences between credences and (the 0/1 numerical correlates of) truth values.
+	%De Finetti used what is called the Brier score, which is just the (squared) Euclidean distance ?
+i.e., the sum of the squared differences between credences and (the 0/1 numerical correlates of) truth values.
 

### 2015-07-03 template.tex
Seção 2.2 revista

@@
 \definechangesauthor[name={Rafael}, color=blue]{raf}
+\setremarkmarkup{(#2)}
+\definechangesauthor[name={Danilo}, color= violet]{danilo}
 \setremarkmarkup{(#2)}
@@
 
-	We adopt a Bayesian approach to calculate the prediction probabilities of an upcoming match of team $T$ ($A$ or $B$) based on its past performance, i.e, the number of matches it has won, tied and lost.
+	We adopt a Bayesian approach to calculate the prediction probabilities of an upcoming match of \added[id=danilo]{a} team \replaced[id=danilo]{$t$}{$T$} \deleted[id = danilo]{($A$ or $B$)} based on its past performance, i.e\added[id=danilo]{.}, the number of matches it has won, tied and lost.
 
-	Let us consider the outcome of each match of team $T$ as a categorical random quantity $X$ that may assume only the values $1$, $2$, $3$, where $1$ means win ($W$), $2$ draw ($D$) and $3$ loss ($L$).
+	Let us consider the outcome of \replaced[id=danilo]{a given}{each} match of team \replaced[id=danilo]{$t$}{$T$} as a categorical random quantity $X$ that may assume only the values $1$ \added[id=danilo]{(if team $t$ wins)}, $2$ \added[id=danilo]{(if a draw occurs)}, $3$ \added[id=danilo]{(if team $t$ loses)}, \deleted[id=danilo]{where $1$ means win ($W$), $2$ draw ($D$) and $3$ loss ($L$)}.
 	Denoting by $\theta_1, \theta_2$ and $\theta_3$ ($\theta_3 = 1-\theta_1 - \theta_2$), the probabilities of win, draw and loss, respectively, the probability mass function of $X$ is
@@
 	value 1 if $x$ equals $i$ and 0 otherwise, and $\boldsymbol{\theta}
-	= (\theta_1, \theta_2)$ belogns to $\boldsymbol{\Theta} =
+	= (\theta_1, \theta_2)$ \replaced[id=danilo]{belongs}{belogns} to $\boldsymbol{\Theta} =
 	\{(\theta_1,\theta_2)\in [0,1]^2: \theta_1+\theta_2 \leq 1 \}$, the 2-simplex.
 
-	Assuming that $n$ matches of team $T$, given $\boldsymbol{\theta}$, are i.i.d.
-quantities with the above categorical distribution, and denoting by $M_1$, $M_2$ and $M_3$ the number of matches won, tied or lost by team $T$, the random vector $(M_1, M_2, M_2)$ has multinomial distribution with parameters $n$ and $\boldsymbol{\theta}$ given by
+	Assuming that \added[id=danilo]{the outcomes from} $n$ matches of team \replaced[id=danilo]{$t$}{$T$}, given $\boldsymbol{\theta}$, are i.i.d.
+quantities with the above categorical distribution, and denoting by $M_1$, $M_2$ and $M_3$ the number of matches won, tied or lost by team \replaced[id=danilo]{$t$}{$T$}, the random vector $(M_1, M_2, M_2)$ has multinomial distribution with parameters $n$ and $\boldsymbol{\theta}$ given by
 	\[
@@
 	\[
-	\pi(\boldsymbol{\theta}|\alpha)=\frac{\Gamma(\alpha_1+\alpha_2+\alpha_3)}{\Gamma(\alpha_1)\Gamma(\alpha_2)\Gamma(\alpha_3)}\theta_1^{\alpha_1-1}\theta_2^{\alpha_2-1}(1-\theta_1-\theta_2)^{\alpha_3-1}
+	\pi(\boldsymbol{\theta}|\replaced[id=danilo]{\boldsymbol{\alpha}}{\alpha})=\frac{\Gamma(\alpha_1+\alpha_2+\alpha_3)}{\Gamma(\alpha_1)\Gamma(\alpha_2)\Gamma(\alpha_3)}\theta_1^{\alpha_1-1}\theta_2^{\alpha_2-1}(1-\theta_1-\theta_2)^{\alpha_3-1}
 	\]
@@
 	P(X_{n+1} = 1 | M_1=n_1,M_2=n_2,M_3=n_3) &=
-	\frac{n_1+\alpha_1}{n+\alpha}\\
+	\frac{n_1+\alpha_1}{n+\replaced[id=danilo]{\alpha_{\bullet}}{\alpha}}\\
 	& \\
 	P(X_{n+1} = 2 | M_1=n_1,M_2=n_2,M_3=n_3) &=
-	\frac{n_2+\alpha_1}{n+\alpha} \\
+	\frac{n_2+\alpha_1}{n+\replaced[id=danilo]{\alpha_{\bullet}}{\alpha}} \\
 	& \\
 	P(X_{n+1} = 1 | M_1=n_1, M_2=n_2, M_3=n_3) &=
-	\frac{n_3+\alpha_1}{n+\alpha}
+	\frac{n_3+\alpha_1}{n+\replaced[id=danilo]{\alpha_{\bullet}}{\alpha}}
 	\end{align*}
-	\noindent where $\alpha=\alpha_1+\alpha_2+\alpha_3$.
+	\noindent where $\replaced[id=danilo]{\alpha_{\bullet}}{\alpha} =\alpha_1+\alpha_2+\alpha_3$.
 
-	In this work we used the uniform prior on the 2-simplex, i.e. $\mathcal{D}(1,1,1)$. 
+	 \replaced[id=danilo]{In this work, we are interested in checking the predictive performance of the Multinomial-Dirichlet model for the second round of the championship given the results from the first round.
+In order to do so, we use full time results from the first round as historical data for construction of the Dirichlet prior.
+Predictions are carried out by using a Bayes information updating mechanism: first, we assign a uniform prior on  $\boldsymbol{\theta}$ over the 2-simplex, i.e.
+$\mathcal{D}(1, 1, 1)$, and combine this prior with the first-round data, obtaining a posterior Dirichlet distribution through conjugacy that represents the information about $\boldsymbol{\theta}$ up to the first round; then, the posterior of the first round becomes the prior for the second round, which will be combined with the second round matches up to date in order to yield predictive distributions for future games.}{In this work we used the uniform prior on the 2-simplex, i.e.
+$\mathcal{D}(1,1,1)$.
 This is not a restrictive prior because, since we predicted only the second round of the championship, the counts of the first round were used to update this prior---thanks to the conjugacy property of Dirichlet priors---and we may say that the actual prior we used is therefore the number of matches won, tied or lost by each team added by one.
-	If we had started our predictions in the first round, this prior would not have given 
-	a good predictive performance, but in this case we could have used team rankings such the ones provided by federations and leagues to assess a more realistic prior for each team instead.
+If we had started our predictions in the first round, this prior would not have given a good predictive performance, but in this case we could have used team rankings such the ones provided by federations and leagues to assess a more realistic prior for each team instead.}\footnote{On the other hand, the two black-box models make predictions from a frequentist perspective; BB1 uses scores of every match in the previous two years, while BB2 uses the match scores of the current championship only.}
 
@@
 	The first one is that we will separately consider home and away games for each team. This will allow us to take into account the different performances under those conditions.
-	The second remark is that the prediction of an upcoming match between $A$ and $B$ can be done using
+	The second remark is that the prediction of an upcoming match between \added[id=danilo]{two teams} $A$ and $B$ can be done using
 	the past performance of either team $A$ or $B$.
@@
 	P(X_{n+1}=1|{\bf h}, {\bf a}) &=
-	\frac{1}{2}\left(\frac{h_1+\alpha_1}{h+\alpha}\right)+\frac{1}{2}\left(\frac{a_3+\alpha_3}{a+\alpha}\right)=0.5
+	\frac{1}{2}\left(\frac{h_1+\alpha_1}{\replaced[id=danilo]{h_{\bullet}+\alpha_{\bullet}}{h+\alpha}}\right)+\frac{1}{2}\left(\frac{a_3+\alpha_3}{\replaced[id=danilo]{a_{\bullet}+\alpha_{\bullet}}{a+\alpha}}\right)=0.5
 	\\
 	P(X_{n+1}=2|{\bf h}, {\bf a}) &=
-	\frac{1}{2}\left(\frac{h_2+\alpha_2}{h+\alpha}\right)+\frac{1}{2}\left(\frac{a_2+\alpha_2}{a+\alpha}\right)\simeq0.2917, \\
+	\frac{1}{2}\left(\frac{h_2+\alpha_2}{\replaced[id=danilo]{h_{\bullet}+\alpha_{\bullet}}{h+\alpha}}\right)+\frac{1}{2}\left(\frac{a_2+\alpha_2}{\replaced[id=danilo]{a_{\bullet}+\alpha_{\bullet}}{a+\alpha}}\right)\simeq0.2917, \\
 	P(X_{n+1}=3|{\bf h}, {\bf a}) &= \frac{1}{2}
-	\left(\frac{h_3+\alpha_3}{h+\alpha}\right)+\frac{1}{2}\left(\frac{a_1+\alpha_1}{a+\alpha}\right)\simeq0.2083.
+	\left(\frac{h_3+\alpha_3}{\replaced[id=danilo]{h_{\bullet}+\alpha_{\bullet}}{h+\alpha}}\right)+\frac{1}{2}\left(\frac{a_1+\alpha_1}{\replaced[id=danilo]{a_{\bullet}+\alpha_{\bullet}}{a+\alpha}}\right)\simeq0.2083.
 	\end{align*}
-	\noindent where $h=h_1+h_2+h_3$ and $a=a_1+a_2+a_3$.
+	\noindent where $\replaced[id=danilo]{h_{\bullet}}{h}=h_1+h_2+h_3$ and $\replaced[id=danilo]{a_{\bullet}}{a}=a_1+a_2+a_3$.
 
@@
 	calculated as
-	\[P(X_{n+1}= 1|{\bf h}, {\bf a})=0.647\left(\frac{h_1+\alpha_1}{h+\alpha}\right)+0.353\left(\frac{a_3+\alpha_3}{a+\alpha}\right)=0.525,\]
+	\[P(X_{n+1}= 1|{\bf h}, {\bf a})=0.647\left(\frac{h_1+\alpha_1}{\replaced[id=danilo]{h_{\bullet}+\alpha_{\bullet}}{h+\alpha}}\right)+0.353\left(\frac{a_3+\alpha_3}{\replaced[id=danilo]{a_{\bullet}+\alpha_{\bullet}}{a+\alpha}}\right)=0.525,\]
 	\noindent and the other probabilities are computed similarly.
@@
 	The probability that Gr\^emio wins is therefore	
-	\[P(X_{n+1}=1|{\bf c})=\frac{c_1+\alpha_1}{c+\alpha}\simeq0.524
+	\[P(X_{n+1}=1|{\bf c})=\frac{c_1+\alpha_1}{\replaced[id=danilo]{c_{\bullet}+\alpha_{\bullet}}{c+\alpha}}\simeq0.524
 	\]
@@
 	\noindent
-	where $c=c_1+c_2+c_3$. The probabilities of drawing and losing are computed similarly.
+	where $\replaced[id=danilo]{c_{\bullet}}{c}=c_1+c_2+c_3$. The probabilities of drawing and losing are computed similarly.
 
@@
 
+=======
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \end{document}

### 2015-07-04 template.tex
com sugestoes do ernesto na secao 3

@@
 
-	Formally, let $X$ be a random variable indicating
-	the result of a given match. Hence, $X$ assumes a value in $\{1,2,3\}$. Moreover, let $P$ denote one's probabilistic prediction
-	about $X$, i.e., $P$ is such that $\sum_{x=1}^3P(X=x)=1$ and
-    $P(X=x)\geq0$ for all $x$ in $\{1,2,3\}$.
+	Formally, let $X$ be a random variable
+	taking values in $\mathcal{X}=\{1,2,3\}$ indicating
+	the outcome of the match, with 1 standing for home win, 2 for draw and 3 for away win.  Moreover, let $P=(P_1,P_2,P_3)$ denote one's probabilistic prediction
+	about $X$, i.e., $P$ lies in the 2-simplex set $\Delta_2=\{(p_1,p_2,p_3):p_1+p_2+p_3=1, \ p_1,p_2,p_3\geq0\}$ (see Figure
+	\ref{fig:simplex}). 	
 	A scoring rule is a function 
-	that assigns a real number (score) $S(x,P)$ to each combination $(x,P)$, where $x$ denotes each possible outcome of the match.
-	For a given $x$ in $\{1,2,3\}$, the score  $S(x,P)$ is minimum when $P$ is degenerate distribution on $x$, i.e., when $P(X=x)=1$.  
-	Thus, the best score (i.e., the score with the smallest value) is achieved when the probabilistic prediction for the outcome of the game is a degenerate  distribution
-  on the observed outcome of that match, i.e., a perfect prediction.\footnote{A scoring rule can also be defined to be such that a \emph{large} value of the score indicates good forecasts.}
+	that assigns a real number (score) $S(x,P)$ to each $x \in \mathcal{X}$
+	and $P \in \Delta_2$ 
+	such that 
+	for any given $x$ in $\mathcal{X}$, the score  $S(x,P)$ is minimized when $P$ is 
+	$(1,0,0)$, $(0,1,0)$ or $(0,0,1)$ depending if $x$ is 1, 2 or 3, respectively.
+	The score $S(x,P)$ can be thought as
+	a penalty to be paid when one assigns the 
+	probabilistic prediction $P$ and outcome
+	$x$ occurs.
+Also, the ``best"\footnote{A scoring rule can also be defined to be such that a \emph{large} value of the score indicates good forecasts.} possible score (i.e., the smallest score value) is achieved when the probabilistic prediction for the outcome of the game is perfect.
 	%Most of the scoring rules also exhibit an arbitrary normalizing feature such as $S(x,P_X)=0$ for each $x$.
 
-	Although many functions satisfy the criteria for a scoring rule specified above, 
-	not all scoring rules encourage honesty and accuracy in assessing numerical values for their predictions.
-	Those that do encourage a fair assessment are named \emph{proper scoring rules} \cite{lad}, which we describe in the sequence.
+	Although many functions can satisfy the above scoring rule definition, not all of them encourage honesty and accuracy when assigning a prediction to an event.
+Those that do enable a fair probabilistic assignment are named \emph{proper scoring rules} \cite{lad}, which we describe in the sequence.
 
-	Say a model's probabilistic prediction for $X$ is $P^*.$ A proper scoring rule is a scoring rule $S$ such that the probabilistic prediction $P$ that minimizes 
-	$$E_{P^*}[S(X,P)]=\sum_{x=1}^3 S(x,P)P^*(X=x)$$
-	 is $P^*$  itself.
-	In other words, if one imagines 
-	a penalty $S(x,P)$ is received 
-	when $x$ happens then, 
-	if $S$ is a proper scoring rule, the lowest expected penalty is obtained by reporting the model's  uncertainty about $X$, $P^*$.
-	The use of a proper scoring rule thus encourages the forecaster to use $P^*$
-	as his probabilistic prediction for the outcome of the game, $X$, rather than some other quantity. 
+	Say a model's probabilistic prediction for $X$ is $P^*=(P_1^*,P_2^*,P_3^*).$ A proper scoring rule $S$ is a scoring rule  such that the mean score value 
+	$$E_{P^*}[S(X,P)]=\sum_{x=1}^3 S(x,P)P^*_x$$
+	 is minimized when $P=P^*$.
+	In other words, if one announces
+	$P$ as his probabilistic prediction
+	and $S$ as a scoring rule, the lowest
+	expected penalty is obtained by reporting the correct model's  uncertainty about $X$, $P^*$.
+	Thus, the use of a proper scoring rule encourages the forecaster to announce $P^*$ (the correct one)
+	as his probabilistic prediction  rather than some other quantity. 
 	%Moreover, this method automatically leads to an overall comparison between the outcomes of different personal evaluations concerned with the same totality of events and, therefore, the accumulated score may be considered a concrete measure of success of each model.
@@
 
-	Let $P$ be a probabilistic prediction  for $X$.
+	Let $P=(P_1,P_2,P_3)$ be a probabilistic prediction  for $X$.
 	The Brier score for a given outcome $x\in\{1,2,3\}$ is given by
-	$$S(x,P)= \sum_{i=1}^3\mathbb{I}(x=i)(1- P(X=i))^2+\sum_{i=1}^3\mathbb{I}(x\neq i)P^2(X=i),$$
+	$$S(x,P)= \sum_{i=1}^3\mathbb{I}(x=i)(1- P_i)^2+\sum_{i=1}^3\mathbb{I}(x\neq i)P^2_i,$$
 	where $\mathbb{I}$ is the indicator function.
@@
 
-	The Brier score for the probabilistic prediction
-	$$P(X=1)=0.25, P(X=2)=0.35, P(X=3)=0.40,$$ 
+	The Brier score for the probabilistic prediction $P=(0.25,0.35,0.40)$
 	assuming the home team loses, is therefore given by $d^2=(0-0.25)^2+(0-0.35)^2+(1-0.40)^2=0.545$. 
-	On the other hand, the prediction $P(X=3)=1$ achieves score  zero, the minimum for this rule.
+	On the other hand, the prediction $P=(0,0,1)$ achieves score  zero, the minimum for this rule.
 
 	It is useful to consider the score of what we will call {\it trivial prediction}:
-	$$P(X=1)=1/3, P(X=2)=1/3, P(X=3)=1/3.$$
+	$P=(1/3,1/3,1/3)$.
 	This assessment will produce a Brier score of $2/3$, no matter what is the final result of the match, providing, thus, a threshold that a good model should consistently beat, meaning, for the Brier score, that the scores of its predictions should be smaller than $0.667$.
@@
 	The logarithmic  score is given by
-	$$S(x,P)=- \sum_{i=1}^3\mathbb{I}(x=i)\ln(P(X=i)),$$
+	$$S(x,P)=- \sum_{i=1}^3\mathbb{I}(x=i)\ln(P_i),$$
 
@@
 	The logarithmic score for the prediction 
-		$$P(X=1)=0.25, P(X=2)=0.35, P(X=3)=0.40,$$ 
+	$P=(0.25,0.35,0.40)$
 		 when the home team loses is therefore 
 	$-\ln(0.4)\approx 0.91$. 
-	On the other hand, the prediction $P(X=3)=1$ achieves score zero, once again the minimum of this rule.
+	On the other hand, the prediction $P=(0,0,1)$ achieves score zero, once again the minimum of this rule.
 	Moreover, for the logarithmic score, the trivial prediction gives a score of approximately $1.098$.
@@
 	The spherical score is given by
-	$$S(x,P)=- \frac{1}{\sqrt{\sum_{i=1}^3 P^2(X=i)}}\sum_{i=1}^3\mathbb{I}(x=x_i)P(X=i),$$
+	$$S(x,P)=- \frac{1}{\sqrt{\sum_{i=1}^3 P^2_i}}\sum_{i=1}^3\mathbb{I}(x=x_i)P_i,$$
 
@@
 	The spherical score for the prediction 
-		$$P(X=1)=0.25, P(X=2)=0.35, P(X=3)=0.40,$$ 
-		 assuming the home team loses, is given by
+		$P=(0.25,0.35,0.40)$ assuming the home team loses, is given by
 	$-0.4/\sqrt{0.25^2+0.35^2+0.40^2} \approx -0.68$.
-	On the other hand, the prediction $P(X=3)=1$ achieves score  $-1$ instead and, for this rule, the trivial prediction results in a score of approximately $-0.577$.
+	On the other hand, the prediction $P=(0,0,1)$ achieves score  $-1$ instead and, for this rule, the trivial prediction results in a score of approximately $-0.577$.
 
@@
 	The first one is the proportion of errors made by the model or assessor. This is simply the proportion of mistakes made when considering the highest probability assessment.
-	More precisely, the proportion of errors of a given probabilistic prediction $P$ is defined by
-	$$\frac{1}{n}\sum_{j=1}^n \mathbb{I}\left(X_j \neq \arg \max_{x \in \{1,2,3\}} P(X_j=x)\right),$$
+	More precisely, the proportion of errors of a a sequence of probabilistic predictions for $n$ games, $P^{(1)},\ldots,P^{(n)}$
+	with
+		$P^{(j)}=(P^{(j)}_1,P^{(j)}_2,P^{(j)}_3)$, is defined by
+	$$\frac{1}{n}\sum_{j=1}^n \mathbb{I}\left(X_j \neq \arg \max_{x \in \{1,2,3\}} P^{(j)}_x\right),$$
 	where $X_j$ is the outcome of the $j$-th match.
@@
 	Because we typically do not have several predictions with the same assigned probability $p$, we obtain a plot by smoothing (i.e., regressing) the indicator function of whether a given result happened as a function of the probability assigned for that result.
-	That is, we estimate the probability that a event occurs given its assigned probability.
+	That is, we estimate the probability that an event occurs given its assigned probability.
 	%, that is, we regress  

### 2015-07-07 template.tex
Seções 2.2-2.5 editadas por Danilo

@@
 
-	We adopt a Bayesian approach to calculate the prediction probabilities of an upcoming match of \added[id=danilo]{a} team \replaced[id=danilo]{$t$}{$T$} \deleted[id = danilo]{($A$ or $B$)} based on its past performance, i.e\added[id=danilo]{.}, the number of matches it has won, tied and lost.
+		We adopt a Bayesian approach to calculate the prediction probabilities of an upcoming match of a team $t$ based on its past performance, i.e., the number of matches it has won, tied and lost.
 
-	Let us consider the outcome of \replaced[id=danilo]{a given}{each} match of team \replaced[id=danilo]{$t$}{$T$} as a categorical random quantity $X$ that may assume only the values $1$ \added[id=danilo]{(if team $t$ wins)}, $2$ \added[id=danilo]{(if a draw occurs)}, $3$ \added[id=danilo]{(if team $t$ loses)}, \deleted[id=danilo]{where $1$ means win ($W$), $2$ draw ($D$) and $3$ loss ($L$)}.
-	Denoting by $\theta_1, \theta_2$ and $\theta_3$ ($\theta_3 = 1-\theta_1 - \theta_2$), the probabilities of win, draw and loss, respectively, the probability mass function of $X$ is
+		Let us consider the outcome of a given match of team $t$ as a categorical random quantity $X$ that may assume only the values $1$ (if team $t$ wins), $2$ (if a draw occurs), $3$ (if team $t$ loses).
+		Denoting by $\theta_1, \theta_2$ and $\theta_3$ (where $\theta_3 = 1-\theta_1 - \theta_2$), the probabilities of win, draw and loss, respectively, the probability mass function of $X$ is
 		\[
@@
 		value 1 if $x$ equals $i$ and 0 otherwise, and $\boldsymbol{\theta}
-	= (\theta_1, \theta_2)$ \replaced[id=danilo]{belongs}{belogns} to $\boldsymbol{\Theta} =
+		= (\theta_1, \theta_2)$ belongs to $\boldsymbol{\Theta} =
 		\{(\theta_1,\theta_2)\in [0,1]^2: \theta_1+\theta_2 \leq 1 \}$, the 2-simplex.
 
-	Assuming that \added[id=danilo]{the outcomes from} $n$ matches of team \replaced[id=danilo]{$t$}{$T$}, given $\boldsymbol{\theta}$, are i.i.d.
-quantities with the above categorical distribution, and denoting by $M_1$, $M_2$ and $M_3$ the number of matches won, tied or lost by team \replaced[id=danilo]{$t$}{$T$}, the random vector $(M_1, M_2, M_2)$ has multinomial distribution with parameters $n$ and $\boldsymbol{\theta}$ given by
+		Assuming that the outcomes from $n$ matches of team $t$, given $\boldsymbol{\theta}$, are i.i.d.
+quantities with the above categorical distribution, and denoting by $M_1$, $M_2$ and $M_3$ the number of matches won, tied or lost by team $t$, the random vector $(M_1, M_2, M_2)$ has multinomial distribution with parameters $n$ and $\boldsymbol{\theta}$ given by
 		\[
@@
 		\[
-	\pi(\boldsymbol{\theta}|\replaced[id=danilo]{\boldsymbol{\alpha}}{\alpha})=\frac{\Gamma(\alpha_1+\alpha_2+\alpha_3)}{\Gamma(\alpha_1)\Gamma(\alpha_2)\Gamma(\alpha_3)}\theta_1^{\alpha_1-1}\theta_2^{\alpha_2-1}(1-\theta_1-\theta_2)^{\alpha_3-1}
+		\pi(\boldsymbol{\theta}|\boldsymbol{\alpha})=\frac{\Gamma(\alpha_1+\alpha_2+\alpha_3)}{\Gamma(\alpha_1)\Gamma(\alpha_2)\Gamma(\alpha_3)}\theta_1^{\alpha_1-1}\theta_2^{\alpha_2-1}(1-\theta_1-\theta_2)^{\alpha_3-1}
 		\]
@@
 			P(X_{n+1} = 1 | M_1=n_1,M_2=n_2,M_3=n_3) &=
-	\frac{n_1+\alpha_1}{n+\replaced[id=danilo]{\alpha_{\bullet}}{\alpha}}\\
+			\frac{n_1+\alpha_1}{n+\alpha_{\bullet}}\\
 			& \\
 			P(X_{n+1} = 2 | M_1=n_1,M_2=n_2,M_3=n_3) &=
-	\frac{n_2+\alpha_1}{n+\replaced[id=danilo]{\alpha_{\bullet}}{\alpha}} \\
+			\frac{n_2+\alpha_2}{n+\alpha_{\bullet}} \\
 			& \\
-	P(X_{n+1} = 1 | M_1=n_1, M_2=n_2, M_3=n_3) &=
-	\frac{n_3+\alpha_1}{n+\replaced[id=danilo]{\alpha_{\bullet}}{\alpha}}
+			P(X_{n+1} = 3 | M_1=n_1, M_2=n_2, M_3=n_3) &=
+			\frac{n_3+\alpha_3}{n+\alpha_{\bullet}}
 		\end{align*}
-	\noindent where $\replaced[id=danilo]{\alpha_{\bullet}}{\alpha} =\alpha_1+\alpha_2+\alpha_3$.
+		\noindent where $\alpha_{\bullet} =\alpha_1+\alpha_2+\alpha_3$.
 
-	 \replaced[id=danilo]{In this work, we are interested in checking the predictive performance of the Multinomial-Dirichlet model for the second round of the championship given the results from the first round.
-In order to do so, we use full time results from the first round as historical data for construction of the Dirichlet prior.
-Predictions are carried out by using a Bayes information updating mechanism: first, we assign a uniform prior on  $\boldsymbol{\theta}$ over the 2-simplex, i.e.
-$\mathcal{D}(1, 1, 1)$, and combine this prior with the first-round data, obtaining a posterior Dirichlet distribution through conjugacy that represents the information about $\boldsymbol{\theta}$ up to the first round; then, the posterior of the first round becomes the prior for the second round, which will be combined with the second round matches up to date in order to yield predictive distributions for future games.}{In this work we used the uniform prior on the 2-simplex, i.e.
-$\mathcal{D}(1,1,1)$.
-This is not a restrictive prior because, since we predicted only the second round of the championship, the counts of the first round were used to update this prior---thanks to the conjugacy property of Dirichlet priors---and we may say that the actual prior we used is therefore the number of matches won, tied or lost by each team added by one.
-If we had started our predictions in the first round, this prior would not have given a good predictive performance, but in this case we could have used team rankings such the ones provided by federations and leagues to assess a more realistic prior for each team instead.}\footnote{On the other hand, the two black-box models make predictions from a frequentist perspective; BB1 uses scores of every match in the previous two years, while BB2 uses the match scores of the current championship only.}
+		In this work, we are interested in checking the predictive performance of the Multinomial-Dirichlet 
+		model for the result of every single match in the second round of the championship given the results 
+		of all the previous matches observed in the same tournament. Predictions 
+		are carried out by using a Bayes information updating mechanism. First, we use full-time 
+		results from the first round as historical data for construction of the Dirichlet prior: we assign a uniform prior on  
+		$\boldsymbol{\theta}$ over the 2-simplex, i.e. $\mathcal{D}(1, 1, 1)$, and combine this prior with 
+		the first-round data, obtaining a posterior Dirichlet distribution through conjugacy that represents 
+		the information about $\boldsymbol{\theta}$ up to the first round. Then, the posterior of the first 
+		round becomes the prior for the second round, which, for every matchday in the second round, will be combined with all the observed second-round matches 
+		up to that matchday in order to yield posterior predictive distributions. Note that, on the other hand, the two 
+		black-box models make predictions from a frequentist perspective; BB1 uses scores of every match 
+		in the previous two years, while BB2 uses the match scores of the current championship only.
 
@@
 		The first one is that we will separately consider home and away games for each team. This will allow us to take into account the different performances under those conditions.
-	The second remark is that the prediction of an upcoming match between \added[id=danilo]{two teams} $A$ and $B$ can be done using
+		The second remark is that the prediction of an upcoming match between two teams $A$ and $B$ can be done using
 		the past performance of either team $A$ or $B$.
@@
 		P(X_{n+1}=1|{\bf h}, {\bf a}) &=
-	\frac{1}{2}\left(\frac{h_1+\alpha_1}{\replaced[id=danilo]{h_{\bullet}+\alpha_{\bullet}}{h+\alpha}}\right)+\frac{1}{2}\left(\frac{a_3+\alpha_3}{\replaced[id=danilo]{a_{\bullet}+\alpha_{\bullet}}{a+\alpha}}\right)=0.5
+		\frac{1}{2}\left(\frac{h_1+\alpha_1}{h_{\bullet}+\alpha_{\bullet}}\right)+\frac{1}{2}\left(\frac{a_3+\alpha_3}{a_{\bullet}+\alpha_{\bullet}}\right)=0.5
 		\\
 		P(X_{n+1}=2|{\bf h}, {\bf a}) &=
-	\frac{1}{2}\left(\frac{h_2+\alpha_2}{\replaced[id=danilo]{h_{\bullet}+\alpha_{\bullet}}{h+\alpha}}\right)+\frac{1}{2}\left(\frac{a_2+\alpha_2}{\replaced[id=danilo]{a_{\bullet}+\alpha_{\bullet}}{a+\alpha}}\right)\simeq0.2917, \\
+		\frac{1}{2}\left(\frac{h_2+\alpha_2}{h_{\bullet}+\alpha_{\bullet}}\right)+\frac{1}{2}\left(\frac{a_2+\alpha_2}{a_{\bullet}+\alpha_{\bullet}}\right)\simeq0.2917, \\
 		P(X_{n+1}=3|{\bf h}, {\bf a}) &= \frac{1}{2}
-	\left(\frac{h_3+\alpha_3}{\replaced[id=danilo]{h_{\bullet}+\alpha_{\bullet}}{h+\alpha}}\right)+\frac{1}{2}\left(\frac{a_1+\alpha_1}{\replaced[id=danilo]{a_{\bullet}+\alpha_{\bullet}}{a+\alpha}}\right)\simeq0.2083.
+		\left(\frac{h_3+\alpha_3}{h_{\bullet}+\alpha_{\bullet}}\right)+\frac{1}{2}\left(\frac{a_1+\alpha_1}{a_{\bullet}+\alpha_{\bullet}}\right)\simeq0.2083.
 	\end{align*}
-	\noindent where $\replaced[id=danilo]{h_{\bullet}}{h}=h_1+h_2+h_3$ and $\replaced[id=danilo]{a_{\bullet}}{a}=a_1+a_2+a_3$.
+	\noindent where $h_{\bullet}=h_1+h_2+h_3$ and $a_{\bullet}=a_1+a_2+a_3$.
 
@@
 	the team ranks just before the match is played. In the illustrative
-	example, we know that after 19 matchdays, Gr\^emio was the $6^{th}$
-	place and Atl\'etico-PR the $11^{th}$. Therefore, we shall consider
+	example, we know that after 19 matchdays, Gr\^emio was the $6^{\footnotesize\mbox{th}}$
+	place and Atl\'etico-PR the $11^{\footnotesize\mbox{th}}$. Therefore, we shall consider
 	the weights
@@
 	calculated as
-	\[P(X_{n+1}= 1|{\bf h}, {\bf a})=0.647\left(\frac{h_1+\alpha_1}{\replaced[id=danilo]{h_{\bullet}+\alpha_{\bullet}}{h+\alpha}}\right)+0.353\left(\frac{a_3+\alpha_3}{\replaced[id=danilo]{a_{\bullet}+\alpha_{\bullet}}{a+\alpha}}\right)=0.525,\]
+	\[P(X_{n+1}= 1|{\bf h}, {\bf a})=0.647\left(\frac{h_1+\alpha_1}{h_{\bullet}+\alpha_{\bullet}}\right)+0.353\left(\frac{a_3+\alpha_3}{a_{\bullet}+\alpha_{\bullet}}\right)=0.525,\]
 	\noindent and the other probabilities are computed similarly.
@@
 	we define the combined vector ${\bf c} = (c_1, c_2, c_3)$ by $c_1 =
-	h_1 + a_3$, $h_2 = h_2 + a_2$, and $h_3 = h_3 + a_1$. Then, assuming that the vector ${\bf c} = (c_1, c_2, c_3)$, given $\boldsymbol{\theta}$, has multinomial distribution with parameters $n$ and
+	h_1 + a_3$, $c_2 = h_2 + a_2$, and $c_3 = h_3 + a_1$. Then, assuming that the vector ${\bf c} = (c_1, c_2, c_3)$, given $\boldsymbol{\theta}$, has multinomial distribution with parameters $n$ and
 	$\boldsymbol{\theta}$, the predictive distribution for $X_{n + 1}$ can
@@
 	The probability that Gr\^emio wins is therefore	
-	\[P(X_{n+1}=1|{\bf c})=\frac{c_1+\alpha_1}{\replaced[id=danilo]{c_{\bullet}+\alpha_{\bullet}}{c+\alpha}}\simeq0.524
+	\[P(X_{n+1}=1|{\bf c})=\frac{c_1+\alpha_1}{c_{\bullet}+\alpha_{\bullet}}\simeq0.524
 	\]
@@
 	\noindent
-	where $\replaced[id=danilo]{c_{\bullet}}{c}=c_1+c_2+c_3$. The probabilities of drawing and losing are computed similarly.
+	where $c_{\bullet}=c_1+c_2+c_3$. The probabilities of drawing and losing are computed similarly.
 

### 2015-07-07 template.tex
Alteracoes.

--- 2015-07-04 template.tex
@@
-%  LaTeX support: latex@mdpi.com\textbf{}
+%  LaTeX support: latex@mdpi.com
 %  In case you need support, please attach any log files that you could have, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).
@@
 \definechangesauthor[name={Rafael}, color=blue]{raf}
-\setremarkmarkup{(#2)}
-\definechangesauthor[name={Danilo}, color= violet]{danilo}
 \setremarkmarkup{(#2)}
@@
 Section \ref{sec::experimental} describes the proposed models, Section \ref{sec::scoring} presents the scoring rules and criteria used in this work to classify the models.
-	Section \ref{sec::results} reports the performance of the models predicting 190 matches comprising the second half of the Brazilian championship of first division.
+Section \ref{sec::results} reports the performance of the models predicting 190 matches comprising the second round of the Brazilian championship of first division.
 In Section \ref{sec::remarks} we discuss the results and close with proposals for future research.
@@
 
-	In this section, we present the basic assumptions adopted by the benchmark models and 
-	by the three proposed models. The predictions of the
+In this section we present the probabilistic justification for the
+three proposed models and the predictive distribution of an upcoming
+match of team $A$ (home team) versus $B$ (away team). The main idea
+is to combine the past performance of both teams in different ways
+in order to predict the outcome of the match. The predictions of the
 two benchmark models were published before each matchday at
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-	\subsection{Benchmark Models}
-	\label{sec::Benchmark}
 
@@
 
-	We adopt a Bayesian approach to calculate the prediction probabilities of an upcoming match of \added[id=danilo]{a} team \replaced[id=danilo]{$t$}{$T$} \deleted[id = danilo]{($A$ or $B$)} based on its past performance, i.e\added[id=danilo]{.}, the number of matches it has won, tied and lost.
+We adopt a Bayesian approach to calculate the prediction probabilities of an upcoming match of team $T$ ($A$ or $B$) based on its past performance, i.e, the number of matches it has won, tied and lost.
 
-	Let us consider the outcome of \replaced[id=danilo]{a given}{each} match of team \replaced[id=danilo]{$t$}{$T$} as a categorical random quantity $X$ that may assume only the values $1$ \added[id=danilo]{(if team $t$ wins)}, $2$ \added[id=danilo]{(if a draw occurs)}, $3$ \added[id=danilo]{(if team $t$ loses)}, \deleted[id=danilo]{where $1$ means win ($W$), $2$ draw ($D$) and $3$ loss ($L$)}.
+Let us consider the outcome of each match of team $T$ as a categorical random quantity $X$ that may assume only the values $1$, $2$, $3$, where $1$ means win ($W$), $2$ draw ($D$) and $3$ loss ($L$).
 Denoting by $\theta_1, \theta_2$ and $\theta_3$ ($\theta_3 = 1-\theta_1 - \theta_2$), the probabilities of win, draw and loss, respectively, the probability mass function of $X$ is
@@
 value 1 if $x$ equals $i$ and 0 otherwise, and $\boldsymbol{\theta}
-	= (\theta_1, \theta_2)$ \replaced[id=danilo]{belongs}{belogns} to $\boldsymbol{\Theta} =
+= (\theta_1, \theta_2)$ belogns to $\boldsymbol{\Theta} =
 \{(\theta_1,\theta_2)\in [0,1]^2: \theta_1+\theta_2 \leq 1 \}$, the 2-simplex.
 
-	Assuming that \added[id=danilo]{the outcomes from} $n$ matches of team \replaced[id=danilo]{$t$}{$T$}, given $\boldsymbol{\theta}$, are i.i.d.
-quantities with the above categorical distribution, and denoting by $M_1$, $M_2$ and $M_3$ the number of matches won, tied or lost by team \replaced[id=danilo]{$t$}{$T$}, the random vector $(M_1, M_2, M_2)$ has multinomial distribution with parameters $n$ and $\boldsymbol{\theta}$ given by
+Assuming that $n$ matches of team $T$, given $\boldsymbol{\theta}$, are i.i.d.
+quantities with the above categorical distribution, and denoting by $M_1$, $M_2$ and $M_3$ the number of matches won, tied or lost by team $T$, the random vector $(M_1, M_2, M_2)$ has multinomial distribution with parameters $n$ and $\boldsymbol{\theta}$ given by
 \[
@@
 \[
-	\pi(\boldsymbol{\theta}|\replaced[id=danilo]{\boldsymbol{\alpha}}{\alpha})=\frac{\Gamma(\alpha_1+\alpha_2+\alpha_3)}{\Gamma(\alpha_1)\Gamma(\alpha_2)\Gamma(\alpha_3)}\theta_1^{\alpha_1-1}\theta_2^{\alpha_2-1}(1-\theta_1-\theta_2)^{\alpha_3-1}
+\pi(\boldsymbol{\theta}|\alpha)=\frac{\Gamma(\alpha_1+\alpha_2+\alpha_3)}{\Gamma(\alpha_1)\Gamma(\alpha_2)\Gamma(\alpha_3)}\theta_1^{\alpha_1-1}\theta_2^{\alpha_2-1}(1-\theta_1-\theta_2)^{\alpha_3-1}
 \]
@@
 P(X_{n+1} = 1 | M_1=n_1,M_2=n_2,M_3=n_3) &=
-	\frac{n_1+\alpha_1}{n+\replaced[id=danilo]{\alpha_{\bullet}}{\alpha}}\\
+\frac{n_1+\alpha_1}{n+\alpha}\\
 & \\
 P(X_{n+1} = 2 | M_1=n_1,M_2=n_2,M_3=n_3) &=
-	\frac{n_2+\alpha_1}{n+\replaced[id=danilo]{\alpha_{\bullet}}{\alpha}} \\
+\frac{n_2+\alpha_1}{n+\alpha} \\
 & \\
-	P(X_{n+1} = 1 | M_1=n_1, M_2=n_2, M_3=n_3) &=
-	\frac{n_3+\alpha_1}{n+\replaced[id=danilo]{\alpha_{\bullet}}{\alpha}}
+P(X_{n+1} = 3 | M_1=n_1, M_2=n_2, M_3=n_3) &=
+\frac{n_3+\alpha_1}{n+\alpha}
 \end{align*}
-	\noindent where $\replaced[id=danilo]{\alpha_{\bullet}}{\alpha} =\alpha_1+\alpha_2+\alpha_3$.
+\noindent where $\alpha=\alpha_1+\alpha_2+\alpha_3$.
 
-	 \replaced[id=danilo]{In this work, we are interested in checking the predictive performance of the Multinomial-Dirichlet model for the second round of the championship given the results from the first round.
-In order to do so, we use full time results from the first round as historical data for construction of the Dirichlet prior.
-Predictions are carried out by using a Bayes information updating mechanism: first, we assign a uniform prior on  $\boldsymbol{\theta}$ over the 2-simplex, i.e.
-$\mathcal{D}(1, 1, 1)$, and combine this prior with the first-round data, obtaining a posterior Dirichlet distribution through conjugacy that represents the information about $\boldsymbol{\theta}$ up to the first round; then, the posterior of the first round becomes the prior for the second round, which will be combined with the second round matches up to date in order to yield predictive distributions for future games.}{In this work we used the uniform prior on the 2-simplex, i.e.
-$\mathcal{D}(1,1,1)$.
+In this work we used the uniform prior on the 2-simplex, i.e. $\mathcal{D}(1,1,1)$. 
 This is not a restrictive prior because, since we predicted only the second round of the championship, the counts of the first round were used to update this prior---thanks to the conjugacy property of Dirichlet priors---and we may say that the actual prior we used is therefore the number of matches won, tied or lost by each team added by one.
-If we had started our predictions in the first round, this prior would not have given a good predictive performance, but in this case we could have used team rankings such the ones provided by federations and leagues to assess a more realistic prior for each team instead.}\footnote{On the other hand, the two black-box models make predictions from a frequentist perspective; BB1 uses scores of every match in the previous two years, while BB2 uses the match scores of the current championship only.}
+If we had started our predictions in the first round, this prior would not have given 
+a good predictive performance, but in this case we could have used team rankings such the ones provided by federations and leagues to assess a more realistic prior for each team instead.
 
@@
 The first one is that we will separately consider home and away games for each team. This will allow us to take into account the different performances under those conditions.
-	The second remark is that the prediction of an upcoming match between \added[id=danilo]{two teams} $A$ and $B$ can be done using
+The second remark is that the prediction of an upcoming match between $A$ and $B$ can be done using
 the past performance of either team $A$ or $B$.
@@
 P(X_{n+1}=1|{\bf h}, {\bf a}) &=
-	\frac{1}{2}\left(\frac{h_1+\alpha_1}{\replaced[id=danilo]{h_{\bullet}+\alpha_{\bullet}}{h+\alpha}}\right)+\frac{1}{2}\left(\frac{a_3+\alpha_3}{\replaced[id=danilo]{a_{\bullet}+\alpha_{\bullet}}{a+\alpha}}\right)=0.5
+\frac{1}{2}\left(\frac{h_1+\alpha_1}{h+\alpha}\right)+\frac{1}{2}\left(\frac{a_3+\alpha_3}{a+\alpha}\right)=0.5
 \\
 P(X_{n+1}=2|{\bf h}, {\bf a}) &=
-	\frac{1}{2}\left(\frac{h_2+\alpha_2}{\replaced[id=danilo]{h_{\bullet}+\alpha_{\bullet}}{h+\alpha}}\right)+\frac{1}{2}\left(\frac{a_2+\alpha_2}{\replaced[id=danilo]{a_{\bullet}+\alpha_{\bullet}}{a+\alpha}}\right)\simeq0.2917, \\
+\frac{1}{2}\left(\frac{h_2+\alpha_2}{h+\alpha}\right)+\frac{1}{2}\left(\frac{a_2+\alpha_2}{a+\alpha}\right)\simeq0.2917, \\
 P(X_{n+1}=3|{\bf h}, {\bf a}) &= \frac{1}{2}
-	\left(\frac{h_3+\alpha_3}{\replaced[id=danilo]{h_{\bullet}+\alpha_{\bullet}}{h+\alpha}}\right)+\frac{1}{2}\left(\frac{a_1+\alpha_1}{\replaced[id=danilo]{a_{\bullet}+\alpha_{\bullet}}{a+\alpha}}\right)\simeq0.2083.
+\left(\frac{h_3+\alpha_3}{h+\alpha}\right)+\frac{1}{2}\left(\frac{a_1+\alpha_1}{a+\alpha}\right)\simeq0.2083.
 \end{align*}
-	\noindent where $\replaced[id=danilo]{h_{\bullet}}{h}=h_1+h_2+h_3$ and $\replaced[id=danilo]{a_{\bullet}}{a}=a_1+a_2+a_3$.
+\noindent where $h=h_1+h_2+h_3$ and $a=a_1+a_2+a_3$.
 
@@
 calculated as
-	\[P(X_{n+1}= 1|{\bf h}, {\bf a})=0.647\left(\frac{h_1+\alpha_1}{\replaced[id=danilo]{h_{\bullet}+\alpha_{\bullet}}{h+\alpha}}\right)+0.353\left(\frac{a_3+\alpha_3}{\replaced[id=danilo]{a_{\bullet}+\alpha_{\bullet}}{a+\alpha}}\right)=0.525,\]
+\[P(X_{n+1}= 1|{\bf h}, {\bf a})=0.647\left(\frac{h_1+\alpha_1}{h+\alpha}\right)+0.353\left(\frac{a_3+\alpha_3}{a+\alpha}\right)=0.525,\]
 \noindent and the other probabilities are computed similarly.
 
-	\subsection{Model Three: Multinomial-Dirichlet 3}
+\subsection{Model 3: Multinomial-Dirichlet 3}
 \label{sec::Mn_Dir3}
@@
 The probability that Gr\^emio wins is therefore	
-	\[P(X_{n+1}=1|{\bf c})=\frac{c_1+\alpha_1}{\replaced[id=danilo]{c_{\bullet}+\alpha_{\bullet}}{c+\alpha}}\simeq0.524
+\[P(X_{n+1}=1|{\bf c})=\frac{c_1+\alpha_1}{c+\alpha}\simeq0.524
 \]
@@
 \noindent
-	where $\replaced[id=danilo]{c_{\bullet}}{c}=c_1+c_2+c_3$. The probabilities of drawing and losing are computed similarly.
+where $c=c_1+c_2+c_3$. The probabilities of drawing and losing are computed similarly.
 
@@
 
-	How can we fairly rank the various predictive models?
-	A way of doing this is by using proper scoring rules, where
-	the score may be interpreted as a numerical measure of how inaccurate was a given probabilistic prediction.
+How can we fairly distinguish better-informed states of knowledge from more poorly informed states?
+A way of doing this is to use proper scoring rules for evaluating states of uncertain knowledge, where
+the score may be interpreted as a numerical measure of how inaccurate was the prevision.
 
-	Formally, let $X$ be a random variable
-	taking values in $\mathcal{X}=\{1,2,3\}$ indicating
-	the outcome of the match, with 1 standing for home win, 2 for draw and 3 for away win.  Moreover, let $P=(P_1,P_2,P_3)$ denote one's probabilistic prediction
-	about $X$, i.e., $P$ lies in the 2-simplex set $\Delta_2=\{(p_1,p_2,p_3):p_1+p_2+p_3=1, \ p_1,p_2,p_3\geq0\}$ (see Figure
-	\ref{fig:simplex}). 	
-	A scoring rule is a function 
-	that assigns a real number (score) $S(x,P)$ to each $x \in \mathcal{X}$
-	and $P \in \Delta_2$ 
-	such that 
-	for any given $x$ in $\mathcal{X}$, the score  $S(x,P)$ is minimized when $P$ is 
-	$(1,0,0)$, $(0,1,0)$ or $(0,0,1)$ depending if $x$ is 1, 2 or 3, respectively.
-	The score $S(x,P)$ can be thought as
-	a penalty to be paid when one assigns the 
-	probabilistic prediction $P$ and outcome
-	$x$ occurs.
-Also, the ``best"\footnote{A scoring rule can also be defined to be such that a \emph{large} value of the score indicates good forecasts.} possible score (i.e., the smallest score value) is achieved when the probabilistic prediction for the outcome of the game is perfect.
+%More precisely, a scoring rule is a function of two variables (or vectors, matrices etc) that assigns a real number (score) to each possible outcome $X$ and its respective prevision value, $P(X)$.
+%It is maximum for each $x$ when $x=P(X)$, and is nonincreasing both as $x$ departs from $P(X)$ (for each $P(X)$) and as $P(X)$ departs from $x$ (for each $x$).
+%Thus, the best score is achieved when knowledge of $X$ is asserted as the value of $X$ itself, whatever it might be.
+Most of the scoring rules also exhibit an arbitrary normalizing feature such as $S[x,P(X)]=0$ for each $x$.
+
+%Although many functions satisfy the criteria for a scoring rule specified above, not every scoring rule can be regarded as providing a fair assessment of the assertion $P(X)$, that is, not all scoring rules encourage honesty and accuracy in assessing numerical values for their previsions.
+%Those that do encourage a fair assessment are named \emph{proper scoring rules} \cite{lad}.
+
+%Say a forecaster's uncertainty about $X$ is $P_0$. A proper scoring rule is a scoring rule $S$ such that the prevision value $P(X)$ that minimizes $E_{P_0}[S(X,P(X))]$ is $P_0$.
+%In other words, if one receives a reward $S(x,P(x))$ when $x$ happens and if $S$ is a proper scoring rule, then the highest expected reward is obtained by reporting one's  true uncertainty about $X$.
+%The use of a proper scoring rule thus encourages the forecaster to be honest to maximize the expected reward.
+%Moreover, this method leads automatically to an overall comparison between the outcomes of different personal evaluations concerned with the same totality of events.
+%Therefore, the accumulated score may be considered a concrete measure of success of each forecaster or model.
+
+More precisely, a scoring rule is a function of two variables (or vectors, matrices etc) that assigns a real number (score) to each possible outcome of $X$ and its respective prevision value, $P_X$, i.e.
+$P_X$ is the probability assigned to each possible outcome of $X$.
+It is minimum for each $x$ when $P_X$ is such that $P_X(X=x)=1$, and is nondecreasing both as $x$ departs from $P_X$ (for each $P_X$) and as $P_X$ departs from $x$ (for each $x$).
+Thus, the best score (the smaller value of the score) is achieved when knowledge of $X$ is asserted as the value of $X$ itself, whatever it might be\footnote{A scoring rule can also be defined to be such that a \emph{large} value of the score indicates good predictions.}.
 %Most of the scoring rules also exhibit an arbitrary normalizing feature such as $S(x,P_X)=0$ for each $x$.
 
-	Although many functions can satisfy the above scoring rule definition, not all of them encourage honesty and accuracy when assigning a prediction to an event.
-Those that do enable a fair probabilistic assignment are named \emph{proper scoring rules} \cite{lad}, which we describe in the sequence.
+Although many functions satisfy the criteria for a scoring rule specified above, not every scoring rule can be regarded as providing a fair assessment of the assertion $P_X$, that is, not all scoring rules encourage honesty and accuracy in assessing numerical values for their previsions.
+Those that do encourage a fair assessment are named \emph{proper scoring rules} \cite{lad}.
 
-	Say a model's probabilistic prediction for $X$ is $P^*=(P_1^*,P_2^*,P_3^*).$ A proper scoring rule $S$ is a scoring rule  such that the mean score value 
-	$$E_{P^*}[S(X,P)]=\sum_{x=1}^3 S(x,P)P^*_x$$
-	 is minimized when $P=P^*$.
-	In other words, if one announces
-	$P$ as his probabilistic prediction
-	and $S$ as a scoring rule, the lowest
-	expected penalty is obtained by reporting the correct model's  uncertainty about $X$, $P^*$.
-	Thus, the use of a proper scoring rule encourages the forecaster to announce $P^*$ (the correct one)
-	as his probabilistic prediction  rather than some other quantity. 
-	%Moreover, this method automatically leads to an overall comparison between the outcomes of different personal evaluations concerned with the same totality of events and, therefore, the accumulated score may be considered a concrete measure of success of each model.
+Say a forecaster's uncertainty about $X$ is $P_0$. A proper scoring rule is a scoring rule $S$ such that the prevision value $P_X$ that minimizes $E_{P_0}[S(X,P_X)]$ is $P_0$.
+In other words, if one receives a penalty $S(x,P_X)$ when $x$ happens and if $S$ is a proper scoring rule, then the lowest expected penalty is obtained by reporting one's  true uncertainty about $X$.
+The use of a proper scoring rule thus encourages the forecaster to be honest to minimize the expected penalty.
+Moreover, this method leads automatically to an overall comparison between the outcomes of different personal evaluations concerned with the same totality of events and, therefore, the accumulated score may be considered a concrete measure of success of each forecaster or model.
 
@@
 
-	Let $P=(P_1,P_2,P_3)$ be a probabilistic prediction  for $X$.
-	The Brier score for a given outcome $x\in\{1,2,3\}$ is given by
-	$$S(x,P)= \sum_{i=1}^3\mathbb{I}(x=i)(1- P_i)^2+\sum_{i=1}^3\mathbb{I}(x\neq i)P^2_i,$$
+Let $P_X$ be a probability assignment for $X$.
+The Brier score is given by
+$$S(X;P_X)= \sum_{i}\mathbb{I}(X=x_i)(1- P_X(x_i))^2+\sum_{i}\mathbb{I}(X\neq x_i)P_X^2(x_i),$$
 where $\mathbb{I}$ is the indicator function.
@@
 \end{tikzpicture}
-			\caption{Bi-dimensional simplex (green surface): area of possible forecasts}\label{fig:simplex}
+\caption{Bi-dimensional simplex (green surface): area of possible predictions}\label{fig:simplex}
 \end{center}
@@
 Drawing a similar equilateral triangle with height 1 and sides $2\sqrt{3}/3$, it is possible to represent all points of the simplex.
-	This new triangle is used to graphically display the forecast as a internal point because the sum of the distances of every point inside it to each side, representing the probability of each event, is always one.
+This new triangle is used to graphically display the predictions as internal points because the sum of the distances of every point inside it to each side, representing the probability of each event, is always one.
 
@@
 
-	The Brier score for the probabilistic prediction $P=(0.25,0.35,0.40)$
-	assuming the home team loses, is therefore given by $d^2=(0-0.25)^2+(0-0.35)^2+(1-0.40)^2=0.545$. 
-	On the other hand, the prediction $P=(0,0,1)$ achieves score  zero, the minimum for this rule.
+The Brier score for the prediction $P_X=(0.25,0.35,0.40)$, assuming the home team loses, is therefore given by $d^2=(0-0.25)^2+(0-0.35)^2+(1-0.40)^2=0.545$. 
+If the prediction was $P_X=(0,0,1)$, the score would be zero, the minimum for this rule.
 
-	It is useful to consider the score of what we will call {\it trivial prediction}:
-	$P=(1/3,1/3,1/3)$.
+It is useful to consider the score of what we will call {\it trivial prediction}: $(1/3,1/3,1/3)$.
 This assessment will produce a Brier score of $2/3$, no matter what is the final result of the match, providing, thus, a threshold that a good model should consistently beat, meaning, for the Brier score, that the scores of its predictions should be smaller than $0.667$.
@@
 The logarithmic  score is given by
-	$$S(x,P)=- \sum_{i=1}^3\mathbb{I}(x=i)\ln(P_i),$$
+$$S(X;P_X)=- \sum_{i}\mathbb{I}(X=x_i)\ln(P_X(x_i)),$$
 
@@
 
-	The logarithmic score for the prediction 
-	$P=(0.25,0.35,0.40)$
-		 when the home team loses is therefore 
+The logarithmic score for the prediction $P_X=(0.25,0.35,0.40)$, when the home team loses is therefore 
 $-\ln(0.4)\approx 0.91$. 
-	On the other hand, the prediction $P=(0,0,1)$ achieves score zero, once again the minimum of this rule.
-	Moreover, for the logarithmic score, the trivial prediction gives a score of approximately $1.098$.
+If the prediction was $P_X=(0,0,1)$, the score would be zero, once again the minimum of this rule.
+For the logarithmic score, the trivial prediction gives a score of approximately $1.098$.
 
@@
 The spherical score is given by
-	$$S(x,P)=- \frac{1}{\sqrt{\sum_{i=1}^3 P^2_i}}\sum_{i=1}^3\mathbb{I}(x=x_i)P_i,$$
+$$S(X;P_X)=- \frac{1}{\sqrt{\sum_i P_X^2(x_i)}}\sum_{i}\mathbb{I}(X=x_i)P_X(x_i),$$
 
@@
 
-	The spherical score for the prediction 
-		$P=(0.25,0.35,0.40)$ assuming the home team loses, is given by
+The spherical score for the prediction $P_X=(0.25,0.35,0.40)$, assuming the home team loses, is given by
 $-0.4/\sqrt{0.25^2+0.35^2+0.40^2} \approx -0.68$.
-	On the other hand, the prediction $P=(0,0,1)$ achieves score  $-1$ instead and, for this rule, the trivial prediction results in a score of approximately $-0.577$.
+If the prediction was $P_X=(0,0,1)$, the score would be $-1$ instead and, for this rule, the trivial prediction results in a score of approximately $-0.577$.
 
@@
 The first one is the proportion of errors made by the model or assessor. This is simply the proportion of mistakes made when considering the highest probability assessment.
-	More precisely, the proportion of errors of a a sequence of probabilistic predictions for $n$ games, $P^{(1)},\ldots,P^{(n)}$
-	with
-		$P^{(j)}=(P^{(j)}_1,P^{(j)}_2,P^{(j)}_3)$, is defined by
-	$$\frac{1}{n}\sum_{j=1}^n \mathbb{I}\left(X_j \neq \arg \max_{x \in \{1,2,3\}} P^{(j)}_x\right),$$
-	where $X_j$ is the outcome of the $j$-th match.
+More precisely, the proportion of errors of a given prediction $P_X$ is defined by
+$$\frac{1}{n}\sum_{j=1}^n \mathbb{I}\left(X_j \neq \arg \max_{x} P_X(x_{j})\right),$$
+where $X_j$ is the outcome of the $j$-th match and $P_X(x_{j})$ is the probability attributed to result $x\in\mathcal{X}=\{1,2,3\}$ for the $j$-th match.
 
@@
 
-	Because we typically do not have several predictions with the same assigned probability $p$, we obtain a plot by smoothing (i.e., regressing) the indicator function of whether a given result happened as a function of the probability assigned for that result.
-	That is, we estimate the probability that an event occurs given its assigned probability.
+Because we typically do not have several predictions with the same assigned probability $p$, we obtain a plot by smoothing (i.e., regressing) the indicator function of whether a given result happened as a function of the probability assigned for that result, that is, we estimate the probability that a event occurs given its assigned probability.
 %, that is, we regress  
@@
 
-	%De Finetti used what is called the Brier score, which is just the (squared) Euclidean distance ?
-i.e., the sum of the squared differences between credences and (the 0/1 numerical correlates of) truth values.
+%De Finetti used what is called the Brier score, which is just the (squared) Euclidean distance — i.e., the sum of the squared differences between credences and (the 0/1 numerical correlates of) truth values.
 
@@
 
-		\bibitem{Crowder2002} Crowder, M.; Dixon, M.; Ledford, A.; Robinson, M. Dynamic modelling and prediction of English
-		Football League matches for betting. {\em Journal of the Royal
+\bibitem{Crowder2002} Crowder, M.; Dixon, M.; Ledford, A.; Robinson, M. Dynamic modelling and prediction of English Football League matches for betting. {\em Journal of the Royal
 Statistical Society - Series D} {\bf 2002}, {\em 51}, 157-168.
@@
 Rue, H.; Salvesen, O. Prediction and Retrospective Analysis of
-		Soccer Matches in a League. {\em Journal of the Royal Statistical
+Soccer Matches in a League {\em Journal of the Royal Statistical
 Society - Series D} {\bf 2000}, {\em 49}, 399-418.
@@
 
-=======
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \end{document}

### 2015-07-07 template.tex
Resolvendo conflito.

--- 2015-07-07 template.tex
@@
 
-	How can we fairly rank the various predictive models?
-	A way of doing this is by using proper scoring rules, where
+	One way of fairly rank the various predictive models is by using proper scoring rules, where
 	the score may be interpreted as a numerical measure of how inaccurate was a given probabilistic prediction.
@@
 
-=======
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-07-07 template.tex
Mudancas minimas.

@@
 	See \cite{constantinou} for a brief survey of such measures applied to football.
-	We decided to score the previsions for each match in terms of their distances from the truth, i.e.
+	We decided to score the predictions for each match in terms of their distances from the truth, i.e.
 the verified event, once it has occurred, and chose the most used distances in the literature: Brier \cite{brier1950}, logarithmic and spherical.
@@
 	Section \ref{sec::experimental} describes the proposed models, Section \ref{sec::scoring} presents the scoring rules and criteria used in this work to classify the models.
-	Section \ref{sec::results} reports the performance of the models predicting 190 matches comprising the second half of the Brazilian championship of first division.
+	Section \ref{sec::results} reports the performance of the models predicting 190 matches comprising the second round of the Brazilian championship of first division--each team plays 19 matches each round, since the championship has 20 teams.
 	In Section \ref{sec::remarks} we discuss the results and close with proposals for future research.
@@
 	$x$ occurs.
-Also, the ``best"\footnote{A scoring rule can also be defined to be such that a \emph{large} value of the score indicates good forecasts.} possible score (i.e., the smallest score value) is achieved when the probabilistic prediction for the outcome of the game is perfect.
+Also, the ``best''\footnote{A scoring rule can also be defined to be such that a \emph{large} value of the score indicates good forecasts.} possible score (i.e., the smallest score value) is achieved when the probabilistic prediction for the outcome of the game is perfect.
 	%Most of the scoring rules also exhibit an arbitrary normalizing feature such as $S(x,P_X)=0$ for each $x$.

### 2015-07-07 responseToReferee2.tex
pequena correcao

\documentclass[11pt]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath, graphicx, layout, verbatim}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{float}
\usepackage{color}
\usepackage{natbib}
\usepackage{verbatim}
\usepackage{subfig}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[pagebackref,colorlinks=true,urlcolor=blue,citecolor=blue	,linkcolor=blue]{hyperref}
\textheight25cm \footskip0.5cm \topmargin-1.5cm \headsep0.2cm
\oddsidemargin-0.5cm \evensidemargin-0.5cm
 \marginparwidth0cm \marginparsep = 0pt
\textwidth16cm

\onehalfspacing
\usepackage{cite}
\usepackage{url}
\urlstyle{rm}

\renewcommand{\vec}[1]{\mathbf{#1}}

\def\x{{\vec{x}}}

\def\G{{\mathbb G}}
 \newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
    \def\independenT#1#2{\mathrel{\setbox0\hbox{$#1#2$}%
    \copy0\kern-\wd0\mkern4mu\box0}}

 \def\X{***ATT***}
\newcommand{\red}[1]{\textbf{\color{red} ***ATT*** #1}}

\title{Response to Reviewer 2}
\date{}

\begin{document}

%the paper and
%hope to have answered the questions that were raised.

\maketitle

\hspace{4mm} \textbf{Reviewer:} \textit{
	The authors explore the predictive performance of a few simple Multinomial-Dirichlet (MD)
	models relative to more sophisticated black box type procedures in predicting outcomes of
	football (soccer) matches in the second half of Brazil's division one. They find that under a
	variety of information metrics the simpler models perform similar to the more complicated ones.
	I think the paper is a good fit for the journal as it compares the predictive information gleaned
	from five models developed to predict football outcomes. However, there are a few issues I feel
	should be addressed. I organized my comments into two sections: general and specific.}

\vspace{2mm}
\textbf{Response:} We thank the referee for taking the time reviewing the paper. Below we list our detailed response to the referee's questions.\\

\vspace{6mm}

\hspace{4mm} \textbf{Reviewer:} \textit{\textbf{General Comments.}
	What the authors have shown in my opinion is that the blackbox predictors they consider as
	competitors do not incorporate covariate information effectively and/or the covariates are not
	informative in learning about game outcomes. Even though it is not the focus of the paper,
	it seems to me that including some detail (at least on an intuitive level) of how information is
	used in these black box methods would be helpful in better understanding why they perform so
	poorly relative to the very unsophisticated MD models.}

\vspace{2mm}
\textbf{Response: we added subsection in Section 2 explaining some details of the benchmark models.***Falta o Ernesto***.}

%We believe this may the case because
%of the fact that estimating $\psi_{j}(\vec{x})$'s accurately is relatively hard (see, e.g., Lee and Wasserman 2010).
%Another related issue is that, as noticed by the referee, although $\psi_{j}(\vec{x})$ 
%are orthonormal,
%$\widehat{\psi}_{j}(\vec{x})$ are not.

\vspace{6mm}

\hspace{4mm} \textbf{Reviewer:} \textit{On a related note (and something I discuss a bit more later), it wasn?t entirely clear to me how
	information was used to make game predictions for the black box methods vs the MD models. I
	understand that predictions from the MD model were done sequentially one at a time employing
	the Bayesian method of updating information as more game outcomes where considered. Is this
	what was done with the black box methods? Or where all the second half games predicted only
	using the first games. I think trying to identify why the MD models are performing on par with
	more sophisticated alternatives would be interesting.
}

\vspace{2mm}
\textbf{Response: we added two paragraphs in subsection 2.2 explaining how the models we are proposing were updated. We used all past results of the teams playing against each other up to the matchday that is being predicted. In this sense, all predictions are ``one-step ahead'' predictions. Regarding the benchmark models, subsection 2.1 comments how they use the information to predict the results. Basically, the predictions of the benchmark models are also one-step ahead predictions, even though they could use the information of the first half of the championship to predict all the second half.} 
% \red{I'm not sure!! Does he mean $1/(\lambda_j\Delta_J^2)$ has to be bounded by the same constant for all $j$'s? Recall that $%\lambda_1>\ldots>\lambda_J$ and $\Delta_1 > \ldots > \Delta_J$}

\vspace{6mm}

\hspace{4mm} \textbf{Reviewer:} \textit{\textbf{Section 1: Introduction.} 
	\begin{itemize}
		\item Line 17 page 2 should ``provisions" be ``predictions"?
		\item It may be beneficial to the reader to briefly describe the second half of the Brazilian
		championship. (As an aside, on page 4 instead of using `` second half", ``second round"
		is used. Are you referring to the same set of games?) How many games per team in the
		second half?
	\end{itemize}}

\vspace{2mm}
\textbf{Response: we changed ``previsions'' by ``predictions''. There was a mistake on p. 4 because we should refer to the ``second round''. We fixed this and added a note explaining that each team plays 19 matches each round, since the championship has 20 teams. More details on the championship rule are given in Section 4 (Results).}

\vspace{6mm}

\hspace{4mm} \textbf{Reviewer:} \textit{\textbf{Section 2: The models: theoretical background.} 
	\begin{itemize}
		\item You point out that the assumptions associated for the MD models and black-box models
		are different. Does this make comparing them untenable? If not, why?
	\end{itemize}}

	\vspace{2mm}
	\textbf{Response:***Ernesto, pode ajudar?***}

\vspace{6mm}

\hspace{4mm} \textbf{Reviewer:} \textit{\textbf{Section 2.1: Multinomial-Dirichlet.} 
	\begin{itemize}
		\item In line 8, ``belongs" is misspelled.
		\item The first paragraph of page 4 is somewhat misleading. If I am understanding things cor-
		rectly, predicting the outcome of game $X_{n+m+1}$ is done using games $X_{n+m} ,\ldots , X_m , \ldots , X_1$
		(where games $X_m , \ldots , X_1$ denote the first half games) and are carried out by repeatedly
		using Bayes information updating mechanism (posterior from old study becomes prior for
		new). Therefore, in reality your prior is not $D(1, 1, 1)$ but rather the posterior distribu-
		tion from outcomes of the first half games coupled a $D(1, 1, 1)$ prior. Can you clarify or
		comment on this? Is this how the blackbox methods are being used as well?
	\end{itemize}}

	\vspace{2mm}
	\textbf{Response: we fixed the word ``belongs'', now on subsection 2.2. Regarding the updating of information, the reviewer understood correctly. We rewrote the first paragraph of p.4 to explain the operation in detail. Regarding the blackbox models, subsection 2.1 clarifies how they use available information.}

\vspace{6mm}

\hspace{4mm} \textbf{Reviewer:} \textit{\textbf{Section 2.4: Model 3: Multinomial-Dirichlet 3.} 
	\begin{itemize}
		\item The section title should be ``Model Three:" (spell out the number 3) in order to be
		consistent with outher section headings.
	\end{itemize}}

	\vspace{2mm}
	\textbf{Response: now we spell out 3, as suggested.}

	\vspace{6mm}

	\hspace{4mm} \textbf{Reviewer:} \textit{\textbf{Section 3: Scoring rules and calibration.} 
		\begin{itemize}
			\item The word ``prevision" appears a few times in the first four paragraphs of this section. I
			don't understand it's use. I initially thought ``prediction" was implied, but am not sure.
			\item Related to the previous comment, I understand that $P_X$ is a probability not a prediction of
			say $X_{n+1}$. Predictions of $X_{n+1}$ should live in $X = \{1, 2, 3\}$. Consider revising terminology.
			In reality the first five paragraphs of Section 3 are hard to read. I'd suggest revising
			exposition.
		\end{itemize}}

		\vspace{2mm}
		\textbf{Response: the word ``prevision'' was replaced by ``prediction''. The first paragraphs were all rewritten to better explain the concepts we introduce. Terminology was also reviewed, as suggested.}

\vspace{6mm}

We are grateful to the referee for the insightful comments that helped to improve the quality of our paper. 
We expect to have addressed all his/her concerns. Please feel
free to contact us in case something is still not clear, or if new concerns arise.

\end{document}

### 2015-07-08 template.tex
Mudança mínima por Danilo

@@
 		Assuming that the outcomes from $n$ matches of team $t$, given $\boldsymbol{\theta}$, are i.i.d.
-quantities with the above categorical distribution, and denoting by $M_1$, $M_2$ and $M_3$ the number of matches won, tied or lost by team $t$, the random vector $(M_1, M_2, M_2)$ has multinomial distribution with parameters $n$ and $\boldsymbol{\theta}$ given by
+quantities with the above categorical distribution, and denoting by $M_1$, $M_2$ and $M_3$ the number of matches won, tied or lost by team $t$, the random vector $(M_1, M_2, M_3)$ has multinomial distribution with parameters $n$ and $\boldsymbol{\theta}$ given by
 		\[

### 2015-07-08 template.tex
Correcoes.

@@
 	{\it``Entities are not to be multiplied without necessity''}, but illustrates very well a principle that is not often followed by researchers, especially when building predictive models.
-	This is true also in the literature of probabilistic sports predictions, particularly regarding models devoted to football or soccer\footnote{Henceforth, football.} predictions.
+	This is true also in the literature of probabilistic sports predictions, particularly regarding models devoted to football or soccer (henceforth football) predictions.
 
@@
 	The predictions of the two benchmark models were published on Internet websites before every matchday, and are treated by us as black-box models (BB1 and BB2). 
-	We know that\footnote{One of the authors is responsible for one of these models and the other was described in a dissertation.
-See \cite{arruda2000}.} both models are based on Holgate bivariate Poisson regression considering as explanatory variables the home field advantage, attack and defense strength for each team, and provide the probabilities of all possible outcomes (home team wins, draws or loses) for each match.
-	Because both models are based on elaborate parametric assumptions, they are suitable for the comparison we are proposing: simple versus complex models\footnote{To be precise we would have to define what is a ``simple'' model and what is a ``complex'' model.
-Based on the opening quotations, one may say that the number of parameters defines the complexity of a model, which is not exactly the definition we will use, since we consider other criteria, like the interpretation of explanatory variables and mathematical structure of the statistical model.}.
+	Since one of the authors is responsible for one of these models and the other was described in a dissertation \cite{arruda2000}, we know that both models are based on Holgate bivariate Poisson regression considering as explanatory variables the home field advantage, attack and defense strength for each team, and provide the probabilities of all possible outcomes (home team wins, draws or loses) for each match.
+	Because both models are based on elaborate parametric assumptions, they are suitable for the comparison we are proposing: simple versus complex models.
+To be precise we would have to define what is a ``simple'' model and what is a ``complex'' model.
+Based on the opening quotations, one may say that the number of parameters defines the complexity of a model, which is not exactly the definition we will use, since we consider other criteria, like the interpretation of explanatory variables and mathematical structure of the statistical model.
 
@@
 	$x$ occurs.
-Also, the ``best''\footnote{A scoring rule can also be defined to be such that a \emph{large} value of the score indicates good forecasts.} possible score (i.e., the smallest score value) is achieved when the probabilistic prediction for the outcome of the game is perfect.
+Also, the ``best'' possible score (i.e., the smallest score value) is achieved when the probabilistic prediction for the outcome of the game is perfect.
+A scoring rule can also be defined to be such that a \emph{large} value of the score indicates good forecasts.
 	%Most of the scoring rules also exhibit an arbitrary normalizing feature such as $S(x,P_X)=0$ for each $x$.
@@
 	According to all scoring rules, all methods have similar performance, and they are more accurate than the trivial prediction, displayed in the plots
-	as an horizontal line\footnote{None of the 95\% confidence intervals for the mean score contain the score given by the trivial prediction.}. The mean scores and their standard errors are displayed
+	as an horizontal line. None of the 95\% confidence intervals for the mean score contain the score given by the trivial prediction. The mean scores and their standard errors are displayed
 	in Table \ref{tab::brier}.
@@
 
-	Figure \ref{fig::entropy} presents the boxplots of the entropy of each prediction for the predictive models considered.\footnote{Recall
-		that the entropy of a prediction $(p_1,p_2,p_3)$ is given by $- \sum_{i=1}^3 p_i \log{p_i}$}
+	Figure \ref{fig::entropy} presents the boxplots of the entropy of each prediction for the predictive models considered.
+Recall that the entropy of a prediction $(p_1,p_2,p_3)$ is given by $- \sum_{i=1}^3 p_i \log{p_i}$.
 	Since the entropy values are smaller than 1.09, the plots show that the predictions
@@
 
-	%De Finetti was a radical subjectivist and pragmatist about probability and did not believe that it even made sense to talk about credences as being ``accurate'' or ``inaccurate''.
-	%Like Ramsey and Savage, he offered pragmatic arguments for probabilism.
-	%As a result, de Finetti did not speak of ``measures of inaccuracy'' or ``measures of distance from the truth'': he used the terms ``scoring rule'' and ``loss function''.
-
-	%De Finetti used what is called the Brier score, which is just the (squared) Euclidean distance ?
-i.e., the sum of the squared differences between credences and (the 0/1 numerical correlates of) truth values.
-
-	%In the statistical literature, football prediction models can be divided in two main approaches: (i) modeling the number of goals \citep{Maher82, Dixon97, Karlis2003} and (ii) modeling the final outcome (win, draw or lose) of the matches \citep{Forrest2000, Koning2000, Brillinger2008, Brillinger2009}.
-For a discussion of these two approaches see \cite{Goddard2005}.
 	Although our benchmark models were here defined as complex, we can find much more elaborate models in the literature, hindering the estimation and prediction processes.
-	Among them, we can cite those based on modeling the match as a stochastic process evolving through time \citep{Dixon98, Volf2009, Titman2015}, those allowing for the team performance parameters to
-	change along the season \citep{Rue2000, Crowder2002, Owen2011, Koopman2015} and those modeling dependence between number of goals by means of bivariate count distributions \citep{Dixon97, Karlis2003, McHale2007, McHale2011}.
-
-	%Although the benchmark models were here considered complex models, we can find in the literature much more elaborate models, hindering the estimation and prediction process. 
-	%Among those, we can cite those based on modeling the match as a stochastic process evolving through time \citep{Dixon98, Volf2009, Titman2015}, those allowing for the team performance parameters to change along the season \citep{Rue2000, Crowder2002, Owen2011, Koopman2015} and those modeling dependence between number of goals by means of bivariate count distributions \citep{Dixon97, Karlis2003, McHale2007, McHale2011}.
+	Among them, we can cite those based on modeling the match as a stochastic process evolving through time \citep{Dixon98, Volf2009, Titman2015}, those allowing for the team performance parameters to change along the season \citep{Rue2000, Crowder2002, Owen2011, Koopman2015} and those modeling dependence between number of goals by means of bivariate count distributions \citep{Dixon97, Karlis2003, McHale2007, McHale2011}.
+	However, models build to predict the number of goals must predict a more specific outcome and this usually requires more elaborate modeling.
 
 	According to standard scoring rules and other criteria here adopted to qualify the predictions, our findings show that the predictive power of the three simple models was quite similar to the benchmark models.
-	%We compared the probabilistic predictions of three simple models with the ones provided by two more complex models for the second round of the 2014 Brazilian football championships of first and second divisions.
-	This work thus indicates that while there has been a boom in the literature with the proposal of several fancy and involved models, especially in the era of big data, simple models can many times do
-	as well as their complex counterparts.
+	This work thus indicates that while there has been a boom in the literature with the proposal of several fancy and involved models, especially in the era of big data, simple models can many times do as well as their complex counterparts.
 
 	This is often unnoticed by users of such methods, which leads to the overuse of models that are
-	hard to interpret and to implement, and that also require one to keep track of several covariates. We would call this phenomenon the {\it king's nudity}\footnote{In allusion to Anderson's {\it The
-			Emperor's New Clothes}, \cite{emperor}: ``But he isn't wearing anything at all!''.}, that is not, of course, always observed. 
+	hard to interpret and to implement, and that also require one to keep track of several covariates.
+We would call this phenomenon the {\it king's nudity}, in allusion to Anderson's {\it The Emperor's New Clothes}, \cite{emperor}: ``But he isn't wearing anything at all!''.
+However , we emphasize that this phenomenon is not always observed.
 	In this spirit, since we have explored only the prediction of football matches, we would like to study if the same extends to other fields such as, for instance, weather or economics forecasts.

### 2015-07-08 template.tex
revisao Ernesto

--- 2015-07-07 template.tex
@@
     assumptions about the number of goals each team scores
-	\citep{Maher82, Dixon97, Karlis2003} and models that make
+    \citep{Maher82, Dixon97, Lee97, Karlis2003} and models that make
     assumptions about the categorical final outcome (win, draw or defeat
@@
     \label{sec::Benchmark}
+
+    The benchmark models assume that the number of goals $(Y_1, Y2)$ scored respectively by teams A (home team) and B (away
+    team) follows a bivariate Poisson distribution \citep{Holgate64} with parameters $(\lambda_1, \lambda_2, \lambda_3)$,
+    which has p.m.f given by
+\begin{equation*}
+P(Y_1 = y_1, Y_2 = y_2 | \lambda_1, \lambda_2, \lambda_3) =
+\exp\{-(\lambda_1 + \lambda_2 + \lambda_3)\}
+ \sum_{k = 0}^{\min(y_1, y_2)} \dfrac{\lambda_1^{x - k} \lambda_2^{y - k} \lambda_3^k}{(x-k)!(y -
+ k)!k!}, \label{eq::pois.biv}
+\end{equation*}
+for $\lambda_1, \lambda_2 > 0$ and $\lambda_3 \geq 0$.
+
+Both marginal distributions of $(Y_1, Y_2)$ follow Poisson
+distributions with dependence parameter $\lambda_3 \geq 0$. If
+$\lambda_3 = 0$ the marginal distributions are independent, while if
+$\lambda_3 > 0$ the marginal distributions are positively
+correlated. Because of its flexibility, \cite{Karlis2003} argues
+that this distribution is a plausible choice for modeling dependence
+of scores in sports competitions.
+
+%Following the literature on soccer prediction \citep{Lee97, Karlis2003},
+%both benchmark models assume log-linear link functions for $\lambda_1, \lambda_2$ and $\lambda_3$
+%expressed in terms of team's attack and defensive abilities, and home advantage effect.
+
+Similar to \cite{Lee97} and \cite{Karlis2003}, both benchmark models
+adopt the following log-linear link functions
+\begin{align*}
+\log(\lambda_1) &= \mu + \text{ATT}_A - \text{DEF}_B + \gamma, \\
+\log(\lambda_2) &= \mu + \text{ATT}_B - \text{DEF}_A,
+\end{align*}
+where $\mu$ is a parameter representing the average number of goals
+in a match, $\text{ATT}_k$ is the offensive strength of team k,
+$\text{DEF}_k$ is the defensive strength of team k and $\gamma$ is
+the home advantage for team A, $k = A, B$.
+
+The prediction for an upcoming match-day is obtained by fitting the
+model to all the observed scores up to the previous match-day and
+then summing up the probabilities of all scores relevant to the win,
+draw and loss outcomes of future matches.
 
@@
 
+        \bibitem{emperor}
+        Andersen, H.  C. The emperor's new clothes. Genesis Publishing Pvt Ltd, 1987.
+
         \bibitem{brier1950}
@@
 
-		\bibitem{emperor}
-		Andersen, H.  C. The emperor's new clothes. Genesis Publishing Pvt Ltd, 1987.
-
         \bibitem{Forrest2000} Forrest, D.; Simmons, R. Making up the results: The work
@@
             Forecasting} {\bf 2005}, {\em 21}, 331-340.
+
+        \bibitem{Holgate64}
+        Holgate, P. Estimation for the bivariate Poisson distribution. {\em Biometrika} {\bf 1964}, {\em 51}, 241-287.
 
@@
             philosophical, and historical introduction}. New York: Wiley, 1996.
+
+        \bibitem{Lee97}
+        Lee, A. J. Modeling scores in the Premier League: Is Manchester United really the best? {\em Chance} {\bf 1997}, {\em 10}, 15-19.
 

### 2015-07-08 responseToReferee2.tex
Correcoes na carta.

@@
 
-\title{Response to Reviewer 2}
+\title{Response to Reviewer}
 \date{}
@@
 \begin{document}
-
-%the paper and
-%hope to have answered the questions that were raised.
 
@@
 \vspace{2mm}
-\textbf{Response: we changed ``previsions'' by ``predictions''.
+\textbf{Response: we changed ``previsions'' to ``predictions''.
 There was a mistake on p.
 4 because we should refer to the ``second round''.
-We fixed this and added a note explaining that each team plays 19 matches each round, since the championship has 20 teams.
+We fixed this and added a noted explaining that each team plays 19 matches each round, since the championship has 20 teams.
 More details on the championship rule are given in Section 4 (Results).}

### 2015-07-08 responseToReferee2.tex
Limpando bagunça

--- 2015-07-07 responseToReferee2.tex
@@
 \usepackage{amssymb}
-\usepackage[pagebackref,colorlinks=true,urlcolor=blue,citecolor=blue	,linkcolor=blue]{hyperref}
+\usepackage[pagebackref,colorlinks=true,urlcolor=blue,citecolor=blue, linkcolor=blue]{hyperref}
 \textheight25cm \footskip0.5cm \topmargin-1.5cm \headsep0.2cm
@@
 
-\vspace{2mm}
-\textbf{Response: we added subsection in Section 2 explaining some details of the benchmark models.***Falta o Ernesto***.}
+\vspace{2mm} \textbf{Response: We included a new subsection
+(Subsection 2.1) in Section 2 giving more details about the
+benchmark models considered, which are quite similar to many other
+approaches in the literature. In fact, we believe that soccer
+prediction is really a hard task. This is mainly because several
+factors may have a great influence on the final match outcome such
+as referee's error, receiving a red card, injury of important
+players, weather, among many others. All those factors are difficult
+(maybe impossible) to take into account in any statistical model.
+Thus, the use of elaborated models leads to small gain in prediction
+accuracy when compared to more simpler models, because of the great
+unpredictability of soccer matches.}
 
@@
 4 because we should refer to the ``second round''.
-We fixed this and added a note explaining that each team plays 19 matches each round, since the championship has 20 teams.
+We fixed this and added a noted explaining that each team plays 19 matches each round, since the championship has 20 teams.
 More details on the championship rule are given in Section 4 (Results).}
@@
     \vspace{2mm}
-	\textbf{Response:***Ernesto, pode ajudar?***}
+    \textbf{Response: We believe that in the such cases where the model assumptions are quite different, the only possible comparison are in terms
+    of predictive accuracy. In the present study, this comparison is possible since all the models report the probabilities of win, draw or loss for the home team.
+    Furthermore, from the perspective of soccer fans the most important value of a model is giving ``good'' predictions.}
 

### 2015-07-08 template.tex
Versao final

--- 2015-07-08 template.tex
@@
     {\it``Entities are not to be multiplied without necessity''}, but illustrates very well a principle that is not often followed by researchers, especially when building predictive models.
-	This is true also in the literature of probabilistic sports predictions, particularly regarding models devoted to football or soccer (henceforth football) predictions.
+    This is true also in the literature of probabilistic sports predictions, particularly regarding models devoted to football or soccer (henceforth, football) predictions.
 
@@
     The predictions of the two benchmark models were published on Internet websites before every matchday, and are treated by us as black-box models (BB1 and BB2).
-	Since one of the authors is responsible for one of these models and the other was described in a dissertation \cite{arruda2000}, we know that both models are based on Holgate bivariate Poisson regression considering as explanatory variables the home field advantage, attack and defense strength for each team, and provide the probabilities of all possible outcomes (home team wins, draws or loses) for each match.
+    Since one of the authors is responsible for one of these models and the other was described in a dissertation \citep{arruda2000}, we know that both models are based on Holgate bivariate Poisson regression considering as explanatory variables the home field advantage, attack and defense strength for each team, and provide the probabilities of all possible outcomes (home team wins, draws or loses) for each match.
     Because both models are based on elaborate parametric assumptions, they are suitable for the comparison we are proposing: simple versus complex models.
-To be precise we would have to define what is a ``simple'' model and what is a ``complex'' model.
+To be precise, we would have to define what is a ``simple'' model and what is a ``complex'' model.
 Based on the opening quotations, one may say that the number of parameters defines the complexity of a model, which is not exactly the definition we will use, since we consider other criteria, like the interpretation of explanatory variables and mathematical structure of the statistical model.
@@
 Also, the ``best'' possible score (i.e., the smallest score value) is achieved when the probabilistic prediction for the outcome of the game is perfect.
-A scoring rule can also be defined to be such that a \emph{large} value of the score indicates good forecasts.
+A scoring rule may also be defined to be such that a large value of the score indicates good forecasts.
         %Most of the scoring rules also exhibit an arbitrary normalizing feature such as $S(x,P_X)=0$ for each $x$.
@@
     $P$ as his probabilistic prediction
-	and $S$ as a scoring rule, the lowest
+    and uses $S$ as scoring rule, the lowest
     expected penalty is obtained by reporting the correct model's  uncertainty about $X$, $P^*$.
@@
 
-	Figure \ref{fig::entropy} presents the boxplots of the entropy of each prediction for the predictive models considered.
-Recall that the entropy of a prediction $(p_1,p_2,p_3)$ is given by $- \sum_{i=1}^3 p_i \log{p_i}$.
+    Figure \ref{fig::entropy} presents the boxplots of the entropy of each prediction for the predictive models considered. Recall
+        that the entropy of a prediction $(p_1,p_2,p_3)$ is given by $- \sum_{i=1}^3 p_i \log{p_i}$.
     Since the entropy values are smaller than 1.09, the plots show that the predictions
@@
     Among them, we can cite those based on modeling the match as a stochastic process evolving through time \citep{Dixon98, Volf2009, Titman2015}, those allowing for the team performance parameters to change along the season \citep{Rue2000, Crowder2002, Owen2011, Koopman2015} and those modeling dependence between number of goals by means of bivariate count distributions \citep{Dixon97, Karlis2003, McHale2007, McHale2011}.
-	However, models build to predict the number of goals must predict a more specific outcome and this usually requires more elaborate modeling.
+Models that predict the number of goals have more specific objectives than those prediciting the final outcomes and therefore require more elaborate modeling, justifying the complexity of such models.
 
     According to standard scoring rules and other criteria here adopted to qualify the predictions, our findings show that the predictive power of the three simple models was quite similar to the benchmark models.
-	This work thus indicates that while there has been a boom in the literature with the proposal of several fancy and involved models, especially in the era of big data, simple models can many times do as well as their complex counterparts.
+    %We compared the probabilistic predictions of three simple models with the ones provided by two more complex models for the second round of the 2014 Brazilian football championships of first and second divisions.
+    This work thus indicates that while there has been a boom in the literature with the proposal of several fancy and involved models, especially in the era of big data, simple models can many times do
+    as well as their complex counterparts.
 
@@
     hard to interpret and to implement, and that also require one to keep track of several covariates.
-We would call this phenomenon the {\it king's nudity}, in allusion to Anderson's {\it The Emperor's New Clothes}, \cite{emperor}: ``But he isn't wearing anything at all!''.
-However , we emphasize that this phenomenon is not always observed.
+We would call this phenomenon the {\it king's nudity} in allusion to Anderson's {\it The Emperor's New Clothes}, \cite{emperor}: ``But he isn't wearing anything at all!''.
+However, this is not always the case.
 In this spirit, since we have explored only the prediction of football matches, we would like to study if the same extends to other fields such as, for instance, weather or economics forecasts.

### 2015-07-08 response.tex
Nova carta.
Ernesto comments

--- 2015-07-07 responseToReferee2.tex
@@
 \vspace{2mm}
-\textbf{Response: we added subsection in Section 2 explaining some details of the benchmark models.***Falta o Ernesto***.}
+\textbf{Response: We included a new subsection
+	(Subsection 2.1) in Section 2 giving more details about the
+	benchmark models considered, which are similar to many other
+	approaches in the literature. In fact, we believe that football
+	prediction is a hard task. This is mainly because several
+	factors may influence the final outcome of a match, such
+	as referee's mistakes, expulsions or injuries of important
+	players, weather conditions, among many others. All those factors are difficult
+	(maybe impossible) to take into account in any statistical model.
+	Thus, the use of elaborate models leads to small gain in prediction
+	accuracy when compared to simpler models, because of the great
+	unpredictability of football matches.}
 
@@
 	\vspace{2mm}
-	\textbf{Response:***Ernesto, pode ajudar?***}
+	\textbf{Response: We believe that iwhen the model assumptions are different, the only possible comparison are in terms
+		of predictive accuracy. In the present study, this comparison is possible since all the models report the probabilities of win, draw or loss of the home team.
+		Furthermore, from the perspective of football fans the most important feature of a model is to provide ``good'' predictions.}
 

### 2015-08-14 template.tex

@@
     {\it``Entities are not to be multiplied without necessity''}, but illustrates very well a principle that is not often followed by researchers, especially when building predictive models.
-    This is true also in the literature of probabilistic sports predictions, particularly regarding models devoted to football or soccer (henceforth, football) predictions.
+    This is true also in the literature of probabilistic sports predictions, particularly regarding models devoted to football or soccer {\color{red}(henceforth, football)} predictions.
 
@@
     To answer this, we compared two sophisticated models that consider multiple covariates with simple multinomial-Dirichlet models that consider only the number of matches won, tied or lost by each team as inputs.
-    The models were tested for the second round of the Brazilian football championships of first division and compared using standard metrics or scoring rules.
+    The models were tested for the second round of the Brazilian football championship of first division and compared using standard metrics or scoring rules.
     We also used other criteria such as the proportion of matches that were predicted ``correctly'' by each model and a measure of calibration, both explained in detail below.
@@
     The predictions of the two benchmark models were published on Internet websites before every matchday, and are treated by us as black-box models (BB1 and BB2).
-    Since one of the authors is responsible for one of these models and the other was described in a dissertation \citep{arruda2000}, we know that both models are based on Holgate bivariate Poisson regression considering as explanatory variables the home field advantage, attack and defense strength for each team, and provide the probabilities of all possible outcomes (home team wins, draws or loses) for each match.
+    {\color{red} Since one of the authors is responsible for one of these models and the other was described in a dissertation \citep{arruda2000}}, we know that both models are based on Holgate bivariate Poisson regression considering as explanatory variables the home field advantage, attack and defense strength of each team, and provide the probabilities of all possible outcomes (home team wins, draws or loses) for each match.
     Because both models are based on elaborate parametric assumptions, they are suitable for the comparison we are proposing: simple versus complex models.
-To be precise, we would have to define what is a ``simple'' model and what is a ``complex'' model.
-Based on the opening quotations, one may say that the number of parameters defines the complexity of a model, which is not exactly the definition we will use, since we consider other criteria, like the interpretation of explanatory variables and mathematical structure of the statistical model.
+
+    {\color{red} To be precise, we would have to define what is a ``simple'' model and what is a ``complex'' model.
+Based on the opening quotations, one may say that the number of parameters defines the complexity of a model, which is not exactly the definition we will use, since we consider other criteria, like the interpretation of explanatory variables and mathematical structure of the statistical model.}
 
@@
     Section \ref{sec::experimental} describes the proposed models, Section \ref{sec::scoring} presents the scoring rules and criteria used in this work to classify the models.
-    Section \ref{sec::results} reports the performance of the models predicting 190 matches comprising the second round of the Brazilian championship of first division--each team plays 19 matches each round, since the championship has 20 teams.
+    Section \ref{sec::results} reports the performance of the models predicting 190 matches comprising the second round of the Brazilian championship of first division---{\color{red}each team plays 19 matches each round, since the championship has 20 teams.}
     In Section \ref{sec::remarks} we discuss the results and close with proposals for future research.
@@
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    \subsection{Benchmark Models}
+    {\color{red} \subsection{Benchmark Models}
     \label{sec::Benchmark}
 
-    The benchmark models assume that the number of goals $(Y_1, Y2)$ scored respectively by teams A (home team) and B (away
-    team) follows a bivariate Poisson distribution \citep{Holgate64} with parameters $(\lambda_1, \lambda_2, \lambda_3)$,
-    which has p.m.f given by
+    The benchmark models assume that the number of goals $(Y_1, Y2)$ scored respectively by teams $A$ (home team) and $B$ (away
+    team) has a bivariate Poisson distribution \citep{Holgate64} with parameters $(\lambda_1, \lambda_2, \lambda_3)$,
+    which has probability mass function given by
 \begin{equation*}
@@
 
-Both marginal distributions of $(Y_1, Y_2)$ follow Poisson
+Both marginal distributions of $(Y_1, Y_2)$ has Poisson
 distributions with dependence parameter $\lambda_3 \geq 0$. If
@@
 where $\mu$ is a parameter representing the average number of goals
-in a match, $\text{ATT}_k$ is the offensive strength of team k,
-$\text{DEF}_k$ is the defensive strength of team k and $\gamma$ is
-the home advantage for team A, $k = A, B$.
+in a match, $\text{ATT}_k$ is the offensive strength of team $k$,
+$\text{DEF}_k$ is the defensive strength of team $k$ and $\gamma$ is
+the home advantage for team $A$, $k = A, B$.
 
-The prediction for an upcoming match-day is obtained by fitting the
+The prediction for an upcoming matchday is obtained by fitting the
 model to all the observed scores up to the previous match-day and
 then summing up the probabilities of all scores relevant to the win,
-draw and loss outcomes of future matches.
+draw and loss outcomes of future matches.}
 
@@
 
-        In this work, we are interested in checking the predictive performance of the Multinomial-Dirichlet
+        {\color{red} In this work, we are interested in checking the predictive performance of the Multinomial-Dirichlet
         model for the result of every single match in the second round of the championship given the results
@@
         black-box models make predictions from a frequentist perspective; BB1 uses scores of every match
-        in the previous two years, while BB2 uses the match scores of the current championship only.
+        in the previous two years, while BB2 uses the match scores of the current championship only.}
 
         Before we explain and illustrate the proposed models with an example, we make two further remarks.
-        The first one is that we will separately consider home and away games for each team. This will allow us to take into account the different performances under those conditions.
+        The first one is that we will separately consider home and away games for each team, allowing us to take into account the different performances under these conditions.
         The second remark is that the prediction of an upcoming match between two teams $A$ and $B$ can be done using
@@
 
-    \section{Scoring rules and calibration}
+    {\color{red}\section{Scoring rules and calibration}
     \label{sec::scoring}
@@
 A scoring rule may also be defined to be such that a large value of the score indicates good forecasts.
-        %Most of the scoring rules also exhibit an arbitrary normalizing feature such as $S(x,P_X)=0$ for each $x$.
 
@@
     Thus, the use of a proper scoring rule encourages the forecaster to announce $P^*$ (the correct one)
-    as his probabilistic prediction  rather than some other quantity.
+    as his probabilistic prediction  rather than some other quantity.}
     %Moreover, this method automatically leads to an overall comparison between the outcomes of different personal evaluations concerned with the same totality of events and, therefore, the accumulated score may be considered a concrete measure of success of each model.
@@
 
-    Figure \ref{fig::entropy} presents the boxplots of the entropy of each prediction for the predictive models considered. Recall
-        that the entropy of a prediction $(p_1,p_2,p_3)$ is given by $- \sum_{i=1}^3 p_i \log{p_i}$.
+    Figure \ref{fig::entropy} presents the boxplots of the entropy of each prediction for the predictive models considered. {\color{red} Recall
+        that the entropy of a prediction $(p_1,p_2,p_3)$ is given by $- \sum_{i=1}^3 p_i \log{p_i}$.}
     Since the entropy values are smaller than 1.09, the plots show that the predictions
@@
     Among them, we can cite those based on modeling the match as a stochastic process evolving through time \citep{Dixon98, Volf2009, Titman2015}, those allowing for the team performance parameters to change along the season \citep{Rue2000, Crowder2002, Owen2011, Koopman2015} and those modeling dependence between number of goals by means of bivariate count distributions \citep{Dixon97, Karlis2003, McHale2007, McHale2011}.
-Models that predict the number of goals have more specific objectives than those prediciting the final outcomes and therefore require more elaborate modeling, justifying the complexity of such models.
+{\color{red} Models that predict the number of goals have more specific objectives than those prediciting the final outcomes and therefore require more elaborate modeling, justifying the complexity of such models}.
 
@@
     hard to interpret and to implement, and that also require one to keep track of several covariates.
-We would call this phenomenon the {\it king's nudity} in allusion to Anderson's {\it The Emperor's New Clothes}, \cite{emperor}: ``But he isn't wearing anything at all!''.
+We would call this phenomenon the {\it king's nudity} {\color{red} in allusion to Anderson's {\it The Emperor's New Clothes}, \cite{emperor}: ``But he isn't wearing anything at all!''}.
 However, this is not always the case.

### 2015-08-14 template.tex
final remarks update

--- 2015-07-08 template.tex
@@
     The predictions of the two benchmark models were published on Internet websites before every matchday, and are treated by us as black-box models (BB1 and BB2).
-    Since one of the authors is responsible for one of these models and the other was described in a dissertation \citep{arruda2000}, we know that both models are based on Holgate bivariate Poisson regression considering as explanatory variables the home field advantage, attack and defense strength for each team, and provide the probabilities of all possible outcomes (home team wins, draws or loses) for each match.
+    Since one of the authors is responsible for one of these models and the other was described in a dissertation \citep{arruda2000}, we know that both models are based on Holgate bivariate Poisson regression considering as explanatory variables the home field advantage, attack and defense strength of each team, and provide the probabilities of all possible outcomes (home team wins, draws or loses) for each match.
     Because both models are based on elaborate parametric assumptions, they are suitable for the comparison we are proposing: simple versus complex models.
+
     To be precise, we would have to define what is a ``simple'' model and what is a ``complex'' model.
@@
     Section \ref{sec::experimental} describes the proposed models, Section \ref{sec::scoring} presents the scoring rules and criteria used in this work to classify the models.
-    Section \ref{sec::results} reports the performance of the models predicting 190 matches comprising the second round of the Brazilian championship of first division--each team plays 19 matches each round, since the championship has 20 teams.
+    Section \ref{sec::results} reports the performance of the models predicting 190 matches comprising the second round of the Brazilian championship of first division---each team plays 19 matches each round, since the championship has 20 teams.
     In Section \ref{sec::remarks} we discuss the results and close with proposals for future research.
@@
 
-    The benchmark models assume that the number of goals $(Y_1, Y2)$ scored respectively by teams A (home team) and B (away
-    team) follows a bivariate Poisson distribution \citep{Holgate64} with parameters $(\lambda_1, \lambda_2, \lambda_3)$,
-    which has p.m.f given by
+    The benchmark models assume that the number of goals $(Y_1, Y_2)$ scored respectively by teams $A$ (home team) and $B$ (away
+    team) has a bivariate Poisson distribution \citep{Holgate64} with parameters $(\lambda_1, \lambda_2, \lambda_3)$,
+    which has probability mass function given by
 \begin{equation*}
@@
 where $\mu$ is a parameter representing the average number of goals
-in a match, $\text{ATT}_k$ is the offensive strength of team k,
-$\text{DEF}_k$ is the defensive strength of team k and $\gamma$ is
-the home advantage for team A, $k = A, B$.
+in a match, $\text{ATT}_k$ is the offensive strength of team $k$,
+$\text{DEF}_k$ is the defensive strength of team $k$ and $\gamma$ is
+the home advantage, $k = A, B$.
 
-The prediction for an upcoming match-day is obtained by fitting the
+The prediction for an upcoming matchday is obtained by fitting the
 model to all the observed scores up to the previous match-day and
@@
         Before we explain and illustrate the proposed models with an example, we make two further remarks.
-        The first one is that we will separately consider home and away games for each team. This will allow us to take into account the different performances under those conditions.
+        The first one is that we will separately consider home and away games for each team, allowing us to take into account the different performances under these conditions.
         The second remark is that the prediction of an upcoming match between two teams $A$ and $B$ can be done using
@@
     %We compared the probabilistic predictions of three simple models with the ones provided by two more complex models for the second round of the 2014 Brazilian football championships of first and second divisions.
-    This work thus indicates that while there has been a boom in the literature with the proposal of several fancy and involved models, especially in the era of big data, simple models can many times do
-    as well as their complex counterparts.
+    {\color{red}This work thus indicates that while there has been a boom in the literature with the proposal of several fancy and involved models, especially in the era of big data, simple models can many times predict the final outcome as well as their complex counterparts.
+Nevertheless, the complex models cited here are able to answer different questions besides the final outcome that the simple multinomial models are not, for instance, they can estimate teams' performance parameters allowing for ranking teams according to attack and deffensive quality.
+Thus, we can not assert that complex models are useless.}
 
@@
     hard to interpret and to implement, and that also require one to keep track of several covariates.
-We would call this phenomenon the {\it king's nudity} in allusion to Anderson's {\it The Emperor's New Clothes}, \cite{emperor}: ``But he isn't wearing anything at all!''.
+We would call this phenomenon the {\it king's nudity} { in allusion to Anderson's {\it The Emperor's New Clothes}, \cite{emperor}: ``But he isn't wearing anything at all!''.
 However, this is not always the case.

### 2015-08-16 template.tex
revisao rafael

@@
 % Abstract (Do not use inserted blank lines, i.e. \\)
-\abstract{We create three simple multinomial-Dirichlet models and compare them to two well-known sophisticated statistical models for association football (soccer) predictions according to their performance in predicting the full-time results for the second round of the 2014 Brazilian first division championship.
+\abstract{We create three simple multinomial-Dirichlet models and compare them to  two 
+well-known sophisticated statistical models for association football (soccer) predictions according to their performance in predicting the full-time results for the second round of the 2014 Brazilian first division championship.
 The predictive models are compared using three proper scoring rules, the proportion of errors and the calibration assessment.
-Our results show similar predictive performances for all the five methods, thus discouraging the use of overcomplicated models for match result forecast.}
+Our results show similar predictive performances for all the five methods, thus {\color{blue} indicating that the new models offer simpler and more interpretable
+predictions while maintaining predictive power. This  discourages the use of the two popular models for match result forecast in the Brazilian football championship.}}
 
@@
 	Bothered by such concerns, our goal was to answer the following question: is it possible, using a simple probabilistic model, to predict results of football matches better than more sophisticated or complex models?
-    To answer this, we compared two sophisticated models that consider multiple covariates with simple multinomial-Dirichlet models that consider only the number of matches won, tied or lost by each team as inputs.
+	{\color{blue}To answer this, we developed simple multinomial-Dirichlet models that consider only the number of matches won, tied or lost by each team as inputs.
+We then compared them with the two most popular
+	 models used to predict the outcomes of the Brazilian football championship. These two sophisticated models are widely used by football fans, and  they consider multiple covariates as inputs.}
 	The models were tested for the second round of the Brazilian football championship of first division and compared using standard metrics or scoring rules. 
@@
 
-    The predictions of the two benchmark models were published on Internet websites before every matchday, and are treated by us as black-box models (BB1 and BB2).
+	The predictions of the two benchmark models are published on Internet websites before every matchday, and are treated by us as black-box models (BB1 and BB2).
 	Since one of the authors is responsible for one of these models and the other was described in a dissertation \citep{arruda2000}, we know that both models are based on Holgate bivariate Poisson regression considering as explanatory variables the home field advantage, attack and defense strength of each team, and provide the probabilities of all possible outcomes (home team wins, draws or loses) for each match.
-    Because both models are based on elaborate parametric assumptions, they are suitable for the comparison we are proposing: simple versus complex models.
+{\color{red}sugiro tirar - Because both models are based on elaborate parametric assumptions, they are suitable for the comparison we are proposing: simple versus complex models. 
+	}
 
-    To be precise, we would have to define what is a ``simple'' model and what is a ``complex'' model.
-Based on the opening quotations, one may say that the number of parameters defines the complexity of a model, which is not exactly the definition we will use, since we consider other criteria, like the interpretation of explanatory variables and mathematical structure of the statistical model.
+	{\color{red}sugiro tirar -To be precise, we would have to define what is a ``simple'' model and what is a ``complex'' model.
+Based on the opening quotations, one may say that the number of parameters defines the complexity of a model, which is not exactly the definition we will use, since we consider other criteria, like the interpretation of explanatory variables and mathematical structure of the statistical model.}
 
@@
 
-    Although our benchmark models were here defined as complex, we can find much more elaborate models in the literature, hindering the estimation and prediction processes.
+	{\color{blue}The benchmark models used in this work were chosen because of their wide popularity among football fans in Brazil.
+	Several other models are also available in the literature, some of which are even more complex.
 	Among them, we can cite those based on modeling the match as a stochastic process evolving through time \citep{Dixon98, Volf2009, Titman2015}, those allowing for the team performance parameters to change along the season \citep{Rue2000, Crowder2002, Owen2011, Koopman2015} and those modeling dependence between number of goals by means of bivariate count distributions \citep{Dixon97, Karlis2003, McHale2007, McHale2011}.
-Models that predict the number of goals have more specific objectives than those prediciting the final outcomes and therefore require more elaborate modeling, justifying the complexity of such models.
+Contrary to the simple multinomial models we propose,	some of these approaches are able to answer several questions;  for instance, they can estimate teams' performance parameters allowing for ranking teams according to attack and deffensive quality, and
+ they can also predict the final outcomes of matches. We therefore do not claim that our models should replace
+	current state-of-the-art approaches. Instead, this work
+	indicates that while there has been a boom in the literature with the proposal of several fancy and involved models,
+	simple models can many times predict the final outcome as well as their complex counterparts. 
+	The importance of such finding is directly related to the model's usability in practice: creators of the
+	benchmark models used in this work often say a difficulty they face is that
+	wrong predictions often  generate anger in football fans, which is then translated into distrust
+	in subsequent predictions. Because of the complexity of those models, they find it hard to explain predicted outcomes
+	to users. This is where using simple models pays off:  the multinomial models yield results that are
+	easy to explain; they simply involve counts of losses, wins and draws!
+	They allow us to offer simple explanations to the football fans about the predictions that were made.}
 
-    According to standard scoring rules and other criteria here adopted to qualify the predictions, our findings show that the predictive power of the three simple models was quite similar to the benchmark models.
-    %We compared the probabilistic predictions of three simple models with the ones provided by two more complex models for the second round of the 2014 Brazilian football championships of first and second divisions.
-    {\color{red}This work thus indicates that while there has been a boom in the literature with the proposal of several fancy and involved models, especially in the era of big data, simple models can many times predict the final outcome as well as their complex counterparts.
-Nevertheless, the complex models cited here are able to answer different questions besides the final outcome that the simple multinomial models are not, for instance, they can estimate teams' performance parameters allowing for ranking teams according to attack and deffensive quality.
-Thus, we can not assert that complex models are useless.}
-
-    This is often unnoticed by users of such methods, which leads to the overuse of models that are
+{\color{blue}The fact that simple models are often as effective as their competitors is often unnoticed by users of such methods, which leads to the overuse of models that are often
 	hard to interpret and to implement, and that also require one to keep track of several covariates.
-We would call this phenomenon the {\it king's nudity} { in allusion to Anderson's {\it The Emperor's New Clothes}, \cite{emperor}: ``But he isn't wearing anything at all!''.
-However, this is not always the case.
-In this spirit, since we have explored only the prediction of football matches, we would like to study if the same extends to other fields such as, for instance, weather or economics forecasts.
+We would call this phenomenon the {\it king's nudity}  in allusion to Anderson's {\it The Emperor's New Clothes}, \cite{emperor}: ``But he isn't wearing anything at all!''.
+In this spirit, since we have explored only the prediction of football matches in the specific case o Brazilian football championship, we would like to study if the same extends to other fields such as, for instance, weather or economics forecasts.}
 

### 2015-08-20 template.tex
tentativa de responder ao famigerado ponto 2

@@
 \newcommand{\green}[1]{\textbf{\color{green} ***ATT*** #1}}
+
+\definecolor{darkgreen}{RGB}{15,127,0}
 
@@
 
+	{\color{darkgreen}Our analyses therefore show that, marginally, all methods yield similar scores in average, i.e., they have similar predictive power. A related question
+	is whether, at each match, the performance of the methods is also similar. Figure \ref{fig::scores2} displays pairwise comparisons
+	of the various score between the five models we investigate. All methods present
+	a reasonable agreement among each other. Evidently, the Multinomial-Dirichlet models
+	are the ones where there is largest agreement. To formally test the hypotheses that the models yield the same scores in average for
+	each match,
+	we use Friedman's rank sum test. All p-values are not significant at the level 5\% (Brier: 0.077; Spherical: 0.055; Proportion
+	of errors: 0.655), except for the logarithmic
+	score, which has p-value of 0.021. Post-hoc analyses show that the differences are in Mn-Dir$_1$ versus BB2 (p=0.031),
+	Mn-Dir$_2$ versus BB1 (p=0.043), and Mn-Dir$_3$ versus BB1 (p=0.030). These results thus indicate that BB1 and BB2
+	are similar to each other in terms of predictive power, while the performance of Mn-Dir models differ from the BB's \emph{for each match}.
+	We therefore conclude that while the models we investigate may yield different scores for each
+	match according to some metrics, the overall scores are similar. That is, while in some matches Mn-Dir models
+	have better results, for others BB models have better performance. However, in the long term, all methods have similar accuracy.
+	}
+
+		\begin{figure}[H]
+			\centering
+			\includegraphics[page=13,scale=0.48]{futebolComparacaoModelosForPaper.pdf}
+			\includegraphics[page=14,scale=0.48]{futebolComparacaoModelosForPaper.pdf}\\
+			\caption{Pairwise comparison of the various scores. Left plot: upper right plots display Brier Scores;
+			lower left plots display Logarithmic Scores. Right plot: upper right plots display proportion of agreements
+			between methods; lower left  plots display Spherical Scores. Red line represents the identity $x=y$.}
+			\label{fig::scores2}
+		\end{figure}
+
 	We also evaluated how reasonable were the predictions by assessing the calibration of the methods considered, i.e., by evaluating how often events which have assigned probability $p$ (for each $0<p<1$) happened (Section \ref{sec::calib}).
@@
 
-	We therefore conclude that all methods have similar predictive power, and none of them is more informative in average.
-	Nevertheless, all methods yielded better predictions than the trivial prediction, and they are well-calibrated.
+	{\color{darkgreen}We therefore conclude that 
+	although the accuracy of each method may depend on the specific characteristics of each match,
+	all methods have similar predictive power, and none of them is more informative  in average. 
+    Moreover, all methods yielded better predictions than the trivial prediction, and they were all well-calibrated.}
 
@@
 
-{\color{blue}The fact that simple models are often as effective as their competitors is often unnoticed by users of such methods, which leads to the overuse of models that are often
+{\color{blue}The fact that simple models are often as effective as their competitors in average is often unnoticed by users of such methods, which leads to the overuse of models that are often
 	hard to interpret and to implement, and that also require one to keep track of several covariates.
@@
 		If, on the one hand, our findings appear as another supportive example of Ockham's razor, on the other they pose several questions about probabilistic prediction of sport events.
-		In particular, based on the fact that the models have similar performance, one may ask: is there an irreducible ``randomness'' or ``degree of unpredictability'' implicit in these events?
+		In particular, based on the fact that the models have similar {\color{darkgreen}predictive power in average}, one may ask: is there an irreducible ``randomness'' or ``degree of unpredictability'' implicit in these events?
 		Is this degree an indicator of how tight or leveled is the championship being studied?

### 2015-08-21 template.tex
Ajeitando alteracoes.

--- 2015-08-16 template.tex
@@
 Our results show similar predictive performances for all the five methods, thus {\color{blue} indicating that the new models offer simpler and more interpretable
-predictions while maintaining predictive power. This  discourages the use of the two popular models for match result forecast in the Brazilian football championship.}}
+predictions while maintaining predictive power.}}% This  discourages the use of two popular models for match result forecast in the Brazilian football championship.}}
 
@@
 	{\color{blue}To answer this, we developed simple multinomial-Dirichlet models that consider only the number of matches won, tied or lost by each team as inputs.
-We then compared them with the two most popular
-	 models used to predict the outcomes of the Brazilian football championship. These two sophisticated models are widely used by football fans, and  they consider multiple covariates as inputs.}
+We compared these models with two popular models in Brazil, whose predictions for matches of the Brazilian national championships are published on Internet websites.
+These two sophisticated models are widely consulted by football fans and consider multiple covariates as inputs.}
 	The models were tested for the second round of the Brazilian football championship of first division and compared using standard metrics or scoring rules. 
@@
 	Since one of the authors is responsible for one of these models and the other was described in a dissertation \citep{arruda2000}, we know that both models are based on Holgate bivariate Poisson regression considering as explanatory variables the home field advantage, attack and defense strength of each team, and provide the probabilities of all possible outcomes (home team wins, draws or loses) for each match.
-{\color{red}sugiro tirar - Because both models are based on elaborate parametric assumptions, they are suitable for the comparison we are proposing: simple versus complex models. 
-	}
-
-	{\color{red}sugiro tirar -To be precise, we would have to define what is a ``simple'' model and what is a ``complex'' model.
+%{\color{red}sugiro tirar - Because both models are based on elaborate parametric assumptions, they are suitable for the comparison we are proposing: simple versus complex models.}
+
+	%{\color{red}sugiro tirar -To be precise, we would have to define what is a ``simple'' model and what is a ``complex'' model.
 Based on the opening quotations, one may say that the number of parameters defines the complexity of a model, which is not exactly the definition we will use, since we consider other criteria, like the interpretation of explanatory variables and mathematical structure of the statistical model.}
@@
 	\noindent where $\alpha_{\bullet} =\alpha_1+\alpha_2+\alpha_3$.
+	{\color{darkgreen} In fact, the multinomial-Dirichlet is a classical model used in several applied works and more information about it can be found in \cite{good1965}, \cite{bernardo1994} and references therein.}
 
@@
 	round becomes the prior for the second round, which, for every matchday in the second round, will be combined with all the observed second-round matches
-	up to that matchday in order to yield posterior predictive distributions. Note that, on the other hand, the two
+	up to that matchday in order to yield posterior predictive distributions. {\color{darkgreen}For more on the uniform prior on the simplex, see \cite{agresti2010} and \cite{good1965}.}
+
+	Note that, on the other hand, the two
 	black-box models make predictions from a frequentist perspective; BB1 uses scores of every match
@@
 
+	%{\color{darkgreen}Therefore, our analyses show that, marginally, all methods yield similar scores in average, i.e., they have similar predictive power. A related question
+	%is whether, for each match, the performance of the methods is also similar. Figure \ref{fig::scores2} displays pairwise comparisons
+	%of the various score between the five models we investigate. All methods present
+	%a reasonable agreement among each other. Evidently, the Multinomial-Dirichlet models
+	%are the ones where there is largest agreement. To formally test the hypotheses that the models yield the same scores in average for
+	%each match,
+	%we use Friedman's rank sum test. All p-values are not significant at the level 5\% (Brier: 0.077; Spherical: 0.055; Proportion
+	%of errors: 0.655), except for the logarithmic
+	%score, which has p-value of 0.021. Post-hoc analyses show that the differences are in Mn-Dir$_1$ versus BB2 (p=0.031),
+	%Mn-Dir$_2$ versus BB1 (p=0.043), and Mn-Dir$_3$ versus BB1 (p=0.030). These results thus indicate that BB1 and BB2
+	%are similar to each other in terms of predictive power, while the performance of Mn-Dir models differ from the BB's \emph{for each match}.
+	%We therefore conclude that while the models we investigate may yield different scores for each
+	%match according to some metrics, the overall scores are similar. That is, while in some matches Mn-Dir models
+	%have better results, for others BB models have better performance. However, in the long term, all methods have similar accuracy.
+	%}
+	{\color{darkgreen}Therefore, our analyses show that all methods yield similar scores in average, i.e., they have similar predictive power. A related question
+	is whether, for each match, the performance of the methods is also similar.
+To answer this question we compared the models pairwise, and the result is found on Figure \ref{fig::scores2}, where the plots display the scores of each match for every couple of models considered.
+The plots show that all methods are reasonably similar and, evidently, the Multinomial-Dirichlet models
+	are the ones that agree the most.
+To formally test the hypotheses that the models yield the same scores in average for each match, we used Friedman's rank sum test.
+Except for the logarithmic score (p-value 0.021), all the other metrics did not present significant differences at the level of confidence of 5\% (Brier: 0.077; Spherical: 0.055; Proportion of errors: 0.655).
+Post-hoc analyses show that the differences are in Mn-Dir$_1$ versus BB2 (p=0.031),
+	Mn-Dir$_2$ versus BB1 (p=0.043), and Mn-Dir$_3$ versus BB1 (p=0.030). These results thus indicate that BB1 and BB2
+	are similar to each other in terms of predictive power, while the performance of Mn-Dir models differ from the BB models \emph{for each match}.
+	We therefore conclude that while the models we investigate may yield different scores for each
+	match according to some metrics, the overall scores are similar, i. e., while in some matches Mn-Dir models
+	have better results, for others BB models have better performance. However, for a large set of matches, all methods have similar accuracy.
+	}
+
+		\begin{figure}[H]
+			\centering
+			\includegraphics[page=13,scale=0.48]{futebolComparacaoModelosForPaper.pdf}
+			\includegraphics[page=14,scale=0.48]{futebolComparacaoModelosForPaper.pdf}\\
+			\caption{Pairwise comparison of the various scores. Left plot: upper right plots display Brier Scores;
+			lower left plots display Logarithmic Scores. Right plot: upper right plots display proportion of agreements
+			between methods; lower left  plots display Spherical Scores. Red line represents the identity $x=y$.}
+			\label{fig::scores2}
+		\end{figure}
+
 	We also evaluated how reasonable were the predictions by assessing the calibration of the methods considered, i.e., by evaluating how often events which have assigned probability $p$ (for each $0<p<1$) happened (Section \ref{sec::calib}).
@@
 
-	We therefore conclude that all methods have similar predictive power, and none of them is more informative in average.
-	Nevertheless, all methods yielded better predictions than the trivial prediction, and they are well-calibrated.
+	{\color{darkgreen}Therefore, we once more highlight that 
+	although the accuracy of each method may depend on the specific characteristics of each match,
+	all methods have similar predictive power, and none of them is more informative  in average. 
+    Moreover, all methods yielded better predictions than the trivial prediction, and they were all well-calibrated.}
 
@@
 	Several other models are also available in the literature, some of which are even more complex.
-	Among them, we can cite those based on modeling the match as a stochastic process evolving through time \citep{Dixon98, Volf2009, Titman2015}, those allowing for the team performance parameters to change along the season \citep{Rue2000, Crowder2002, Owen2011, Koopman2015} and those modeling dependence between number of goals by means of bivariate count distributions \citep{Dixon97, Karlis2003, McHale2007, McHale2011}.
-Contrary to the simple multinomial models we propose,	some of these approaches are able to answer several questions;  for instance, they can estimate teams' performance parameters allowing for ranking teams according to attack and deffensive quality, and
- they can also predict the final outcomes of matches. We therefore do not claim that our models should replace
-	current state-of-the-art approaches. Instead, this work
-	indicates that while there has been a boom in the literature with the proposal of several fancy and involved models,
-	simple models can many times predict the final outcome as well as their complex counterparts. 
-	The importance of such finding is directly related to the model's usability in practice: creators of the
-	benchmark models used in this work often say a difficulty they face is that
+	Among them, we can cite those based on modeling the match as a stochastic process evolving in time \citep{Dixon98, Volf2009, Titman2015}, those allowing for the team performance parameters to change along the season \citep{Rue2000, Crowder2002, Owen2011, Koopman2015} and those modeling dependence between number of goals by means of bivariate count distributions \citep{Dixon97, Karlis2003, McHale2007, McHale2011}.
+Contrary to the simple multinomial models we propose, some of these approaches are able to answer several questions, for instance, they can estimate teams' performance parameters allowing to rank the teams according to their offensive and defensive qualities, and can also predict the number of goals scored of a particular match.
+
+Therefore, we do not claim that our models should replace
+	current state-of-the-art approaches. Instead, this work points out that, while there has been a boom in the literature with the proposal of several fancy and involved models,
+	simple models can many times predict the final outcome equally well as their complex counterparts. 
+	The importance of such finding is directly related to the models usability in practice: professionals that use the mentioned
+	benchmark models often say a difficulty they face is that
 	wrong predictions often generate anger in football fans, which is then translated into distrust
-	in subsequent predictions. Because of the complexity of those models, they find it hard to explain predicted outcomes
-	to users. This is where using simple models pays off:  the multinomial models yield results that are
-	easy to explain; they simply involve counts of losses, wins and draws!
-	They allow us to offer simple explanations to the football fans about the predictions that were made.}
-
-{\color{blue}The fact that simple models are often as effective as their competitors is often unnoticed by users of such methods, which leads to the overuse of models that are often
-	hard to interpret and to implement, and that also require one to keep track of several covariates.
+	in subsequent predictions. Because of the complexity of these models, they find hard to explain to the lay user how the outcomes were predicted.
+	This is where using simple models pays off:  the multinomial models yield results that are
+	easy to explain and only involve counts of losses, wins and draws, allowing one to offer simple explanations to football fans and journalists about the proposed predictions.}
+
+{\color{blue}The fact that simple models are often as effective as their competitors in average is often unnoticed by users of such methods, which leads to the overuse of models that are often
+	hard to interpret and to implement, and also requires one to keep track of several covariates.
 We would call this phenomenon the {\it king's nudity} in allusion to Anderson's {\it The Emperor's New Clothes}, \cite{emperor}: ``But he isn't wearing anything at all!''.
-In this spirit, since we have explored only the prediction of football matches in the specific case o Brazilian football championship, we would like to study if the same extends to other fields such as, for instance, weather or economics forecasts.}
+In this spirit, since we have explored only the prediction of football matches in the specific case of the Brazilian championship, we would like to study if the same extends to other fields such as, for instance, weather or economics forecasts.}
 
 		If, on the one hand, our findings appear as another supportive example of Ockham's razor, on the other they pose several questions about probabilistic prediction of sport events.
-		In particular, based on the fact that the models have similar performance, one may ask: is there an irreducible ``randomness'' or ``degree of unpredictability'' implicit in these events?
+		In particular, based on the fact that the models have similar {\color{darkgreen}predictive power in average}, one may ask: is there an irreducible ``randomness'' or ``degree of unpredictability'' implicit in these events?
 		Is this degree an indicator of how tight or leveled is the championship being studied?
@@
 
+			\bibitem{agresti2010}
+			Agresti, A. {\em Analysis of Ordinal Categorical Data}. Wiley, 2010.
+
 			\bibitem{arruda2000}
@@
 			\bibitem{emperor}
-			Andersen, H.  C. The emperor's new clothes. Genesis Publishing Pvt Ltd, 1987.
+			Andersen, H.  C. The emperor's new clothes. Genesis Publishing, 1987.
+
+			\bibitem{bernardo1994}
+			Bernardo, J. M. and Smith, A. F. M. {\em Bayesian Theory}. Wiley, 1994.
 
@@
 
+			\bibitem{good1965}
+			Good, I. J. {\em The Estimation of Probabilities: An Essay on Modern Bayesian Methods}. MIT Press, 1965.
+
 			\bibitem{Holgate64}
@@
 			Lad, F. {\it Operational Subjective Statistical Methods: a mathematical,
-				philosophical, and historical introduction}. New York: Wiley, 1996.
+				philosophical, and historical introduction}. Wiley, 1996.
 

### 2015-08-22 template.tex
com comentarios do Danilo

@@
 
-	Figure \ref{fig::entropy} presents the boxplots of the entropy of each prediction for the predictive models considered. Recall
-	that the entropy of a prediction $(p_1,p_2,p_3)$ is given by $- \sum_{i=1}^3 p_i \log{p_i}$.
-	Since the entropy values are smaller than 1.09, the plots show that the predictions
-	are typically more informative than the trivial prediction. Nevertheless, all methods yielded similar entropies in average, that is,
-	none of them seem to provide more informative probabilities.
-
-	\begin{figure}[H]
-		\centering
-		\includegraphics[page=10,scale=0.3]{futebolComparacaoModelosForPaper.pdf}
-		\caption{Entropy of the predictions of the various methods. Horizontal line represents the entropy of the trivial prediction $(1/3,1/3,1/3)$.}
-		\label{fig::entropy}
-	\end{figure}
-
 		%{\color{darkgreen}Therefore, our analyses show that, marginally, all methods yield similar scores in average, i.e., they have similar predictive power. A related question
@@
 		%}
-	{\color{darkgreen}Therefore, our analyses show that all methods yield similar scores in average, i.e., they have similar predictive power. A related question
-	is whether, for each match, the performance of the methods is also similar.
-To answer this question we compared the models pairwise, and the result is found on Figure \ref{fig::scores2}, where the plots display the scores of each match for every couple of models considered.
-The plots show that all methods are reasonably similar and, evidently, the Multinomial-Dirichlet models
-	are the ones that agree the most.
-To formally test the hypotheses that the models yield the same scores in average for each match, we used Friedman's rank sum test.
+		{\color{darkgreen}Therefore, our analyses indicate that all methods yield similar scores in average, i.e., they have similar predictive power. In order to formally check this, 
+		we test the hypotheses that all five models have the same median score.
+		We do this by using Friedman's rank sum test for each score, a statistical test that takes into account
+		the dependency between the observations (notice each match is evaluated by each model). 
 		Except for the logarithmic score (p-value 0.021), all the other metrics did not present significant differences at the level of confidence of 5\% (Brier: 0.077; Spherical: 0.055; Proportion of errors: 0.655).
-Post-hoc analyses show that the differences are in Mn-Dir$_1$ versus BB2 (p=0.031),
-	Mn-Dir$_2$ versus BB1 (p=0.043), and Mn-Dir$_3$ versus BB1 (p=0.030). These results thus indicate that BB1 and BB2
-	are similar to each other in terms of predictive power, while the performance of Mn-Dir models differ from the BB models \emph{for each match}.
-	We therefore conclude that while the models we investigate may yield different scores for each
-	match according to some metrics, the overall scores are similar, i. e., while in some matches Mn-Dir models
-	have better results, for others BB models have better performance. However, for a large set of matches, all methods have similar accuracy.
+Post-hoc analyses\footnote{We used
+		Friedman tests for the pairwise comparisons as well.} for the logarithmic score show that the differences are in Mn-Dir$_1$ versus BB2 (p=0.031),
+				Mn-Dir$_2$ versus BB1 (p=0.043), and Mn-Dir$_3$ versus BB1 (p=0.030). 
+				The median logarithmic scores are 
+				 0.97 for Mn-Dir$_1$, 0.94 for Mn-Dir$_2$, 0.95 for Mn-Dir$_3$,  0.97 for BB1, and  1.00
+				 for BB2, thus indicating that the new models are slightly better according to this criterium (but not according to
+				 the others).
+                 We further illustrate this point in Figure \ref{fig::scores2}, where the plots display the scores of each match for every couple of models considered.
+The plots show that all methods are reasonably similar and, evidently, the Multinomial-Dirichlet models are the ones that agree the most.
 		}
@@
 				lower left plots display Logarithmic Scores. Right plot: upper right plots display proportion of agreements
-			between methods; lower left  plots display Spherical Scores. Red line represents the identity $x=y$.}
+				between methods (i.e., proportion of times the conclusions are the same; see Section \ref{sec::calib}); lower left  plots display Spherical Scores. Red line represents the identity $x=y$.}
 				\label{fig::scores2}
+			\end{figure}
+
+	In order to check how informative the models are, Figure \ref{fig::entropy} presents the boxplots of the entropy of each prediction for the predictive models considered. Recall
+	that the entropy of a prediction $(p_1,p_2,p_3)$ is given by $- \sum_{i=1}^3 p_i \log{p_i}$.
+	Since the entropy values are smaller than 1.09, the plots show that the predictions
+	are typically more informative than the trivial prediction. Nevertheless, all methods yielded similar entropies in average, that is,
+	none of them seem to provide more informative probabilities.
+
+	\begin{figure}[H]
+		\centering
+		\includegraphics[page=10,scale=0.3]{futebolComparacaoModelosForPaper.pdf}
+		\caption{Entropy of the predictions of the various methods. Horizontal line represents the entropy of the trivial prediction $(1/3,1/3,1/3)$.}
+		\label{fig::entropy}
 	\end{figure}
@@
 	{\color{darkgreen}Therefore, we once more highlight that  
-	although the accuracy of each method may depend on the specific characteristics of each match,
 	all methods have similar predictive power, and none of them is more informative  in average. 
@@
 		If, on the one hand, our findings appear as another supportive example of Ockham's razor, on the other they pose several questions about probabilistic prediction of sport events.
-		In particular, based on the fact that the models have similar {\color{darkgreen}predictive power in average}, one may ask: is there an irreducible ``randomness'' or ``degree of unpredictability'' implicit in these events?
+		In particular, based on the fact that the models have similar predictive power in average, one may ask: is there an irreducible ``randomness'' or ``degree of unpredictability'' implicit in these events?
 		Is this degree an indicator of how tight or leveled is the championship being studied?

### 2015-08-24 response2.tex
Segunda resposta.

\documentclass[11pt]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath, graphicx, layout, verbatim}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{float}
\usepackage{color}
\usepackage{natbib}
\usepackage{verbatim}
\usepackage{subfig}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[pagebackref,colorlinks=true,urlcolor=blue,citecolor=blue	,linkcolor=blue]{hyperref}
\textheight25cm \footskip0.5cm \topmargin-1.5cm \headsep0.2cm
\oddsidemargin-0.5cm \evensidemargin-0.5cm
 \marginparwidth0cm \marginparsep = 0pt
\textwidth16cm

\onehalfspacing
\usepackage{cite}
\usepackage{url}
\urlstyle{rm}

\renewcommand{\vec}[1]{\mathbf{#1}}

\def\x{{\vec{x}}}

\def\G{{\mathbb G}}
 \newcommand\independent{\protect\mathpalette{\protect\independenT}{\perp}}
    \def\independenT#1#2{\mathrel{\setbox0\hbox{$#1#2$}%
    \copy0\kern-\wd0\mkern4mu\box0}}

 \def\X{***ATT***}
\newcommand{\red}[1]{\textbf{\color{red} ***ATT*** #1}}

\title{Response to Reviewer 2}
\date{}

\begin{document}

%the paper and
%hope to have answered the questions that were raised.

\maketitle

First of all, we would like to apologize to the referee for the miscommunication that happened at the first round. We had not received the pdf with the comments, but only the paper with some parts highlighted in yellow. We thought that point 2 was about the the word ``prevision'', but we were wrong. We now address the first review in full details.

\

\hspace{4mm} \textbf{Reviewer:} \textit{
	This is a very nicely written and clear article. It is does not set out to be particularly innovative, and that is clearly stated in the paper and the abstract. What is stated is that a Bayesian analysis (multinomial Dirichlet) of team win-loss-and-tie records for both home and away games is as good a predictor as the ``black-box'' predictors based on more complex models and data sets: and this seems to be true from the analysis presented.}

\vspace{2mm}
\textbf{Response:} We thank the referee for taking the time reviewing the paper. Below we list our detailed response to the referee's questions.\\

\vspace{6mm}

\hspace{4mm} \textbf{Reviewer:} 
	{\it 1. First paragraph page 4 needs a standard reference in support of the uniform Dirichlet. Agresti (2012) ``Analysis of Ordinal Categorical Data'' coverers this well and sites the historical work of Good (1965) and Lindley's text book (1964). There are similar supporting reference issues for for Section 2.1. There may be a better authoritative and ``web available'' reference, but I could not find one in a quick search.}

\vspace{2mm}
\textbf{Response: we have included standard references in the suggested Section (now 2.2). They are highlighted in dark green. Besides the books of Agresti and Good, we also cite Bayesian Theory (1994), by Bernardo and Smith, an authoritative reference for the multinomial-Dirichlet model.}

\vspace{6mm}

\hspace{4mm} \textbf{Reviewer:} \textit{2. My suspicion is that a slightly different way of looking at the data summarized in
Table 2 and Figure 3 on page 9 and 10 would show that here is a ``statistically significant'' difference between these methods (We will leave the definition of practical significance
to the sports writers, team managers and the bettors.). To simplify the analysis consider only Brier score and the probability predictors BB1 and Mn-Dr3. For each of the 190 matches there is an effect due to the match (home-away, quality of the two teams, etc.); and an effect due to the differences in the probability predictors. We are only interested in testing for the predictor effect. The variability reported in Figure 3 and Table 2
incudes variation across in all 190 matches, which will tend to obscure the ``predictor effect''. In this setup the obvious analysis is a paired comparison of Brier sore of BB1 vs the Brier Score for Mn-Dr3 across all 190 pairs (matches). Assuming the differences
are normally distributed this would be a paired t-test. A nonparametric test would be the paired sign test or sign-rank test. An x-y scatter plot (with the x=y line drawn) of Brier scores for all 190 matches would graphically summarize the analysis. Some form of
these pairwise plots should be included in the paper, even if the above statistical analysis indicates no significant differences.
For the analysis of all five predictors the matches are random blocks and there are methods similar to the paired t (randomized block) and sign test (Kendalls W) in this case.}

\vspace{2mm}
{\bf Response: the referee is correct in point out that our previous analyses did not include formal paired hypotheses tests concerning the performance of the models. We have now included pairwise comparisons (both statistical tests and graphical analyses), and changed the text accordingly; the new material is highlighted in dark green. Please let us know whether the new version is more sound.

We are grateful to the referee for all the insightful comments that helped to improve the paper. We hope to have addressed all his/her concerns. Please feel free to contact us in case something is still not clear, or if new concerns arise.}

\end{document}

### 2015-08-24 response2.tex
com comentarios do Danilo para respostas ao referee

@@
 {\bf Response: the referee is correct in point out that our previous analyses did not include formal paired hypotheses tests concerning the performance of the models.
-We have now included pairwise comparisons (both statistical tests and graphical analyses), and changed the text accordingly; the new material is highlighted in dark green.
+We have now included pairwise comparisons (both statistical tests and graphical analyses).
+We have decided to perform Friedman's rank sum test during the analysis, since Friedman test is an analog of the approaches suggested in the reviewer's comments, and it also allows us to make multiple comparisons among models.
+The text was modified accordingly; the new material is highlighted in dark green.
 Please let us know whether the new version is more sound.
